### 2024-08-14 paper/main.tex
Added current version of everything

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
%Template version as of 6/27/2024

\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\title{Decoding the Amplitude of the DCF77 Longwave Time Signal by using the Goertzel Algorithm}

\author{\IEEEauthorblockN{1\textsuperscript{st} Leander Hackmann}
\IEEEauthorblockA{\textit{Master Embedded Systems Engineering} \\
\textit{FH Dortmund}\\
Dortmund, Germany \\
Mat.-Nr.: 7217912, leander.hackmann001@stud.fh-dortmund.de}
}

\maketitle

\begin{abstract}
This document is a model and instructions for \LaTeX.
This and the IEEEtran.cls file define the components of your paper [title, text, heads, etc.]. *CRITICAL: Do Not Use Symbols, Special Characters, Footnotes, 
or Math in Paper Title or Abstract.
\end{abstract}

\begin{IEEEkeywords}
DCF77, Goertzel, Time Signal, Decoding, Longwave
\end{IEEEkeywords}

\section{Introduction}
This document is a model and instructions for \LaTeX.
Please observe the conference page limits. For more information about how to become an IEEE Conference author or how to write your paper, please visit   IEEE Conference Author Center website: https://conferences.ieeeauthorcenter.ieee.org/.

\subsection{Maintaining the Integrity of the Specifications}

The IEEEtran class file is used to format your paper and style the text. All margins, 
column widths, line spaces, and text fonts are prescribed; please do not 
alter them. You may note peculiarities. For example, the head margin
measures proportionately more than is customary. This measurement 
and others are deliberate, using specifications that anticipate your paper 
as one part of the entire proceedings, and not as an independent document. 
Please do not revise any of the current designations.

\section{Prepare Your Paper Before Styling}
Before you begin to format your paper, first write and save the content as a 
separate text file. Complete all content and organizational editing before 
formatting. Please note sections \ref{AA} to \ref{FAT} below for more information on 
proofreading, spelling and grammar.

Keep your text and graphic files separate until after the text has been 
formatted and styled. Do not number text heads---{\LaTeX} will do that 
for you.

\subsection{Abbreviations and Acronyms}\label{AA}
Define abbreviations and acronyms the first time they are used in the text, 
even after they have been defined in the abstract. Abbreviations such as 
IEEE, SI, MKS, CGS, ac, dc, and rms do not have to be defined. Do not use 
abbreviations in the title or heads unless they are unavoidable.

\subsection{Units}
\begin{itemize}
\item Use either SI (MKS) or CGS as primary units. (SI units are encouraged.) English units may be used as secondary units (in parentheses). An exception would be the use of English units as identifiers in trade, such as ``3.5-inch disk drive''.
\item Avoid combining SI and CGS units, such as current in amperes and magnetic field in oersteds. This often leads to confusion because equations do not balance dimensionally. If you must use mixed units, clearly state the units for each quantity that you use in an equation.
\item Do not mix complete spellings and abbreviations of units: ``Wb/m\textsuperscript{2}'' or ``webers per square meter'', not ``webers/m\textsuperscript{2}''. Spell out units when they appear in text: ``. . . a few henries'', not ``. . . a few H''.
\item Use a zero before decimal points: ``0.25'', not ``.25''. Use ``cm\textsuperscript{3}'', not ``cc''.)
\end{itemize}

\subsection{Equations}
Number equations consecutively. To make your 
equations more compact, you may use the solidus (~/~), the exp function, or 
appropriate exponents. Italicize Roman symbols for quantities and variables, 
but not Greek symbols. Use a long dash rather than a hyphen for a minus 
sign. Punctuate equations with commas or periods when they are part of a 
sentence, as in:
\begin{equation}
a+b=\gamma\label{eq}
\end{equation}

Be sure that the 
symbols in your equation have been defined before or immediately following 
the equation. Use ``\eqref{eq}'', not ``Eq.~\eqref{eq}'' or ``equation \eqref{eq}'', except at 
the beginning of a sentence: ``Equation \eqref{eq} is . . .''

\subsection{\LaTeX-Specific Advice}

Please use ``soft'' (e.g., \verb|\eqref{Eq}|) cross references instead
of ``hard'' references (e.g., \verb|(1)|). That will make it possible
to combine sections, add equations, or change the order of figures or
citations without having to go through the file line by line.

Please don't use the \verb|{eqnarray}| equation environment. Use
\verb|{align}| or \verb|{IEEEeqnarray}| instead. The \verb|{eqnarray}|
environment leaves unsightly spaces around relation symbols.

Please note that the \verb|{subequations}| environment in {\LaTeX}
will increment the main equation counter even when there are no
equation numbers displayed. If you forget that, you might write an
article in which the equation numbers skip from (17) to (20), causing
the copy editors to wonder if you've discovered a new method of
counting.

{\BibTeX} does not work by magic. It doesn't get the bibliographic
data from thin air but from .bib files. If you use {\BibTeX} to produce a
bibliography you must send the .bib files.

{\LaTeX} can't read your mind. If you assign the same label to a
subsubsection and a table, you might find that Table I has been cross
referenced as Table IV-B3.

{\LaTeX} does not have precognitive abilities. If you put a
\verb|\label| command before the command that updates the counter it's
supposed to be using, the label will pick up the last counter to be
cross referenced instead. In particular, a \verb|\label| command
should not go before the caption of a figure or a table.

Do not use \verb|\nonumber| inside the \verb|{array}| environment. It
will not stop equation numbers inside \verb|{array}| (there won't be
any anyway) and it might stop a wanted equation number in the
surrounding equation.

\subsection{Some Common Mistakes}\label{SCM}
\begin{itemize}
\item The word ``data'' is plural, not singular.
\item The subscript for the permeability of vacuum $\mu_{0}$, and other common scientific constants, is zero with subscript formatting, not a lowercase letter ``o''.
\item In American English, commas, semicolons, periods, question and exclamation marks are located within quotation marks only when a complete thought or name is cited, such as a title or full quotation. When quotation marks are used, instead of a bold or italic typeface, to highlight a word or phrase, punctuation should appear outside of the quotation marks. A parenthetical phrase or statement at the end of a sentence is punctuated outside of the closing parenthesis (like this). (A parenthetical sentence is punctuated within the parentheses.)
\item A graph within a graph is an ``inset'', not an ``insert''. The word alternatively is preferred to the word ``alternately'' (unless you really mean something that alternates).
\item Do not use the word ``essentially'' to mean ``approximately'' or ``effectively''.
\item In your paper title, if the words ``that uses'' can accurately replace the word ``using'', capitalize the ``u''; if not, keep using lower-cased.
\item Be aware of the different meanings of the homophones ``affect'' and ``effect'', ``complement'' and ``compliment'', ``discreet'' and ``discrete'', ``principal'' and ``principle''.
\item Do not confuse ``imply'' and ``infer''.
\item The prefix ``non'' is not a word; it should be joined to the word it modifies, usually without a hyphen.
\item There is no period after the ``et'' in the Latin abbreviation ``et al.''.
\item The abbreviation ``i.e.'' means ``that is'', and the abbreviation ``e.g.'' means ``for example''.
\end{itemize}
An excellent style manual for science writers is \cite{b7}.

\subsection{Authors and Affiliations}\label{AAA}
\textbf{The class file is designed for, but not limited to, six authors.} A 
minimum of one author is required for all conference articles. Author names 
should be listed starting from left to right and then moving down to the 
next line. This is the author sequence that will be used in future citations 
and by indexing services. Names should not be listed in columns nor group by 
affiliation. Please keep your affiliations as succinct as possible (for 
example, do not differentiate among departments of the same organization).

\subsection{Identify the Headings}\label{ITH}
Headings, or heads, are organizational devices that guide the reader through 
your paper. There are two types: component heads and text heads.

Component heads identify the different components of your paper and are not 
topically subordinate to each other. Examples include Acknowledgments and 
References and, for these, the correct style to use is ``Heading 5''. Use 
``figure caption'' for your Figure captions, and ``table head'' for your 
table title. Run-in heads, such as ``Abstract'', will require you to apply a 
style (in this case, italic) in addition to the style provided by the drop 
down menu to differentiate the head from the text.

Text heads organize the topics on a relational, hierarchical basis. For 
example, the paper title is the primary text head because all subsequent 
material relates and elaborates on this one topic. If there are two or more 
sub-topics, the next level head (uppercase Roman numerals) should be used 
and, conversely, if there are not at least two sub-topics, then no subheads 
should be introduced.

\subsection{Figures and Tables}\label{FAT}
\paragraph{Positioning Figures and Tables} Place figures and tables at the top and 
bottom of columns. Avoid placing them in the middle of columns. Large 
figures and tables may span across both columns. Figure captions should be 
below the figures; table heads should appear above the tables. Insert 
figures and tables after they are cited in the text. Use the abbreviation 
``Fig.~\ref{fig}'', even at the beginning of a sentence.

\begin{table}[htbp]
\caption{Table Type Styles}
\begin{center}
\begin{tabular}{|c|c|c|c|}
\hline
\textbf{Table}&\multicolumn{3}{|c|}{\textbf{Table Column Head}} \\
\cline{2-4} 
\textbf{Head} & \textbf{\textit{Table column subhead}}& \textbf{\textit{Subhead}}& \textbf{\textit{Subhead}} \\
\hline
copy& More table copy$^{\mathrm{a}}$& &  \\
\hline
\multicolumn{4}{l}{$^{\mathrm{a}}$Sample of a Table footnote.}
\end{tabular}
\label{tab1}
\end{center}
\end{table}

\begin{figure}[htbp]
\centerline{\includegraphics{fig1.png}}
\caption{Example of a figure caption.}
\label{fig}
\end{figure}

Figure Labels: Use 8 point Times New Roman for Figure labels. Use words 
rather than symbols or abbreviations when writing Figure axis labels to 
avoid confusing the reader. As an example, write the quantity 
``Magnetization'', or ``Magnetization, M'', not just ``M''. If including 
units in the label, present them within parentheses. Do not label axes only 
with units. In the example, write ``Magnetization (A/m)'' or ``Magnetization 
\{A[m(1)]\}'', not just ``A/m''. Do not label axes with a ratio of 
quantities and units. For example, write ``Temperature (K)'', not 
``Temperature/K''.

\section*{Acknowledgment}

The preferred spelling of the word ``acknowledgment'' in America is without 
an ``e'' after the ``g''. Avoid the stilted expression ``one of us (R. B. 
G.) thanks $\ldots$''. Instead, try ``R. B. G. thanks$\ldots$''. Put sponsor 
acknowledgments in the unnumbered footnote on the first page.

\section*{References}

Please number citations consecutively within brackets \cite{b1}. The 
sentence punctuation follows the bracket \cite{b2}. Refer simply to the reference 
number, as in \cite{b3}---do not use ``Ref. \cite{b3}'' or ``reference \cite{b3}'' except at 
the beginning of a sentence: ``Reference \cite{b3} was the first $\ldots$''

Number footnotes separately in superscripts. Place the actual footnote at 
the bottom of the column in which it was cited. Do not put footnotes in the 
abstract or reference list. Use letters for table footnotes.

Unless there are six authors or more give all authors' names; do not use 
``et al.''. Papers that have not been published, even if they have been 
submitted for publication, should be cited as ``unpublished'' \cite{b4}. Papers 
that have been accepted for publication should be cited as ``in press'' \cite{b5}. 
Capitalize only the first word in a paper title, except for proper nouns and 
element symbols.

For papers published in translation journals, please give the English 
citation first, followed by the original foreign-language citation \cite{b6}.

\begin{thebibliography}{00}
\bibitem{b1} G. Eason, B. Noble, and I. N. Sneddon, ``On certain integrals of Lipschitz-Hankel type involving products of Bessel functions,'' Phil. Trans. Roy. Soc. London, vol. A247, pp. 529--551, April 1955.
\bibitem{b2} J. Clerk Maxwell, A Treatise on Electricity and Magnetism, 3rd ed., vol. 2. Oxford: Clarendon, 1892, pp.68--73.
\bibitem{b3} I. S. Jacobs and C. P. Bean, ``Fine particles, thin films and exchange anisotropy,'' in Magnetism, vol. III, G. T. Rado and H. Suhl, Eds. New York: Academic, 1963, pp. 271--350.
\bibitem{b4} K. Elissa, ``Title of paper if known,'' unpublished.
\bibitem{b5} R. Nicole, ``Title of paper with only first word capitalized,'' J. Name Stand. Abbrev., in press.
\bibitem{b6} Y. Yorozu, M. Hirano, K. Oka, and Y. Tagawa, ``Electron spectroscopy studies on magneto-optical media and plastic substrate interface,'' IEEE Transl. J. Magn. Japan, vol. 2, pp. 740--741, August 1987 [Digests 9th Annual Conf. Magnetics Japan, p. 301, 1982].
\bibitem{b7} M. Young, The Technical Writer's Handbook. Mill Valley, CA: University Science, 1989.
\bibitem{b8} D. P. Kingma and M. Welling, ``Auto-encoding variational Bayes,'' 2013, arXiv:1312.6114. [Online]. Available: https://arxiv.org/abs/1312.6114
\bibitem{b9} S. Liu, ``Wi-Fi Energy Detection Testbed (12MTC),'' 2023, gitHub repository. [Online]. Available: https://github.com/liustone99/Wi-Fi-Energy-Detection-Testbed-12MTC
\bibitem{b10} ``Treatment episode data set: discharges (TEDS-D): concatenated, 2006 to 2009.'' U.S. Department of Health and Human Services, Substance Abuse and Mental Health Services Administration, Office of Applied Studies, August, 2013, DOI:10.3886/ICPSR30122.v2
\bibitem{b11} K. Eves and J. Valasek, ``Adaptive control for singularly perturbed systems examples,'' Code Ocean, Aug. 2023. [Online]. Available: https://codeocean.com/capsule/4989235/tree
\end{thebibliography}

\vspace{12pt}
\color{red}
IEEE conference templates contain guidance text for composing and formatting conference papers. Please ensure that all template text is removed from your conference paper prior to submission to the conference. Failure to remove the template text from your paper may result in your paper not being published.

\end{document}

### 2024-08-14 matlab_scripts/adaptive_threshold1.m

@@ -1,0 +1,58 @@
+clear;
+close all;
+clc;
+
+
+
+% Generate a longer sample signal
+rng(0);  % For reproducibility
+N = 1000;  % Length of the signal
+signal = [randn(1, 300) * 0.1, randn(1, 200) * 0.1 + 1, randn(1, 300) * 0.1, randn(1, 200) * 0.1 + 1];
+
+% Initialize parameters
+threshold = 0.5;  % Initial threshold
+output = zeros(1, length(signal));  % Initialize output array
+alpha = 0.001;  % Learning rate for adaptive threshold
+
+% Adaptive thresholding
+for i = 1:length(signal)
+    % Determine output based on current threshold
+    if signal(i) > threshold
+        output(i) = 1;
+    else
+        output(i) = 0;
+    end
+    
+    % Update the threshold based on the current sample
+    % If output is 1, threshold should move closer to the current sample if it is 1
+    % If output is 0, threshold should move closer to the current sample if it is 0
+    if output(i) == 1
+        threshold = threshold + alpha * (signal(i) - threshold);
+    else
+        threshold = threshold - alpha * (threshold - signal(i));
+    end
+end
+
+% Display results
+disp('Final Threshold:');
+disp(threshold);
+
+% Plot the signal, threshold, and output
+figure;
+subplot(3,1,1);
+plot(signal, '-o');
+title('Input Signal');
+ylabel('Amplitude');
+xlabel('Sample');
+
+subplot(3,1,2);
+plot(output, '-o');
+title('Output Signal');
+ylabel('Binary Output');
+xlabel('Sample');
+
+subplot(3,1,3);
+plot(1:length(signal), threshold * ones(1,length(signal)), '--');
+title('Adaptive Threshold');
+ylabel('Threshold');
+xlabel('Sample');

### 2024-08-14 matlab_scripts/derivative_ramps.m

@@ -1,0 +1,45 @@
+clear;
+close all;
+clc;
+
+
+
+% Define the time vector
+t = 0:0.01:10; % from 0 to 10 seconds with a step of 0.01 seconds
+
+% Define the ramp signal
+ramp1 = t(t<=2);         % Ramp from 0 to 2 seconds
+ramp2 = 2*ones(size(t(t>2 & t<=4))); % Constant from 2 to 4 seconds
+ramp3 = (t(t>4 & t<=6)-4) + 2; % Ramp from 4 to 6 seconds starting from 2
+ramp4 = 4*ones(size(t(t>6 & t<=8))); % Constant from 6 to 8 seconds
+ramp5 = (t(t>8 & t<=10)-8) + 4; % Ramp from 8 to 10 seconds starting from 4
+
+% Concatenate all parts to form the complete signal
+signal = [ramp1, ramp2, ramp3, ramp4, ramp5];
+
+% Calculate the derivative using numerical differentiation
+dt = t(2) - t(1); % time step
+derivative = diff(signal) / dt; % numerical derivative
+t_derivative = t(1:end-1); % time vector for the derivative
+
+% Plot the original signal and its derivative
+figure;
+
+% Plot original signal
+subplot(2,1,1);
+plot(t, signal, 'b', 'LineWidth', 1.5);
+title('Original Signal (Series of Ramps)');
+xlabel('Time (s)');
+ylabel('Amplitude');
+grid on;
+
+% Plot derivative of the signal
+subplot(2,1,2);
+plot(t_derivative, derivative, 'r', 'LineWidth', 1.5);
+title('Derivative of the Signal');
+xlabel('Time (s)');
+ylabel('Amplitude');
+grid on;
+
+% Adjust plot spacing
+tight_layout();

### 2024-08-14 matlab_scripts/goertzel_test1.m

@@ -1,0 +1,41 @@
+clear;
+close all;
+clc;
+
+
+% Parameters
+fs = 8000;  % Sampling frequency
+f = 1000;   % Frequency to detect
+N = 256;    % Number of samples
+n = 0:N-1;  % Sample index
+
+% Generate a test signal (sine wave at 1 kHz)
+x = sin(2 * pi * f * n / fs);
+
+% Apply the Goertzel Algorithm
+k = round((f / fs) * N);  % Bin index for target frequency
+result = goertzel(x, k);
+
+% Display result
+disp(['Magnitude at ', num2str(f), ' Hz: ', num2str(abs(result))]);
+
+function magnitude = goertzel(x, k)
+    N = length(x);
+    omega = 2 * pi * k / N;
+    cos_omega = cos(omega);
+    sin_omega = sin(omega);
+    coeff = 2 * cos_omega;
+
+    Q1 = 0;
+    Q2 = 0;
+    for n = 1:N
+        Q0 = x(n) + coeff * Q1 - Q2;
+        Q2 = Q1;
+        Q1 = Q0;
+    end
+
+    real_part = (Q1 - Q2 * cos_omega);
+    imag_part = (Q2 * sin_omega);
+
+    magnitude = real_part + 1i * imag_part;
+end

### 2024-08-14 matlab_scripts/goertzel_test2.m

@@ -1,0 +1,57 @@
+clear;
+close all;
+clc;
+
+
+% Parameters
+fs = 1000;            % Sampling frequency
+f = 100;              % Carrier frequency
+duration = 4;         % Duration of the signal in seconds
+N = fs * duration;    % Total number of samples
+t = (0:N-1)/fs;       % Time vector
+
+% Create a signal with amplitude switching
+signal = [sin(2*pi*f*t(1:N/4)), 0.5*sin(2*pi*f*t(N/4+1:N/2)), ...
+          sin(2*pi*f*t(N/2+1:3*N/4)), 0.5*sin(2*pi*f*t(3*N/4+1:end))];
+
+% Initialize Goertzel algorithm parameters
+k = round(f*duration);            % Frequency bin
+omega = 2 * pi * k / N;
+coeff = 2 * cos(omega);
+s_prev = 0;
+s_prev2 = 0;
+
+% Segment size for analysis (e.g., 1 second)
+segment_size = fs;
+
+% Initialize array to store power of the carrier frequency
+power = zeros(1, duration);
+
+for i = 1:duration
+    s_prev = 0;
+    s_prev2 = 0;
+    for j = 1:segment_size
+        s = signal((i-1)*segment_size + j) + coeff * s_prev - s_prev2;
+        s_prev2 = s_prev;
+        s_prev = s;
+    end
+    % Calculate power
+    power(i) = s_prev2^2 + s_prev^2 - coeff * s_prev * s_prev2;
+end
+
+% Normalize power to see the variations clearly
+normalized_power = power / max(power);
+
+% Plot the results
+figure;
+subplot(2,1,1);
+plot(t, signal);
+title('Signal with Amplitude Switching');
+xlabel('Time (s)');
+ylabel('Amplitude');
+
+subplot(2,1,2);
+stem(1:duration, normalized_power);
+title('Normalized Power of Carrier Frequency over Time');
+xlabel('Time (s)');
+ylabel('Normalized Power');

### 2024-08-14 matlab_scripts/goertzel_test3.m

@@ -1,0 +1,61 @@
+clear;
+close all;
+clc;
+
+
+
+% Parameters
+fs = 1000;            % Sampling frequency
+f = 100;              % Carrier frequency
+total_duration = 8;   % Total duration of the signal in seconds
+N = fs * total_duration;  % Total number of samples
+t = (0:N-1)/fs;       % Time vector
+
+% Create a signal with amplitude switching every second
+signal = [sin(2*pi*f*t(1:N/4)), 0.5*sin(2*pi*f*t(N/4+1:N/2)), ...
+          sin(2*pi*f*t(N/2+1:3*N/4)), 0.5*sin(2*pi*f*t(3*N/4+1:end))];
+
+% Parameters for Goertzel algorithm
+segment_duration = 0.5;   % Duration of each segment in seconds
+segment_size = fs * segment_duration; % Segment size in samples
+num_segments = total_duration / segment_duration; % Number of segments
+
+% Initialize Goertzel algorithm parameters
+k = round(f*segment_duration);  % Frequency bin for the segment
+omega = 2 * pi * k / segment_size;
+coeff = 2 * cos(omega);
+
+% Initialize array to store power of the carrier frequency
+power = zeros(1, num_segments);
+
+% Loop through each segment and apply Goertzel algorithm
+for seg = 1:num_segments
+    s_prev = 0;
+    s_prev2 = 0;
+    start_idx = (seg-1)*segment_size + 1;
+    end_idx = seg*segment_size;
+    for j = start_idx:end_idx
+        s = signal(j) + coeff * s_prev - s_prev2;
+        s_prev2 = s_prev;
+        s_prev = s;
+    end
+    % Calculate power
+    power(seg) = s_prev2^2 + s_prev^2 - coeff * s_prev * s_prev2;
+end
+
+% Normalize power to see the variations clearly
+normalized_power = power / max(power);
+
+% Plot the results
+figure;
+subplot(2,1,1);
+plot(t, signal);
+title('Signal with Amplitude Switching');
+xlabel('Time (s)');
+ylabel('Amplitude');
+
+subplot(2,1,2);
+stem((1:num_segments)*segment_duration, normalized_power);
+title('Normalized Power of Carrier Frequency over Time');
+xlabel('Time (s)');
+ylabel('Normalized Power');

### 2024-08-14 matlab_scripts/goertzel_test4.m

@@ -1,0 +1,91 @@
+clear;
+close all;
+clc;
+
+
+
+
+% Parameters
+fs = 1000;            % Sampling frequency
+f = 100;              % Carrier frequency
+total_duration = 8;   % Total duration of the signal in seconds
+N = fs * total_duration;  % Total number of samples
+t = (0:N-1)/fs;       % Time vector
+
+% Create a signal with amplitude switching every second
+signal = [sin(2*pi*f*t(1:N/4)), 0.5*sin(2*pi*f*t(N/4+1:N/2)), ...
+          sin(2*pi*f*t(N/2+1:3*N/4)), 0.5*sin(2*pi*f*t(3*N/4+1:end))];
+
+% Parameters for Goertzel algorithm
+segment_duration = 1;   % Duration of each segment in seconds
+segment_size = fs * segment_duration; % Segment size in samples
+num_segments = total_duration / segment_duration; % Number of segments
+
+% Initialize Goertzel algorithm parameters
+k = round(f*segment_duration);  % Frequency bin for the segment
+omega = 2 * pi * k / segment_size;
+coeff = 2 * cos(omega);
+
+% Initialize array to store power of the carrier frequency
+power = zeros(1, num_segments);
+
+% Loop through each segment and apply Goertzel algorithm
+for seg = 1:num_segments
+    s_prev = 0;
+    s_prev2 = 0;
+    start_idx = (seg-1)*segment_size + 1;
+    end_idx = seg*segment_size;
+    for j = start_idx:end_idx
+        s = signal(j) + coeff * s_prev - s_prev2;
+        s_prev2 = s_prev;
+        s_prev = s;
+    end
+    % Calculate power
+    power(seg) = s_prev2^2 + s_prev^2 - coeff * s_prev * s_prev2;
+end
+
+% Normalize power to see the variations clearly
+normalized_power = power / max(power);
+
+% Parameters for adaptive threshold
+window_size = 3; % Size of the moving window
+alpha = 1.5;    % Multiplier for standard deviation to define the threshold
+
+% Initialize array to store adaptive thresholds
+adaptive_threshold = zeros(1, num_segments);
+
+% Calculate adaptive thresholds
+for i = window_size:num_segments
+    window_data = normalized_power(i-window_size+1:i);
+    moving_avg = mean(window_data);
+    moving_std = std(window_data);
+    adaptive_threshold(i) = moving_avg - alpha * moving_std;
+end
+
[…]

### 2024-08-14 matlab_scripts/main_goertzel_derivative_running.m

@@ -1,0 +1,142 @@
+clear;
+close all;
+clc;
+
+%% Parameter Section
+
+%Sampling parameters
+fs = 200e3; %Sampling frequency in Hz
+duration = 5; %Sampling duration in s
+
+%AWGN-Channel parameters
+awgn_snr = 0; %SNR of the AWGN-channel in dB
+
+
+
+%% Signal Creation Section
+
+%Create time vector
+t = 0:1/fs:duration;
+
+%Create a variable with the number of samples
+N_samples = length(t);
+
+%Carrier signal (cos at 77.5kHz)
+fc = 77.5e3; %Carrier frequency of the DCF77 transmitter in Hz (77.5kHz)
+carrier_signal = cos(2*pi*fc*t);
+
+%Time signal (square wave with frequency of 1Hz, 80% duty cycle, and a range from 0 to 1)
+time_signal = 0.5*(square(-2*pi*1*t, 80) + 1);
+
+%Create the DCF77 signal by using Amplitude Modulation (carrier is reduced to 15% during the gap)
+dcf77_signal = (0.85*time_signal + 0.15) .* carrier_signal;
+
+
+
+%% AWGN-Channel Section
+
+%Add noise by passing the DCF77 signal through an AWGN-Channel
+dcf77_signal_noise = awgn(dcf77_signal, awgn_snr, 'measured');
+
+
+
+%% Goertzel Section
+
+%Goertzel parameters
+goertzel_N = N_samples;                             % Length of signal
+goertzel_k = round(fc * goertzel_N / fs);           % Bin index corresponding to carrier frequency
+goertzel_omega = (2*pi*goertzel_k) / goertzel_N;    % Frequency bin
+goertzel_coeff = 2*cos(goertzel_omega);             % Goertzel coefficient
+
+%Initialize Goertzel variables
+s_prev = 0;
+s_prev2 = 0;
+goertzel_magnitude_vec = zeros(1, goertzel_N);
+
+%Goertzel algorithm execution
+for n = 1:goertzel_N
+    s = dcf77_signal_noise(n) + goertzel_coeff * s_prev - s_prev2;
+    s_prev2 = s_prev;
+    s_prev = s;
[…]

### 2024-08-14 matlab_scripts/main_script_dynamic_detection.m

@@ -1,0 +1,212 @@
+clear;
+close all;
+clc;
+
+%% Simulation Parameter Section
+
+%Sampling parameters
+fs = 200e3; %Sampling frequency in Hz
+duration = 24; %Overall sampling duration in s (duration of the simulation)
+
+%AWGN-Channel parameters
+awgn_snr = -10; %SNR after the AWGN-channel in dB
+
+%Goertzel Macro parameters
+goertzel_segment_duration = 0.01; %Duration of the Goertzel algorithm segment in s
+
+%Detector parameters
+det_threshold = 0.15; %Threshold for the detector
+
+%% Signal Creation Section
+
+%Creating a time vector for the duration of the simulation
+t = 0:1/fs:duration;
+
+%Creating a variable with the number of samples
+N_samples = length(t);
+
+%Carrier signal (cos at 77.5kHz)
+fc = 77.5e3; %Storing the carrier frequency of the DCF77 transmitter in Hz (77.5kHz)
+carrier_signal = cos(2*pi*fc*t);
+
+%Time signal (square wave with frequency of 1Hz, 80% duty cycle, and a range from 0 to 1)
+one_samples_80 = round(0.8 * fs);
+one_samples_90 = round(0.9 * fs);
+
+rect_duty_80 = [zeros(1, fs - one_samples_80), ones(1, one_samples_80)]; %Rect, duty-cycle 80%, starting at 0
+rect_duty_90 = [zeros(1, fs - one_samples_90), ones(1, one_samples_90)]; %Rect, duty-cycle 90%, starting at 0
+
+time_code_signal = [];
+for i = 1:ceil(duration)
+    if mod(i, 3) == 0
+        time_code_signal = [time_code_signal, rect_duty_90];
+    else
+        time_code_signal = [time_code_signal, rect_duty_80];
+    end
+end
+time_code_signal = time_code_signal(1:N_samples-1);
+time_code_signal = [zeros(1, 1), time_code_signal];
+
+%Creating the DCF77 signal by using Amplitude Modulation (carrier is reduced to 15% during the gap)
+dcf77_signal = (0.85*time_code_signal + 0.15) .* carrier_signal;
+
+
+
+%% AWGN-Channel Section
+
+%Add noise by passing the DCF77 signal through an AWGN-Channel
+dcf77_signal_noise = awgn(dcf77_signal, awgn_snr, 'measured');
+
+
+
[…]

### 2024-08-14 matlab_scripts/main_script_fixed_threshold.m

@@ -1,0 +1,180 @@
+clear;
+close all;
+clc;
+
+%% Simulation Parameter Section
+
+%Sampling parameters
+fs = 200e3; %Sampling frequency in Hz
+duration = 5; %Overall sampling duration in s (duration of the simulation)
+
+%AWGN-Channel parameters
+awgn_snr = -15; %SNR after the AWGN-channel in dB
+
+%Goertzel Macro parameters
+goertzel_segment_duration = 0.01; %Duration of the Goertzel algorithm segment in s
+
+%Detector parameters
+det_threshold = 0.15; %Threshold for the detector
+
+%% Signal Creation Section
+
+%Creating a time vector for the duration of the simulation
+t = 0:1/fs:duration;
+
+%Creating a variable with the number of samples
+N_samples = length(t);
+
+%Carrier signal (cos at 77.5kHz)
+fc = 77.5e3; %Storing the carrier frequency of the DCF77 transmitter in Hz (77.5kHz)
+carrier_signal = cos(2*pi*fc*t);
+
+%Time signal (square wave with frequency of 1Hz, 80% duty cycle, and a range from 0 to 1)
+time_code_signal = 0.5*(square(-2*pi*1*t, 80) + 1);
+
+%Creating the DCF77 signal by using Amplitude Modulation (carrier is reduced to 15% during the gap)
+dcf77_signal = (0.85*time_code_signal + 0.15) .* carrier_signal;
+
+
+
+%% AWGN-Channel Section
+
+%Add noise by passing the DCF77 signal through an AWGN-Channel
+dcf77_signal_noise = awgn(dcf77_signal, awgn_snr, 'measured');
+
+
+
+%% Goertzel Section
+
+%Batch analysis parameters
+goertzel_segment_size = fs * goertzel_segment_duration; %Calculating the number of samples for one segment
+goertzel_num_segments = duration / goertzel_segment_duration; %Calculating the number of segments
+t_goertzel_segments_results = (1:goertzel_num_segments)*goertzel_segment_duration; %Create a time vector for the results for plotting
+
+%Goertzel parameters
+goertzel_k = round(fc * goertzel_segment_duration);
+goertzel_omega = 2 * pi * goertzel_k / goertzel_segment_size;
+goertzel_coeff = 2 * cos(goertzel_omega);
+
[…]

### 2024-08-14 matlab_scripts/main_script_normalized_detection.m

@@ -1,0 +1,198 @@
+clear;
+close all;
+clc;
+
+%% Simulation Parameter Section
+
+%Sampling parameters
+fs = 200e3; %Sampling frequency in Hz
+duration = 6; %Overall sampling duration in s (duration of the simulation)
+
+%AWGN-Channel parameters
+awgn_snr = -15; %SNR after the AWGN-channel in dB
+
+%Goertzel Macro parameters
+goertzel_segment_duration = 0.01; %Duration of the Goertzel algorithm segment in s
+
+%Detector parameters
+det_threshold = 0.15; %Threshold for the detector
+
+%% Signal Creation Section
+
+%Creating a time vector for the duration of the simulation
+t = 0:1/fs:duration;
+
+%Creating a variable with the number of samples
+N_samples = length(t);
+
+%Carrier signal (cos at 77.5kHz)
+fc = 77.5e3; %Storing the carrier frequency of the DCF77 transmitter in Hz (77.5kHz)
+carrier_signal = cos(2*pi*fc*t);
+
+%Time signal (square wave with frequency of 1Hz, 80% duty cycle, and a range from 0 to 1)
+one_samples_80 = round(0.8 * fs);
+one_samples_90 = round(0.9 * fs);
+
+rect_duty_80 = [zeros(1, fs - one_samples_80), ones(1, one_samples_80)]; %Rect, duty-cycle 80%, starting at 0
+rect_duty_90 = [zeros(1, fs - one_samples_90), ones(1, one_samples_90)]; %Rect, duty-cycle 90%, starting at 0
+
+time_code_signal = [];
+for i = 1:ceil(duration)
+    if mod(i, 3) == 0
+        time_code_signal = [time_code_signal, rect_duty_90];
+    else
+        time_code_signal = [time_code_signal, rect_duty_80];
+    end
+end
+time_code_signal = time_code_signal(1:N_samples-1);
+time_code_signal = [zeros(1, 1), time_code_signal];
+
+%Creating the DCF77 signal by using Amplitude Modulation (carrier is reduced to 15% during the gap)
+dcf77_signal = (0.85*time_code_signal + 0.15) .* carrier_signal;
+
+
+
+%% AWGN-Channel Section
+
+%Add noise by passing the DCF77 signal through an AWGN-Channel
+dcf77_signal_noise = awgn(dcf77_signal, awgn_snr, 'measured');
+
+
+
[…]

### 2024-08-14 matlab_scripts/test_signal.m

@@ -1,0 +1,35 @@
+clear;
+close all;
+clc;
+
+% Parameters
+fs = 1000; % Sampling frequency in Hz
+duration = 1; % Duration of the signal in seconds
+duty_cycle = 0.8; % Duty cycle (80%)
+
+% Time vector
+t = 0:1/fs:duration;
+
+% Number of samples
+num_samples = length(t);
+
+% Calculate the number of samples for the pulse width and gap
+pulse_width_samples = round(duty_cycle * num_samples);
+gap_samples = num_samples - pulse_width_samples;
+
+% Create the rectangular pulse with the gap at the beginning
+rect_signal = [zeros(1, gap_samples), ones(1, pulse_width_samples)];
+
+% Truncate or extend the signal to match the duration exactly
+rect_signal = rect_signal(1:num_samples);
+
+% Plot the signal
+figure;
+plot(t, rect_signal, 'LineWidth', 1.5);
+xlabel('Time (s)');
+ylabel('Amplitude');
+title('Rectangular Pulse with 80% Duty Cycle and Gap at Beginning');
+grid on;
+
+% Optionally, you can save the signal to a file
+audiowrite('rect_signal.wav', rect_signal, fs);

### 2024-08-14 stm32_workspace/bluePill_DCF77/Core/Src/main.c

@@ -1,0 +1,401 @@
+/* USER CODE BEGIN Header */
+/**
+  ******************************************************************************
+  * @file           : main.c
+  * @brief          : Main program body
+  ******************************************************************************
+  * @attention
+  *
+  * Copyright (c) 2024 STMicroelectronics.
+  * All rights reserved.
+  *
+  * This software is licensed under terms that can be found in the LICENSE file
+  * in the root directory of this software component.
+  * If no LICENSE file comes with this software, it is provided AS-IS.
+  *
+  ******************************************************************************
+  */
+/* USER CODE END Header */
+/* Includes ------------------------------------------------------------------*/
+#include "main.h"
+
+/* Private includes ----------------------------------------------------------*/
+/* USER CODE BEGIN Includes */
+#include <math.h>
+/* USER CODE END Includes */
+
+/* Private typedef -----------------------------------------------------------*/
+/* USER CODE BEGIN PTD */
+
+/* USER CODE END PTD */
+
+/* Private define ------------------------------------------------------------*/
+/* USER CODE BEGIN PD */
+#define N 4000
+#define halfN 2000
+/* USER CODE END PD */
+
+/* Private macro -------------------------------------------------------------*/
+/* USER CODE BEGIN PM */
+
+/* USER CODE END PM */
+
+/* Private variables ---------------------------------------------------------*/
+ADC_HandleTypeDef hadc1;
+DMA_HandleTypeDef hdma_adc1;
+
+TIM_HandleTypeDef htim3;
+
+/* USER CODE BEGIN PV */
+uint16_t adc_buffer[N];
[…]

### 2024-08-14 paper/main.tex
Abstract done

@@
 
-\title{Decoding the Amplitude of the DCF77 Longwave Time Signal by using the Goertzel Algorithm}
+\title{Decoding the Amplitude-Modulated Part the DCF77 Longwave Time Signal by using the Goertzel Algorithm}
 
@@
 \begin{abstract}
-This document is a model and instructions for \LaTeX.
-This and the IEEEtran.cls file define the components of your paper [title, text, heads, etc.]. *CRITICAL: Do Not Use Symbols, Special Characters, Footnotes, 
-or Math in Paper Title or Abstract.
+    The DCF77, a long wave time signal transmitter that is located near Frankfurt am Main in Germany, is the primary source of time information for
+    radio-controlled clocks in Europe. Its signal consists of a phase and an amplitude-modulated part, both containing the time information.
+    Devices that use the signal usually consist of an amplitude modulation long wave receiver, often realized by using a dedicated integrated circuit, and an
+    application processor. In this paper, a novel approach for the demodulation of the amplitude-modulated part of the signal, without the need for specialized
+    analog cicruitry and only a minimal amount of simple hardware components, is presented.
+    This is done by utilizing direct-sampling software-defined radio techniques together with leveraging the efficiency of the Goertzel algorithm.
+    As a result, the presented approach removes the need for most of the usually employed analog circuitry, leaving only a front-end amplifier, and
+    effectively proposes a new type of design where the receiver is implemented inside the application processor.
+    The employed lightweight algorithms keep it realizable on a system with limited resources, which is shown in an example implementation on a Arm Cortex-M3 microcontroller. 
 \end{abstract}
@@
 \begin{IEEEkeywords}
-DCF77, Goertzel, Time Signal, Decoding, Longwave
+DCF77, SDR, Goertzel, DSP, Time Signal
 \end{IEEEkeywords}
@@
 \section{Introduction}
+    %End-user devices usually make use of the amplitude-modulated part of this signal by utilizing specialized ICs
+    %together with big ferrite-rod antennas for obtaining the time signal. This signal then needs further hardware, often in form of microcontrollers,
+    %to be used in the application. With increasing availability
+
+    %The demodulation and decoding of the amplitude and phase-modulated signal in the end-user devices
+    %is usually done by using specialized ICs together with ferrite-rod antennas. With increasing availability of cheap In this paper, a n
+
 This document is a model and instructions for \LaTeX.

### 2024-08-16 paper/main.tex
Added TikZ picture of spectrum with aliasing

@@
 \usepackage{xcolor}
+\usepackage{tikz}
+\usetikzlibrary{calc,patterns,patterns.meta}
+\usepackage{siunitx}  
+\sisetup{locale = US}
 \def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
@@
     Devices that use the signal usually consist of an amplitude modulation long wave receiver, often realized by using a dedicated integrated circuit, and an
-    application processor. In this paper, a novel approach for the demodulation of the amplitude-modulated part of the signal, without the need for specialized
+    application processor. In this paper, an alternative approach for the demodulation of the amplitude-modulated part of the signal, without the need for specialized
     analog cicruitry and only a minimal amount of simple hardware components, is presented.
@@
 \begin{IEEEkeywords}
-DCF77, SDR, Goertzel, DSP, Time Signal
+    DCF77, Goertzel, Digital Signal Processing, Time Signal, Software Defined Radio
 \end{IEEEkeywords}
@@
 \section{Introduction}
+\begin{figure}[!h]
+    \centering
+    \resizebox{0.48\textwidth}{!}{
+        \begin{tikzpicture}
+            \clip (-11.5,-1) rectangle + (23,5); %Clipping: where to start, shape and size
+
+            \coordinate (fc) at (7.75,0);
+            \coordinate (fs) at (2.4,0);
+
+            %Axes
+            \draw[->, very thick] (-11,0) -- (11,0) node[right] {f};
+            \draw[->, very thick] (0,-1) -- (0,3) node[above] {Amplitude};
+
+            %DCF77 at f_c
+            \draw[thick, pattern={Dots[angle=45,distance={1.25pt/sqrt(2)}]}, pattern color=blue]
+            ($(fc) + (-0.12,0)$) -- % Left line start
+            ++(0,1) -- %Left line up
+            ++(0.24,0.5) -- %Roof
+            ++(0,-1.5) -- %Right line down
+            cycle; % Close the shape
+            \draw[very thick] ($(fc) + (0, -0.2)$) -- ++(0, 0.4); %Line x-axis
+            \node at ($(fc) + (0, -0.8)$) {$f_{c}$}; %Index x-axis
+            \draw[<->] ($(fc) + (-0.12,1.75)$) -- ++(0.24,0) node[midway, above] {$B$}; %Bandwidth
+
+            %DCF77 at f_c
+            \draw[thick, pattern={Dots[angle=45,distance={1.25pt/sqrt(2)}]}, pattern color=blue]
+            ($-1*(fc) + (-0.12,0)$) -- % Left line start
+            ++(0,1.5) -- %Left line up
+            ++(0.24,-0.5) -- %Roof
+            ++(0,-1) -- %Right line down
+            cycle; % Close the shape
+            \draw[very thick] ($-1*(fc) + (0, -0.2)$) -- ++(0, 0.4); %Line x-axis
+            \node at ($-1*(fc) + (0, -0.8)$) {$-f_{c}$}; %Index x-axis
+            \draw[<->] ($-1*(fc) + (-0.12,1.75)$) -- ++(0.24,0) node[midway, above] {$B$}; %Bandwidth
+
+            %f_s and their multiples
+            \foreach \x in {-3,-2,-1,1,2,3}{
+                \draw[-> , thick] ($\x*(fs)$) -- ++(0,1.5);
+                \draw[very thick] ($\x*(fs) + (0,-0.2)$) -- ++(0,0.4);
+                \node at ($\x*(fs) + (0,-0.4)$) {$\x f_{s}$};
+
+                \draw[thick]
+                ($(fc) + (-0.12,0) + \x*(fs)$) -- % Left line start
+                ++(0,1) -- %Left line up
+                ++(0.24,0.5) -- %Roof
+                ++(0,-1.5) -- %Right line down
+                cycle; % Close the shape
+                \draw[very thick] ($(fc) + (0, -0.2) + \x*(fs)$) -- ++(0, 0.4); %Line x-axis
+                \node at ($(fc) + (0, -0.8) + \x*(fs)$) {$f_{c} \pgfmathprintnumber[print sign]{\x} f_{s}$}; %Index x-axis
+
+                %DCF77 at -f_c
+                \draw[thick]
+                ($-1*(fc) + (-0.12,0) + \x*(fs)$) -- % Left line start
+                ++(0,1.5) -- %Left line up
+                ++(0.24,-0.5) -- %Roof
+                ++(0,-1) -- %Right line down
+                cycle; % Close the shape
+                \draw[very thick] ($-1*(fc) + (0, -0.2) + \x*(fs)$) -- ++(0, 0.4); %Line x-axis
+                \node at ($-1*(fc) + (0, -0.8) + \x*(fs)$) {$-f_{c} \pgfmathprintnumber[print sign]{\x} f_{s}$}; %Index x-axis
+            };
+        \end{tikzpicture}
+    } 
+\end{figure}
+
 %End-user devices usually make use of the amplitude-modulated part of this signal by utilizing specialized ICs

### 2024-08-16 paper/main.tex
Introduction done

@@
 \usepackage{siunitx}  
+\usepackage{placeins}
 \sisetup{locale = US}
@@
     This is done by utilizing direct-sampling software-defined radio techniques together with leveraging the efficiency of the Goertzel algorithm.
-    As a result, the presented approach removes the need for most of the usually employed analog circuitry, leaving only a front-end amplifier, and
+    As a result, the presented approach removes the need for most of the usually employed analog circuitry, leaving only a front-end amplifier, and therefore
     effectively proposes a new type of design where the receiver is implemented inside the application processor.
@@
 \section{Introduction}
+Radio controlled clocks are very popular because they dont require periodical re-adjustment in comparison to common mechanical or quartz-powered clocks.
+Instead, the information about the current time is obtained from a RF-signal that is transmitted by an official authority that ensures its availability and
+correctness.
+The probably most important time signal in Europe is transmitted by the station DCF77 from Mainflingen, a city in Germany that is close to Frankfurt am Main.
+The station is operated by a private company that is commissioned by the Physikalisch-Technische Bundesanstalt (PTB) which also supplies the current time information,
+generated by two caesium clocks and two caesium fountains. Its operating frequency lies in the long wave area at \SI{77.5}{\kilo\hertz} and the time signal
+uses simple modulation techniques (amplitude and phase-modulation) and transmits with \SI{100}{\kilo\watt} Effective Isotropic Radiated Power (EIRP) to enable the reception of the signal in relatively close distances (up to \SI{2000}{\kilo\meter})
+with simple technical equipment \cite{b2}.
+\begin{figure}[!htbp]
+    \centerline{\includegraphics[width=0.3\textwidth]{img/dcf77_range.jpg}}
+    \caption{Coverage of the DCF77 signal. Adapted from \cite{b1}}
+    \label{fig:upchirp}
+\end{figure}
+\FloatBarrier
+End-user devices usually make use of the amplitude-modulated part of the signal by using an amplitude modulation receiver, often a by employing specialized integrated circuit,
+together with a rather big ferrite-rod antenna to obtain the time signal.
+This time signal then needs further hardware, often in form of a microcontroller used as the applicaton processor, to decode and retrieve the actual time information.
+With the increasing availability of computation power and Digital Signal Processing (DSP) capabilities inside cheap mixed-signal microcontrollers, which are already used
+to process the time information, the idea to replace to replace the analog receiver portion with a Software Defined Radio (SDR) is more or less obvious.
+Moving the receiver into the application processor would allow for a simpler hardware design by shrinking down the complexity and the parts count of the
+external analog circuitry. In fact, only a tuned antenna with a basic pre-amplifier is needed.
+
+In this paper, a straightfoward principle for designing a lightweight receiver for the DCF77, based on SDR-techniques, is presented.
+After taking a look at the structure of the DCF77 signal, the theoretical operation principle of the receiver is explained and shown in a MATLAB simulation.
+To further underline the simplicity and the possibility to implement the principle on a system with limited resources, a demonstration on a Arm Cortex-M3 microcontroller
+is shown.
+
 \begin{figure}[!h]
@@
 \end{figure}
-
-%End-user devices usually make use of the amplitude-modulated part of this signal by utilizing specialized ICs
-    %together with big ferrite-rod antennas for obtaining the time signal. This signal then needs further hardware, often in form of microcontrollers,
-    %to be used in the application. With increasing availability
-
-    %The demodulation and decoding of the amplitude and phase-modulated signal in the end-user devices
-    %is usually done by using specialized ICs together with ferrite-rod antennas. With increasing availability of cheap In this paper, a n
-
-This document is a model and instructions for \LaTeX.
-Please observe the conference page limits.
-For more information about how to become an IEEE Conference author or how to write your paper, please visit   IEEE Conference Author Center website: https://conferences.ieeeauthorcenter.ieee.org/.
 
@@
 \begin{thebibliography}{00}
-\bibitem{b1} G.
-Eason, B.
-Noble, and I.
-N.
-Sneddon, ``On certain integrals of Lipschitz-Hankel type involving products of Bessel functions,'' Phil.
-Trans.
-Roy.
-Soc.
-London, vol.
-A247, pp.
-529--551, April 1955.
-\bibitem{b2} J. Clerk Maxwell, A Treatise on Electricity and Magnetism, 3rd ed., vol. 2. Oxford: Clarendon, 1892, pp.68--73.
+\bibitem{b1} -, ``DCF77,'' 2023, Wikipedia entry. [Online]. Available: https://de.wikipedia.org/wiki/DCF77
+\bibitem{b2} D.
+Priester and P.
+Hetzel and A.
+Bauch, ``Zeit- und Normalfrequenzverbreitung mit DCF77,'' PTB Mitteilungen, 2004, [Online].
+Available: https://www.ptb.de/cms/fileadmin/internet/fachabteilungen/abteilung\_4/4.4\_zeit\_und\_frequenz/4.42/dcf77.pdf
+
 \bibitem{b3} I. S. Jacobs and C. P. Bean, ``Fine particles, thin films and exchange anisotropy,'' in Magnetism, vol. III, G. T. Rado and H. Suhl, Eds. New York: Academic, 1963, pp. 271--350.
@@
 \bibitem{b7} M. Young, The Technical Writer's Handbook. Mill Valley, CA: University Science, 1989.
-\bibitem{b8} D. P. Kingma and M. Welling, ``Auto-encoding variational Bayes,'' 2013, arXiv:1312.6114. [Online]. Available: https://arxiv.org/abs/1312.6114
+
 \bibitem{b9} S. Liu, ``Wi-Fi Energy Detection Testbed (12MTC),'' 2023, gitHub repository. [Online]. Available: https://github.com/liustone99/Wi-Fi-Energy-Detection-Testbed-12MTC

### 2024-08-16 paper/main.tex
First part of the description of the DCF77 signal done

@@
 
+\section{The DCF77 signal}
+The DCF77 station operates in the long wave area at a frequency of \SI{77.5}{\kilo\hertz}.
+Its operation started with transmitting a frequency standard in 1959.
+In 1973, the transmission of the current time information was added to the signal by using amplitude modulation.
+To allow a reception under more challenging conditions and with a higher resolution and accuracy, the same time information is also added to the signal since 1983 by using phase-modulation \cite{b3}.
+The two different parts of the signal that result out of the parallel amplitude and the phase-modulation can be used for different use-cases that are separated by the
+requirements regarding the resolution, accuracy, and the reliability of the obtained time information. 
+Whereas the amplitude-modulated part is mainly used for general-purpose time application with low resolution requirements, the phase-modulated part is usually used
+for specialized applications that require a higher resolution, accuracy, and reliability.
+Although being considered as low in comparison to what is achievable by analyzing the phase-modulated part, the usually observed accuracy uncertainity when using the
+amplitude-modulated part it is still well below \SI{1}{\second}, being \SI{100}{\milli\second} \cite{b2}.
+When using the phase-modulated part, a standard deviation of \SIrange{\pm 2}{\pm 22}{\micro\second} from the atomic clock to the receving device can be observed \cite{b4}.
+\par
+As the amplitude-modulated part allows simplistic receiver designs through its straightfoward modulation scheme, it is used in the principle presented in this paper
+and a focus is put on explaining this part of the DCF77 signal.
+
+\section{Principle of a DCF77 receiver}
 \begin{figure}[!h]
@@
 \begin{figure}[htbp]
-\centerline{\includegraphics{fig1.png}}
+\centerline{\includegraphics{img/fig1.png}}
 \caption{Example of a figure caption.}
@@
 Available: https://www.ptb.de/cms/fileadmin/internet/fachabteilungen/abteilung\_4/4.4\_zeit\_und\_frequenz/4.42/dcf77.pdf
+\bibitem{b3} D.
+Priester and P.
+Hetzel and A.
+Bauch, ``Zeit- und Normalfrequenzverbreitung mit DCF77: 1959-2009 und darüber hinaus,'' PTB Mitteilungen, 2009, [Online].
+Available: https://www.ptb.de/cms/fileadmin/internet/fachabteilungen/abteilung\_4/4.4\_zeit\_und\_frequenz/pdf/2009\_Bauch\_PTBM\_\_DCF77.pdf
+\bibitem{b4} P.
+Hetzel, ``Time dissemination via the LF transmitter DCF77 using a pseudo-random phase-shift keying of the carrier,'' PTB Braunschweig, 1988, [Online].
+Available: https://www.ptb.de/cms/fileadmin/internet/fachabteilungen/abteilung\_4/4.4\_zeit\_und\_frequenz/pdf/5\_1988\_Hetzel\_-\_Proc\_EFTF\_88.pdf
 
-\bibitem{b3} I. S. Jacobs and C. P. Bean, ``Fine particles, thin films and exchange anisotropy,'' in Magnetism, vol. III, G. T. Rado and H. Suhl, Eds. New York: Academic, 1963, pp. 271--350.
-\bibitem{b4} K. Elissa, ``Title of paper if known,'' unpublished.
-\bibitem{b5} R. Nicole, ``Title of paper with only first word capitalized,'' J. Name Stand. Abbrev., in press.
-\bibitem{b6} Y.
+%\bibitem{b3} I. S. Jacobs and C. P. Bean, ``Fine particles, thin films and exchange anisotropy,'' in Magnetism, vol. III, G. T. Rado and H. Suhl, Eds. New York: Academic, 1963, pp. 271--350.
+%\bibitem{b4} K. Elissa, ``Title of paper if known,'' unpublished.
+%\bibitem{b5} R. Nicole, ``Title of paper with only first word capitalized,'' J. Name Stand. Abbrev., in press.
+%\bibitem{b6} Y.
 Yorozu, M.
@@
 301, 1982].
-\bibitem{b7} M. Young, The Technical Writer's Handbook. Mill Valley, CA: University Science, 1989.
-
-\bibitem{b9} S. Liu, ``Wi-Fi Energy Detection Testbed (12MTC),'' 2023, gitHub repository. [Online]. Available: https://github.com/liustone99/Wi-Fi-Energy-Detection-Testbed-12MTC
-\bibitem{b10} ``Treatment episode data set: discharges (TEDS-D): concatenated, 2006 to 2009.'' U.S.
+%\bibitem{b7} M. Young, The Technical Writer's Handbook. Mill Valley, CA: University Science, 1989.
+%\bibitem{b9} S. Liu, ``Wi-Fi Energy Detection Testbed (12MTC),'' 2023, gitHub repository. [Online]. Available: https://github.com/liustone99/Wi-Fi-Energy-Detection-Testbed-12MTC
+%\bibitem{b10} ``Treatment episode data set: discharges (TEDS-D): concatenated, 2006 to 2009.'' U.S.
 Department of Health and Human Services, Substance Abuse and Mental Health Services Administration, Office of Applied Studies, August, 2013, DOI:10.3886/ICPSR30122.v2
-\bibitem{b11} K. Eves and J. Valasek, ``Adaptive control for singularly perturbed systems examples,'' Code Ocean, Aug. 2023. [Online]. Available: https://codeocean.com/capsule/4989235/tree
+%\bibitem{b11} K. Eves and J. Valasek, ``Adaptive control for singularly perturbed systems examples,'' Code Ocean, Aug. 2023. [Online]. Available: https://codeocean.com/capsule/4989235/tree
 \end{thebibliography}

### 2024-08-16 paper/main.tex
DCF77 signal part finished.

@@
 \usepackage{xcolor}
+\usepackage{placeins}
+
 \usepackage{tikz}
 \usetikzlibrary{calc,patterns,patterns.meta}
+
 \usepackage{siunitx} 
-\usepackage{placeins}
 \sisetup{locale = US}
+\DeclareSIUnit{\Bit}{Bit}
+
 \def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
     T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
+
     \begin{document}
@@
     \caption{Coverage of the DCF77 signal. Adapted from \cite{b1}}
-    \label{fig:upchirp}
+    \label{fig:dcf77_range}
 \end{figure}
@@
 As the amplitude-modulated part allows simplistic receiver designs through its straightfoward modulation scheme, it is used in the principle presented in this paper
-and a focus is put on explaining this part of the DCF77 signal.
+and therefore a focus is put on explaining this part of the DCF77 signal.
+The time information, represented as a series of binary symbols, is modulated onto the carrier with a frequency of \SI{77.5}{\kilo\hertz} by using
+Amplitude-Shift Keying (ASK). Every symbol has the duration of exactly \SI{1}{\second}, with a part that is either \SI{100}{\milli\second} or \SI{200}{\milli\second}
+long where it has a value to zero.
+This the duration of this "gap" is used to encode respectively a 0 or a 1 and effectively switches the strength of the carrier between \SI{15}{\percent} and \SI{100}{\percent} \cite{b5}.
+\begin{figure}[htbp]
+    \centerline{\includegraphics[width=0.45\textwidth]{img/dcf77_symbol_encoding.png}}
+    \caption{Symbol encoding of the DCF77 signal. From \cite{b1}}
+    \label{fig:dcf77_symbol_encoding}
+\end{figure}
+\FloatBarrier\noindent
+To allow the detection of a new minute, the gap is left out between the last (59) second of the ongoing and the first (0) second of the next minute.
+By using this scheme, a dataframe consisting out \SI{59}{\Bit}, starting at second one, can be transmitted every minute.
+Bit \SIrange{0}{19}{} are used to send encrypted weather data, to notify the PTB in case of errors in the transmitter, to announce an upcoming
+switch to or from Daylight Saving Time (DST), to show if DST is currently enabled or not, and to announce an upcoming leap second \cite{b5}.
+As the decryption of the weather date requires a specialized third-party integrated circuit and the notification bit is only important for the PTB, these parts
+of the frame are discarded by most applications.
+The leftover Bits \SIrange{20}{58}{} are used to represent the current time and date in Binary Coded Decimal (BCD) format, including parity bits for recognizing errors.
+\begin{figure}[htbp]
+    \centerline{\includegraphics[width=0.35\textwidth]{img/dcf77_frame_encoding.jpg}}
+    \caption{Data frame encoding of the DCF77 signal. From \cite{b5}}
+    \label{fig:dcf77_data_encoding}
+\end{figure}
+\FloatBarrier\noindent
+This means that a receiver needs to run at least for \SI{39}{\second} after powerup to receive one whole block containing the current time information.
+In reality, this period is usually longer because the receiver needs to adapt to the current receiving conditions. 
+These conditions underly a lot of influences, including temporary fading, electromagnetic noise from the close environment or varying signal strengths
+during different times of the day.
 
 \section{Principle of a DCF77 receiver}
-\begin{figure}[!h]
+\begin{figure*}[!htbp]
     \centering
-    \resizebox{0.48\textwidth}{!}{
+    \resizebox{0.9\textwidth}{!}{
         \begin{tikzpicture}
@@
     } 
-\end{figure}
+\end{figure*}
 
@@
 
-\begin{figure}[htbp]
-\centerline{\includegraphics{img/fig1.png}}
-\caption{Example of a figure caption.}
-\label{fig}
-\end{figure}
-
 Figure Labels: Use 8 point Times New Roman for Figure labels. Use words 
@@
 \begin{thebibliography}{00}
-\bibitem{b1} -, ``DCF77,'' 2023, Wikipedia entry. [Online]. Available: https://de.wikipedia.org/wiki/DCF77
+\bibitem{b1} -, ``DCF77,'' 2024, Wikipedia entry. [Online]. Available: https://de.wikipedia.org/wiki/DCF77
 \bibitem{b2} D.
@@
 Available: https://www.ptb.de/cms/fileadmin/internet/fachabteilungen/abteilung\_4/4.4\_zeit\_und\_frequenz/pdf/5\_1988\_Hetzel\_-\_Proc\_EFTF\_88.pdf
-
+\bibitem{b5} -, ``DCF77 webpage,'' 2024, Official page of the PTB [Online]. Available: https://www.ptb.de/cms/en/ptb/fachabteilungen/abt4/fb-44/ag-442/dissemination-of-legal-time/dcf77.html
 %\bibitem{b3} I. S. Jacobs and C. P. Bean, ``Fine particles, thin films and exchange anisotropy,'' in Magnetism, vol. III, G. T. Rado and H. Suhl, Eds. New York: Academic, 1963, pp. 271--350.

### 2024-08-16 paper/main.tex
Added a TikZ picture of the structure of the receiver

@@
 \usepackage{tikz}
-\usetikzlibrary{calc,patterns,patterns.meta}
+\usetikzlibrary{calc, patterns, patterns.meta, shapes.geometric, arrows.meta, positioning, fit}
 
@@
 
-\section{Principle of a DCF77 receiver}
+\section{Principle of the receiver}
+To understand the principle of the receiver, it is compared to the common structure that is used in radio controlled clocks.
+\begin{figure}[htbp]
+    \centering
+    \resizebox{0.48\textwidth}{!}{
+        \begin{tikzpicture}
+            % Block styles
+            \tikzstyle{block} = [rectangle, draw, text width=4.5em, text centered, minimum width=6em, minimum height=4em]
+            \tikzstyle{block_dashed} = [rectangle, draw, text width=2em, text centered, minimum width=4em, minimum height=4em, dashed]
+            % Input and output
+            \begin{scope}[shift={(-3,0)}] % Adjust the position of the antenna
+                \coordinate (antenna) at (0,0);
+                \draw[thick] (0,0) -- (0,1); % Antenna pole
+                \draw[thick] (-0.25,1) -- (0,0.75); % Antenna horizontal line
+                \draw[thick] (0.25,1) -- (0,0.75); % Antenna horizontal line
+            \end{scope}
+            \node[block, right=of antenna, minimum width=4em, minimum height=4em] (bpf) {BPF};
+            \node[block, right=of bpf] (rfamp) {RF Amp};
+            \node[block, right=of rfamp] (adc) {ADC};
+            \node[block, below=of adc] (timer) {Timer};
+            \node[block, right=of adc] (goertzel) {Goertzel Algorithm};
+            \node[block, right=of goertzel] (det) {Detector};
+            % Connections
+            \draw[thick] (antenna) -- (bpf);
+            \draw[->] (bpf) -- (rfamp); % Connection from antenna to RF amplifier
+            \draw[->] (rfamp) -- (adc);
+            \draw[->] (timer) -- (adc);
+            \draw[->] (adc) -- (goertzel);
+            \draw[->] (goertzel) -- (det);
+
+            \node[draw, dashed, fit={(antenna) (bpf)}, inner sep=12pt] (tank_circuit) {};
+            \node[below=0.5em of tank_circuit, align=center] {Tuned Tank Circuit};
+        \end{tikzpicture}
+    }
+\end{figure}
+\FloatBarrier\noindent
+Test
+
 \begin{figure*}[!htbp]
@@
 
-\vspace{12pt}
-\color{red}
-IEEE conference templates contain guidance text for composing and formatting conference papers.
-Please ensure that all template text is removed from your conference paper prior to submission to the conference.
-Failure to remove the template text from your paper may result in your paper not being published.
-
 \end{document}

### 2024-08-18 paper/main.tex
Progress in explaining the structure of the receiver

@@
 \usetikzlibrary{calc, patterns, patterns.meta, shapes.geometric, arrows.meta, positioning, fit}
+
+\usepackage{ifthen}
 
@@
 As the amplitude-modulated part allows simplistic receiver designs through its straightfoward modulation scheme, it is used in the principle presented in this paper
-and therefore a focus is put on explaining this part of the DCF77 signal.
+and therefore a focus is put on explaining this part of the DCF77 signal. The following explainations in this paper therefore refer explicitly to the amplitude-modulated part.
 The time information, represented as a series of binary symbols, is modulated onto the carrier with a frequency of \SI{77.5}{\kilo\hertz} by using
@@
 \section{Principle of the receiver}
-To understand the principle of the receiver, it is compared to the common structure that is used in radio controlled clocks.
+As the seen in the description of the DCF77 signal, retrieving the the binary time signal from the amplitude-modulated part is more or less trivial.
+Conventional applications execute this task by using analog receiving circuits, usually by using a simple amplitude modulation receiver together with a
+tuned ferrite-rod antenna, acting as a Bandpass Filter (BPF), to filter out the irrelevant part of the spectrum. 
+Moving the receiver into the digital domain allows for more advanced techniques to retrieve this binary time signal, rather than demodulating the signal with a
+diode-detector inside the amplitude modulation receiver.
+Because the information is contained only in the amplitude of the signal, and therefore inside the signal strength at the receiver, it can also be obtained by doing a
+continuous analysis of the spectrum at the carrier's frequency of \SI{77.5}{\kilo\hertz}.
+\subsection{The Goertzel Algorithm}
+The standard approach to analyze a spectrum in the digital domain after sampling is the well-known Discrete Fourier Transform (DFT), implemented by using
+the Fast Fourier Transform (FFT). This yields an analysis of the complete spectrum, producing $\frac{N}{2} + 1$ relevant results for equally distributed frequencies
+("frequency bins") within range from \SI{0}{\hertz} to $\frac{f_{s}}{2}$ where $N$ is the number of samples and $f_{s}$ the sampling frequency \cite{b6}.
+The signal strength, and therefore the binary time signal of the amplitude-modulated part can then be examined by observing the value of the curresponding frequency bin
+over time. Because of only one frequency bin being relevant, it is obvious that a full FFT produces a lot of overhead and redundant calculation operations in this use-case. 
+This overhead can be avoided by using the Goertzel algorithm instead of the FFT, which is able to calculate the value of one specific frequency bin with a smaller
+amount of needed calculations.
+It was invented in 1958 by Gerald Goertzel and since then most commonly used in the detection tones employed in Dual-tone Multi-frequency (DTMF) signaling \cite{b7}.
+The working principle of the algorithm can be percieved as a second-order Infinite Impulse Response (IIR) filter where the results $y[n-1]$ and $y[n-2]$ of the output
+are stored in states $Q_{1}$ and $Q_{2}$, so they are still available after the execution of the filter.
+\begin{equation}
+    y[n] = x[n] + 2 \cdot cos(\omega_{g}) \cdot y[n-1] - y[n-2]
+\end{equation}
+From these equations, the following structure can be derived:
+\begin{figure}[htbp]
+    \centering
+    \resizebox{0.4\textwidth}{!}{
+        \begin{tikzpicture}[auto, node distance=2cm]
+            %Defining a cross set for the multiplication elements
+            \tikzset{cross/.style={path picture={ 
+            \draw[black]
+            (path picture bounding box.south east) -- (path picture bounding box.north west) (path picture bounding box.south west) -- (path picture bounding box.north east);
+            }}}
+
+          % Define block styles
+            \tikzstyle{delay} = [draw, rectangle, minimum height=2em, minimum width=2em]
+            \tikzstyle{sum} = [draw, circle, minimum size=2em, node distance=1.5cm]
+            \tikzstyle{mult} = [draw, circle, minimum size=2em, node distance=1.5cm, cross]
+            \tikzstyle{state} = [draw, rectangle, rounded corners, minimum height=2em, minimum width=2em]
+
+            % Nodes
+            \node at (-2, 0) (x) {$x[n]$};
+            \node[sum] at (0,0) (sum1) {+};
+            \node[sum] at (0,-2) (sum2) {+};
+            \node[mult] at (2,-2) (mult1) {};
+            \node[mult] at (2,-4) (mult2) {};
+            \node[delay] at (4,-1) (del1) {$z^{-1}$};
+            \node[delay] at (4,-3) (del2) {$z^{-1}$};
+            \node[state] at (6,-2) (st1) {$Q_{1}$};
+            \node[state] at (6,-4) (st2) {$Q_{2}$};
+            \node at (6, 0) (y) {$y[n]$};
+
+            \draw[->] (x.east) -- (sum1.west);
+            \draw[->] (sum1.east) -- (y.west);
+            \draw[->] (sum2.north) -- (sum1.south);
+            \draw[->] (mult1.west) -- (sum2.east);
+            \draw[->] (mult2.west) -- (0, -4) -- (sum2.south);
+            \draw[->] (4, 0) -- (del1.north);
+            \draw[->] (del1.south) -- (del2.north);
+            \draw[->] (del2.south) -- (4,-4) -- (mult2.east);
+            \draw[->] (4,-2) -- (mult1.east);
+            \draw[->] (2, -1.25) -- (mult1.north);
+            \draw[->] (2, -3.25) -- (mult2.north);
+            \draw[->] (4, -2) -- (st1.west);
+            \draw[->] (4, -4) -- (st2.west);
+            \node at (2, -1) {$2 \cdot cos(\omega_{g})$};
+            \node at (2, -3) {$-1$};
+            \node[draw, shape=circle, fill=black, scale=0.3] at (4,0) {};
+            \node[draw, shape=circle, fill=black, scale=0.3] at (4,-2) {};
+            \node[draw, shape=circle, fill=black, scale=0.3] at (4,-4) {};
+        \end{tikzpicture}
+    }
+\end{figure}
+\FloatBarrier\noindent
+
+The constant $2 \cdot cos(\omega_{g})$ is computed before the execution.
+It is calculated based on $\omega_{g}$ and defines the frequency to be analyzed, dependent on the sampling frequency $f_{s}$, the
+frequency to analyze $f_{a}$ and the number of input samples $N$.
+\begin{equation}
+    k = \left\lfloor \frac{N \cdot f_{a}}{f_{s}} \right\rceil
+\end{equation}
+\begin{equation}
+    w_g = \frac{2\pi \cdot k}{N}
+\end{equation}
+
 \begin{figure}[htbp]
@@
             \node[draw, dashed, fit={(antenna) (bpf)}, inner sep=12pt] (tank_circuit) {};
-            \node[below=0.5em of tank_circuit, align=center] {Tuned Tank Circuit};
+            \node[below=0.3em of tank_circuit, align=center] {Tuned ferrite-rod antenna};
+
+            \node[draw, dashed, fit={(adc) (timer) (goertzel) (det)}, inner sep=12pt] (microcontroller) {};
+            \node[below=0.3em of microcontroller, align=center] {Microcontroller};
         \end{tikzpicture}
@@
 
-            %f_s and their multiples
+            %f_s their result of the convulutions
             \foreach \x in {-3,-2,-1,1,2,3}{
@@
                 \draw[very thick] ($(fc) + (0, -0.2) + \x*(fs)$) -- ++(0, 0.4); %Line x-axis
+                \ifthenelse{\x = -3}{
+                    \node at ($(fc) + (0.3, -0.8) + \x*(fs)$) {$f_{c} \pgfmathprintnumber[print sign]{\x} f_{s}$}; %Index x-axis
+                }{
                     \node at ($(fc) + (0, -0.8) + \x*(fs)$) {$f_{c} \pgfmathprintnumber[print sign]{\x} f_{s}$}; %Index x-axis
+                }
 
@@
                 \draw[very thick] ($-1*(fc) + (0, -0.2) + \x*(fs)$) -- ++(0, 0.4); %Line x-axis
+                \ifthenelse{\x = 3}{
+                    \node at ($-1*(fc) + (-0.3, -0.8) + \x*(fs)$) {$-f_{c} \pgfmathprintnumber[print sign]{\x} f_{s}$}; %Index x-axis
+                }{
                     \node at ($-1*(fc) + (0, -0.8) + \x*(fs)$) {$-f_{c} \pgfmathprintnumber[print sign]{\x} f_{s}$}; %Index x-axis
+                }
             };
@@
 \bibitem{b5} -, ``DCF77 webpage,'' 2024, Official page of the PTB [Online]. Available: https://www.ptb.de/cms/en/ptb/fachabteilungen/abt4/fb-44/ag-442/dissemination-of-legal-time/dcf77.html
+\bibitem{b6} R. G. Lyons, ``Understanding Digital Signal Processing,'' Third Edition, Prentice Hall, 2010.
+\bibitem{b7} -, ``Goertzel algorithm,'' 2024, Wikipedia entry. [Online]. Available: https://en.wikipedia.org/wiki/Goertzel\_algorithm
 %\bibitem{b3} I. S. Jacobs and C. P. Bean, ``Fine particles, thin films and exchange anisotropy,'' in Magnetism, vol. III, G. T. Rado and H. Suhl, Eds. New York: Academic, 1963, pp. 271--350.

### 2024-08-19 paper/main.tex
Goertzel algorithm description done. Rearrangend some parts

@@
 \section{Principle of the receiver}
-As the seen in the description of the DCF77 signal, retrieving the the binary time signal from the amplitude-modulated part is more or less trivial.
+As the seen in the description of the DCF77 signal, retrieving back the binary time signal from the amplitude-modulated part is more or less trivial.
 Conventional applications execute this task by using analog receiving circuits, usually by using a simple amplitude modulation receiver together with a
@@
 Moving the receiver into the digital domain allows for more advanced techniques to retrieve this binary time signal, rather than demodulating the signal with a
-diode-detector inside the amplitude modulation receiver.
+diode detector inside the amplitude modulation receiver.
 Because the information is contained only in the amplitude of the signal, and therefore inside the signal strength at the receiver, it can also be obtained by doing a
 continuous analysis of the spectrum at the carrier's frequency of \SI{77.5}{\kilo\hertz}.
+This task will be carried out by using the Goertzel algorithm, which is presented later.
+The structure of the whole receiver simplifies to only two external hardware parts and four internal software parts.
+
+\begin{figure}[!htbp]
+    \centering
+    \resizebox{0.48\textwidth}{!}{
+        \begin{tikzpicture}
+            % Block styles
+            \tikzstyle{block} = [rectangle, draw, text width=4.5em, text centered, minimum width=6em, minimum height=4em]
+            \tikzstyle{block_dashed} = [rectangle, draw, text width=2em, text centered, minimum width=4em, minimum height=4em, dashed]
+            % Input and output
+            \begin{scope}[shift={(-3,0)}] % Adjust the position of the antenna
+                \coordinate (antenna) at (0,0);
+                \draw[thick] (0,0) -- (0,1); % Antenna pole
+                \draw[thick] (-0.25,1) -- (0,0.75); % Antenna horizontal line
+                \draw[thick] (0.25,1) -- (0,0.75); % Antenna horizontal line
+            \end{scope}
+            \node[block, right=of antenna, minimum width=4em, minimum height=4em] (bpf) {BPF};
+            \node[block, right=of bpf] (rfamp) {RF Amp};
+            \node[block, right=of rfamp] (adc) {ADC};
+            \node[block, below=of adc] (timer) {Timer};
+            \node[block, right=of adc] (goertzel) {Goertzel Algorithm};
+            \node[block, right=of goertzel] (det) {Detector};
+            % Connections
+            \draw[thick] (antenna) -- (bpf);
+            \draw[->] (bpf) -- (rfamp); % Connection from antenna to RF amplifier
+            \draw[->] (rfamp) -- (adc);
+            \draw[->] (timer) -- (adc);
+            \draw[->] (adc) -- (goertzel);
+            \draw[->] (goertzel) -- (det);
+
+            \node[draw, dashed, fit={(antenna) (bpf)}, inner sep=12pt] (tank_circuit) {};
+            \node[below=0.3em of tank_circuit, align=center] {Tuned ferrite-rod antenna};
+
+            \node[draw, dashed, fit={(adc) (timer) (goertzel) (det)}, inner sep=12pt] (microcontroller) {};
+            \node[below=0.3em of microcontroller, align=center] {Microcontroller};
+        \end{tikzpicture}
+    }
+\end{figure}
+\FloatBarrier\noindent
+The tuned ferrite-rod antenna is kept to provide a good selectivity
+
 \subsection{The Goertzel Algorithm}
@@
 ("frequency bins") within range from \SI{0}{\hertz} to $\frac{f_{s}}{2}$ where $N$ is the number of samples and $f_{s}$ the sampling frequency \cite{b6}.
-The signal strength, and therefore the binary time signal of the amplitude-modulated part can then be examined by observing the value of the curresponding frequency bin
+The signal strength, and therefore the binary time signal of the amplitude-modulated part, can then be examined by observing the value of the curresponding frequency bin
 over time. Because of only one frequency bin being relevant, it is obvious that a full FFT produces a lot of overhead and redundant calculation operations in this use-case. 
@@
 amount of needed calculations.
-It was invented in 1958 by Gerald Goertzel and since then most commonly used in the detection tones employed in Dual-tone Multi-frequency (DTMF) signaling \cite{b7}.
-The working principle of the algorithm can be percieved as a second-order Infinite Impulse Response (IIR) filter where the results $y[n-1]$ and $y[n-2]$ of the output
-are stored in states $Q_{1}$ and $Q_{2}$, so they are still available after the execution of the filter.
+It was invented in 1958 by Gerald Goertzel and since then is most commonly used in the detection tones employed in Dual-tone Multi-frequency (DTMF) signaling \cite{b7}.
+The working principle of the algorithm can be percieved as a second-order Infinite Impulse Response (IIR) filter where the results $y[n-1]$ and $y[n-2]$ of the output $y[n]$
+are stored in states $Q_{1}$ and $Q_{2}$, so they are still available after the execution of the filter:
 \begin{equation}
@@
 \end{equation}
-From these equations, the following structure can be derived:
-\begin{figure}[htbp]
+\begin{figure}[!htbp]
     \centering
@@
     }
+    \caption{IIR representation of the Goertzel algorithm without the final calculation of the squared magnitude}
+    \label{fig:goertzel_iir}
 \end{figure}
 \FloatBarrier\noindent
-
-The constant $2 \cdot cos(\omega_{g})$ is computed before the execution.
-It is calculated based on $\omega_{g}$ and defines the frequency to be analyzed, dependent on the sampling frequency $f_{s}$, the
-frequency to analyze $f_{a}$ and the number of input samples $N$.
+The system takes the input sequence $x[n]$ with length $N$ and is executed exactly $N$ times.
+After the execution, the squared magnitude of $f_{a}$, the frequency to be analyzed, inside $x[n]$ can be calculated using the two states $Q_{1}$ and $Q_{2}$:
+\begin{equation}
+    |X(f_{a})|^2 = Q_{1}^2 + Q_{2}^2 - Q_{1} \cdot Q_{2} \cdot 2 \cdot \cos(\omega_{g})
+\end{equation}
+The constant $2 \cdot cos(\omega_{g})$, often called the "Goertzel coefficient", is calculated before the execution and used to adapt the algorithm to the frequency to be analyzed.
+The Value of $\omega_{g}$ itself is calculated based on a integer number $k$ and $N$.
+The integer number $k$ is a rounded fraction based on $N$, the frequency to be analyzed $f_{a}$, and the the sampling frequency $f_{s}$.
 \begin{equation}
@@
 
-\begin{figure}[htbp]
-    \centering
-    \resizebox{0.48\textwidth}{!}{
-        \begin{tikzpicture}
-            % Block styles
-            \tikzstyle{block} = [rectangle, draw, text width=4.5em, text centered, minimum width=6em, minimum height=4em]
-            \tikzstyle{block_dashed} = [rectangle, draw, text width=2em, text centered, minimum width=4em, minimum height=4em, dashed]
-            % Input and output
-            \begin{scope}[shift={(-3,0)}] % Adjust the position of the antenna
-                \coordinate (antenna) at (0,0);
-                \draw[thick] (0,0) -- (0,1); % Antenna pole
-                \draw[thick] (-0.25,1) -- (0,0.75); % Antenna horizontal line
-                \draw[thick] (0.25,1) -- (0,0.75); % Antenna horizontal line
-            \end{scope}
-            \node[block, right=of antenna, minimum width=4em, minimum height=4em] (bpf) {BPF};
-            \node[block, right=of bpf] (rfamp) {RF Amp};
-            \node[block, right=of rfamp] (adc) {ADC};
-            \node[block, below=of adc] (timer) {Timer};
-            \node[block, right=of adc] (goertzel) {Goertzel Algorithm};
-            \node[block, right=of goertzel] (det) {Detector};
-            % Connections
-            \draw[thick] (antenna) -- (bpf);
-            \draw[->] (bpf) -- (rfamp); % Connection from antenna to RF amplifier
-            \draw[->] (rfamp) -- (adc);
-            \draw[->] (timer) -- (adc);
-            \draw[->] (adc) -- (goertzel);
-            \draw[->] (goertzel) -- (det);
-
-            \node[draw, dashed, fit={(antenna) (bpf)}, inner sep=12pt] (tank_circuit) {};
-            \node[below=0.3em of tank_circuit, align=center] {Tuned ferrite-rod antenna};
-
-            \node[draw, dashed, fit={(adc) (timer) (goertzel) (det)}, inner sep=12pt] (microcontroller) {};
-            \node[below=0.3em of microcontroller, align=center] {Microcontroller};
-        \end{tikzpicture}
-    }
-\end{figure}
-\FloatBarrier\noindent
-Test
+\par
+Just as with the conventional FFT, the amount of needed calculations for executing the Goertzel algorithm is based on the number of samples.
+In total, $N + 1$ multiplications and $2 \cdot N + 2$ additions are needed, which can be seen from the formulas for the IIR-part and the final calculation of the squared magnitude.
+For example, a length of $N = 512$ requires in $513$ multiplications and $1026$ additions to calculate the squared magnitude of the desired frequency.
+In comparison, the typical radix-2 FFT, needs $\frac{N}{2} \cdot \log_{2}(N)$ complex multiplications and $N \cdot \log_{2}(N)$ complex additions.
+With $N = 512$ this would result in $2034$ complex multiplications and $4608$ complex additions.
+\par
+With this simple example, it is already visible that the Goertzel algorithm can reduce the amount of needed resources compared to a full FFT, when only one or a small amount of frequency bins should be analyzed.
+It is therefore used to observe the DCF77 signal's amplitude over time by being executed periodically.
+As the gap of the encoded symbols is eiter \SI{100}{\milli\second} or \SI{200}{\milli\second} long, the duration of the analyzation set to \SI{10}{\milli\second} to provide a good tradeoff between resolution in time and a longest possible analyzation time
+to leverage the DFT gain.
+The result is then passed to a detector to obtain the binary time signal from the analyzed
+amplitude.
 

### 2024-08-19 paper/main.tex
Progress in Structure of the receiver.

@@
 \DeclareSIUnit{\Bit}{Bit}
+
+\usepackage{cuted}
+\usepackage{stfloats}
 
@@
 This task will be carried out by using the Goertzel algorithm, which is presented later.
-The structure of the whole receiver simplifies to only two external hardware parts and four internal software parts.
+The structure of the whole receiver then simplifies to only two external hardware parts
+(besides the application processor) and four internal software parts.
 
@@
             \node[draw, dashed, fit={(adc) (timer) (goertzel) (det)}, inner sep=12pt] (microcontroller) {};
-            \node[below=0.3em of microcontroller, align=center] {Microcontroller};
+            \node[below=0.3em of microcontroller, align=center] {Application Processor};
         \end{tikzpicture}
     }
+    \caption{Block diagram of the receiver}
+    \label{fig:block_diag_receiver}
 \end{figure}
 \FloatBarrier\noindent
-The tuned ferrite-rod antenna is kept to provide a good selectivity
+The tuned ferrite-rod antenna is kept to filter out the irrelevant spectral components, leaving only the DCF77's component at \SI{77.5}{\kilo\hertz}.
+This signal is then amplified by a RF amplifier and sampled at a certain sampling rate $f_{s}$ using the Analog to Digital Converter (ADC) of the application processsor.
+A timer producing a frequency equal to $f_{s}$ is used to trigger the sampling.
+The samples are passed to the Goertzel algorithm to analyze the amplitude of the DCF77 signal.
+The result of the analyzation is then passed to a detector to reconstruct the binary time signal.
+\par
+Before discussing the simulation of the whole reciever, the internal parts executing the sampling, the spectral analysis and the detection are explained in more detail, as they use some special techniques that should be introduced and explained beforehand.
+
+\subsection{Bandpass sampling the DCF77 signal}
+
+%Needs to be placed here so it is in the left column and then on the bottom of the page
+\begin{figure*}[b]
+    \centering
+    \resizebox{0.95\textwidth}{!}{
+        \begin{tikzpicture}
+            \clip (-11.5,-1) rectangle + (23,4); %Clipping: where to start, shape and size
+
+            \coordinate (fc) at (7.75,0);
+            \coordinate (fs) at (2.4,0);
+
+            %Axes
+            \draw[->, very thick] (-11,0) -- (11,0) node[right] {f};
+            \draw[->, very thick] (0,-1) -- (0,2.5) node[above] {Amplitude};
+
+            %DCF77 at f_c
+            \draw[thick, pattern={Dots[angle=45,distance={1.25pt/sqrt(2)}]}, pattern color=blue]
+            ($(fc) + (-0.12,0)$) -- % Left line start
+            ++(0,1) -- %Left line up
+            ++(0.24,0.5) -- %Roof
+            ++(0,-1.5) -- %Right line down
+            cycle; % Close the shape
+            \draw[very thick] ($(fc) + (0, -0.2)$) -- ++(0, 0.4); %Line x-axis
+            \node at ($(fc) + (0, -0.8)$) {$f_{c}$}; %Index x-axis
+            \draw[<->] ($(fc) + (-0.12,1.75)$) -- ++(0.24,0) node[midway, above] {$B$}; %Bandwidth
+
+            %DCF77 at f_c
+            \draw[thick, pattern={Dots[angle=45,distance={1.25pt/sqrt(2)}]}, pattern color=blue]
+            ($-1*(fc) + (-0.12,0)$) -- % Left line start
+            ++(0,1.5) -- %Left line up
+            ++(0.24,-0.5) -- %Roof
+            ++(0,-1) -- %Right line down
+            cycle; % Close the shape
+            \draw[very thick] ($-1*(fc) + (0, -0.2)$) -- ++(0, 0.4); %Line x-axis
+            \node at ($-1*(fc) + (0, -0.8)$) {$-f_{c}$}; %Index x-axis
+            \draw[<->] ($-1*(fc) + (-0.12,1.75)$) -- ++(0.24,0) node[midway, above] {$B$}; %Bandwidth
+
+            %f_s their result of the convulutions
+            \foreach \x in {-3,-2,-1,1,2,3}{
+                \draw[-> , thick] ($\x*(fs)$) -- ++(0,1.5);
+                \draw[very thick] ($\x*(fs) + (0,-0.2)$) -- ++(0,0.4);
+                \node at ($\x*(fs) + (0,-0.4)$) {$\x f_{s}$};
+
+                \draw[thick]
+                ($(fc) + (-0.12,0) + \x*(fs)$) -- % Left line start
+                ++(0,1) -- %Left line up
+                ++(0.24,0.5) -- %Roof
+                ++(0,-1.5) -- %Right line down
+                cycle; % Close the shape
+                \draw[very thick] ($(fc) + (0, -0.2) + \x*(fs)$) -- ++(0, 0.4); %Line x-axis
+                \ifthenelse{\x = -3}{
+                    \node at ($(fc) + (0.3, -0.8) + \x*(fs)$) {$f_{c} \pgfmathprintnumber[print sign]{\x} f_{s}$}; %Index x-axis
+                }{
+                    \node at ($(fc) + (0, -0.8) + \x*(fs)$) {$f_{c} \pgfmathprintnumber[print sign]{\x} f_{s}$}; %Index x-axis
+                }
+
+                %DCF77 at -f_c
+                \draw[thick]
+                ($-1*(fc) + (-0.12,0) + \x*(fs)$) -- % Left line start
+                ++(0,1.5) -- %Left line up
+                ++(0.24,-0.5) -- %Roof
+                ++(0,-1) -- %Right line down
+                cycle; % Close the shape
+                \draw[very thick] ($-1*(fc) + (0, -0.2) + \x*(fs)$) -- ++(0, 0.4); %Line x-axis
+                \ifthenelse{\x = 3}{
+                    \node at ($-1*(fc) + (-0.3, -0.8) + \x*(fs)$) {$-f_{c} \pgfmathprintnumber[print sign]{\x} f_{s}$}; %Index x-axis
+                }{
+                    \node at ($-1*(fc) + (0, -0.8) + \x*(fs)$) {$-f_{c} \pgfmathprintnumber[print sign]{\x} f_{s}$}; %Index x-axis
+                }
+            };
+        \end{tikzpicture}
+    }
+    \caption{Spectrum after bandpass sampling the DCF77 signal at $f_{s} = \SI{24}{\kilo\hertz}$}
+\end{figure*}
+
+Lowpass sampling is probably the most commonly used sampling technique.
+Stated by the Nyquist criterion, it requires the sampling rate $f_{s}$ to be at greater or equal to twice of the frequency of the highest frequency $f_{h}$ component in the signal to be sampled:
+\begin{equation}
+    f_{s} \geq 2 \cdot f_{h}
+\end{equation}
+Only when this condition is satisfied, the original signal can be reconstructed from the samples and it must be ensured that the signal contains no spectral elements that might violate the condition \cite{b6}.
+This is usually done by filtering the signal through a lowpass before sampling.
+\par
+Besides lowpass sampling, a signal can also be bandpass sampled if it is has a limited bandwidth $B$, defined by the frequency of the lowest spectral component $f_{l}$ and the highest spectral component $f_{h}$:
+\begin{equation}
+    B = f_{h} - f_{l}
+\end{equation}
+The center frequency $f_{c}$ is then located in the middle between $f_{l}$ and $f_{h}$:
+\begin{equation}
+    f_{c} = \frac{f_{l} + f_{h}}{2} = f_{l} + \frac{B}{2}
+\end{equation}
+Signals that fulfill this requirements can also be sampled with a lower $f_{s}$ and still be reconstructed, if special care is taken when selecting the actual value of $f_{s}$.
+The ranges of possible values for $f_{s}$ are defined by the equation
+\begin{equation}
+    \frac{2 \cdot f_{c} - B}{m} \geq f_{s} \geq \frac{2 \cdot f_{c} + B}{m + 1}
+\end{equation}
+and $f_{s} \geq 2 \cdot B$ hold true with $m$ being an arbitrary, positive integer \cite{b6}.
+During this sampling process, the signal is also shifted in frequency. This can be imagined
+by sum of convolutions of the initial spectrum with dirac delta functions, located at
+positive and negative integer multiples of $f_{s}$ \cite{b9}.
+
+Test
 
@@
 The working principle of the algorithm can be percieved as a second-order Infinite Impulse Response (IIR) filter where the results $y[n-1]$ and $y[n-2]$ of the output $y[n]$
-are stored in states $Q_{1}$ and $Q_{2}$, so they are still available after the execution of the filter:
+are stored in states $Q_{1}$ and $Q_{2}$, so they are still available after the execution of the filter \cite{b8}.
 \begin{equation}
@@
 \end{equation}
-\begin{figure}[!htbp]
+\begin{figure}[h]
     \centering
@@
 amplitude.
-
-\begin{figure*}[!htbp]
-    \centering
-    \resizebox{0.9\textwidth}{!}{
-        \begin{tikzpicture}
-            \clip (-11.5,-1) rectangle + (23,5); %Clipping: where to start, shape and size
-
-            \coordinate (fc) at (7.75,0);
-            \coordinate (fs) at (2.4,0);
-
-            %Axes
-            \draw[->, very thick] (-11,0) -- (11,0) node[right] {f};
-            \draw[->, very thick] (0,-1) -- (0,3) node[above] {Amplitude};
-
-            %DCF77 at f_c
-            \draw[thick, pattern={Dots[angle=45,distance={1.25pt/sqrt(2)}]}, pattern color=blue]
-            ($(fc) + (-0.12,0)$) -- % Left line start
-            ++(0,1) -- %Left line up
-            ++(0.24,0.5) -- %Roof
-            ++(0,-1.5) -- %Right line down
-            cycle; % Close the shape
-            \draw[very thick] ($(fc) + (0, -0.2)$) -- ++(0, 0.4); %Line x-axis
-            \node at ($(fc) + (0, -0.8)$) {$f_{c}$}; %Index x-axis
-            \draw[<->] ($(fc) + (-0.12,1.75)$) -- ++(0.24,0) node[midway, above] {$B$}; %Bandwidth
-
-            %DCF77 at f_c
-            \draw[thick, pattern={Dots[angle=45,distance={1.25pt/sqrt(2)}]}, pattern color=blue]
-            ($-1*(fc) + (-0.12,0)$) -- % Left line start
-            ++(0,1.5) -- %Left line up
-            ++(0.24,-0.5) -- %Roof
-            ++(0,-1) -- %Right line down
-            cycle; % Close the shape
-            \draw[very thick] ($-1*(fc) + (0, -0.2)$) -- ++(0, 0.4); %Line x-axis
-            \node at ($-1*(fc) + (0, -0.8)$) {$-f_{c}$}; %Index x-axis
-            \draw[<->] ($-1*(fc) + (-0.12,1.75)$) -- ++(0.24,0) node[midway, above] {$B$}; %Bandwidth
-
-            %f_s their result of the convulutions
-            \foreach \x in {-3,-2,-1,1,2,3}{
-                \draw[-> , thick] ($\x*(fs)$) -- ++(0,1.5);
-                \draw[very thick] ($\x*(fs) + (0,-0.2)$) -- ++(0,0.4);
-                \node at ($\x*(fs) + (0,-0.4)$) {$\x f_{s}$};
-
-                \draw[thick]
-                ($(fc) + (-0.12,0) + \x*(fs)$) -- % Left line start
-                ++(0,1) -- %Left line up
-                ++(0.24,0.5) -- %Roof
-                ++(0,-1.5) -- %Right line down
-                cycle; % Close the shape
-                \draw[very thick] ($(fc) + (0, -0.2) + \x*(fs)$) -- ++(0, 0.4); %Line x-axis
-                \ifthenelse{\x = -3}{
-                    \node at ($(fc) + (0.3, -0.8) + \x*(fs)$) {$f_{c} \pgfmathprintnumber[print sign]{\x} f_{s}$}; %Index x-axis
-                }{
-                    \node at ($(fc) + (0, -0.8) + \x*(fs)$) {$f_{c} \pgfmathprintnumber[print sign]{\x} f_{s}$}; %Index x-axis
-                }
-
-                %DCF77 at -f_c
-                \draw[thick]
-                ($-1*(fc) + (-0.12,0) + \x*(fs)$) -- % Left line start
-                ++(0,1.5) -- %Left line up
-                ++(0.24,-0.5) -- %Roof
-                ++(0,-1) -- %Right line down
-                cycle; % Close the shape
-                \draw[very thick] ($-1*(fc) + (0, -0.2) + \x*(fs)$) -- ++(0, 0.4); %Line x-axis
-                \ifthenelse{\x = 3}{
-                    \node at ($-1*(fc) + (-0.3, -0.8) + \x*(fs)$) {$-f_{c} \pgfmathprintnumber[print sign]{\x} f_{s}$}; %Index x-axis
-                }{
-                    \node at ($-1*(fc) + (0, -0.8) + \x*(fs)$) {$-f_{c} \pgfmathprintnumber[print sign]{\x} f_{s}$}; %Index x-axis
-                }
-            };
-        \end{tikzpicture}
-    } 
-\end{figure*}
 
@@
 \bibitem{b6} R. G. Lyons, ``Understanding Digital Signal Processing,'' Third Edition, Prentice Hall, 2010.
+\bibitem{b9} J. Hoffmann, ``Sampling bandpass signals,'' 2021, Internet Article. [Online]. Available: https://www.dsprelated.com/showarticle/1407.php
 \bibitem{b7} -, ``Goertzel algorithm,'' 2024, Wikipedia entry. [Online]. Available: https://en.wikipedia.org/wiki/Goertzel\_algorithm
+\bibitem{b8} K. Banks, ``The Goertzel Algorithm,'' 2002, Internet Article. [Online]. Available: https://courses.cs.washington.edu/courses/cse466/12au/calendar/Goertzel-EETimes.pdf
 %\bibitem{b3} I. S. Jacobs and C. P. Bean, ``Fine particles, thin films and exchange anisotropy,'' in Magnetism, vol. III, G. T. Rado and H. Suhl, Eds. New York: Academic, 1963, pp. 271--350.

### 2024-08-20 paper/main.tex
Progress in Structure of the receiver

@@
 \usepackage{stfloats}
+\usepackage{tabularray}
 
@@
 \begin{document}
-
 \title{Decoding the Amplitude-Modulated Part the DCF77 Longwave Time Signal by using the Goertzel Algorithm}
@@
 generated by two caesium clocks and two caesium fountains. Its operating frequency lies in the long wave area at \SI{77.5}{\kilo\hertz} and the time signal
-uses simple modulation techniques (amplitude and phase-modulation) and transmits with \SI{100}{\kilo\watt} Effective Isotropic Radiated Power (EIRP) to enable the reception of the signal in relatively close distances (up to \SI{2000}{\kilo\meter})
-with simple technical equipment \cite{b2}.
+uses simple modulation techniques (amplitude and phase-modulation) and transmits with \SI{100}{\kilo\watt} Effective Isotropic Radiated Power (EIRP) to enable the reception of the
+signal in relatively close distances (up to \SI{2000}{\kilo\meter}) with simple technical equipment \cite{b2}.
 \begin{figure}[!htbp]
@@
 In 1973, the transmission of the current time information was added to the signal by using amplitude modulation.
-To allow a reception under more challenging conditions and with a higher resolution and accuracy, the same time information is also added to the signal since 1983 by using phase-modulation \cite{b3}.
+To allow a reception under more challenging conditions and with a higher resolution and accuracy, the same time information is also added to the signal since 1983 by using
+phase-modulation \cite{b3}.
 The two different parts of the signal that result out of the parallel amplitude and the phase-modulation can be used for different use-cases that are separated by the
@@
 \par
-Before discussing the simulation of the whole reciever, the internal parts executing the sampling, the spectral analysis and the detection are explained in more detail, as they use some special techniques that should be introduced and explained beforehand.
+Before discussing the simulation of the whole reciever, the internal parts executing the sampling, the spectral analysis and the detection are explained in more detail,
+as they use some special techniques that should be introduced and explained beforehand.
 
 \subsection{Bandpass sampling the DCF77 signal}
+Lowpass sampling is probably the most commonly used sampling technique.
+Stated by the Nyquist criterion, it requires the sampling rate $f_{s}$ to be at greater or equal to twice of the frequency of the highest frequency $f_{h}$ component in the
+signal to be sampled:
+\begin{equation}
+    f_{s} \geq 2 \cdot f_{h}
+\end{equation}
+Only when this condition is satisfied, the original signal can be reconstructed from the samples and it must be ensured that the signal contains no spectral elements
+that might violate the condition \cite{b6}.
+This is usually done by filtering the signal through a lowpass before sampling.
+\par
+Besides lowpass sampling, a signal can also be bandpass sampled if it is has a limited bandwidth $B$, defined by the frequency of the lowest spectral component $f_{l}$ and
+the highest spectral component $f_{h}$:
+\begin{equation}
+    B = f_{h} - f_{l}
+\end{equation}
+The center frequency $f_{c}$ is then located in the middle between $f_{l}$ and $f_{h}$:
+\begin{equation}
+    f_{c} = \frac{f_{l} + f_{h}}{2} = f_{l} + \frac{B}{2}
+\end{equation}
+Signals that fulfill these requirements can also be sampled with a lower $f_{s}$ and still be reconstructed, if special care is taken when selecting the actual value of $f_{s}$.
+The ranges of possible values for $f_{s}$ are defined by the conditions
+\begin{equation}
+    \frac{2 \cdot f_{c} - B}{m} \geq f_{s} \geq \frac{2 \cdot f_{c} + B}{m + 1} \label{eqn:fs}
+\end{equation}
+and
+\begin{equation}
+    f_{s} \geq 2 \cdot B \label{eqn:fs_b}
+\end{equation}
+with $m$ being an arbitrary, positive integer \cite{b6}.
+During this sampling process, the signal is also shifted in frequency. This can be imagined
+by a sum of convolutions of the initial spectrum with dirac delta functions, located at
+positive and negative integer multiples of $f_{s}$ \cite{b9}.
+\par
+As the DCF77's signal fulfills the stated requirements after it is received by the tuned ferrite-rod antenna and therefore bandpass filtered, it qualifies for being bandpass sampled.
+Its center frequency $f_{c}$ lies at \SI{77.5}{\kilo\hertz} with a theoretical maximum bandwidth $B$ of \SI{2.4}{\kilo\hertz} \cite{b2}.
+The effective bandwidth is much smaller in reality but \SI{2.4}{\kilo\hertz} will be used for finding a proper sampling frequency to provide enough safety margin.
+With (\ref{eqn:fs}), a table containing possible ranges for $f_{s}$ can be created.
+\begin{table}[htbp]
+    \caption{Possible ranges for $f_{s}$ with $f_{c} = \SI{77.5}{\kilo\hertz}$ and $B = \SI{2.4}{\kilo\hertz}$}
+    \centering
+    \begin{tblr}{|c|c|c|}
+        \hline
+        & Lower boundary of $f_{s}$ & Upper boundary of $f_{s}$\\
+        $m$ & $\left\lceil\frac{2 \cdot f_{c} + B}{m + 1}\right\rceil$ & $\left\lfloor\frac{2 \cdot f_{c} - B}{m}\right\rfloor$\\
+        \hline
+        $1$ & $\SI{78700}{\hertz}$ & $\SI{152600}{\hertz}$\\
+        $3$ & $\SI{52467}{\hertz}$ & $\SI{76300}{\hertz}$\\
+        $4$ & $\SI{39350}{\hertz}$ & $\SI{50866}{\hertz}$\\
+        $5$ & $\SI{31480}{\hertz}$ & $\SI{38150}{\hertz}$\\
+        $6$ & $\SI{26234}{\hertz}$ & $\SI{30520}{\hertz}$\\
+        $7$ & $\SI{22486}{\hertz}$ & $\SI{25433}{\hertz}$\\
+        $8$ & $\SI{19675}{\hertz}$ & $\SI{21800}{\hertz}$\\
+        $\vdots$ & $\vdots$ & $\vdots$\\
+        $31$ & $\SI{4919}{\hertz}$ & $\SI{4922}{\hertz}$\\
+        \color{red} $32$ & \color{red} $\SI{4770}{\hertz}$ & \color{red} $\SI{4768}{\hertz}$\\
+        \color{red} $33$ & \color{red} $\SI{4630}{\hertz}$ & \color{red} $\SI{4624}{\hertz}$\\
+        \hline
+    \end{tblr}
+    \label{tab0}
+\end{table}
+\FloatBarrier\noindent
+It is visible that with increasing values for $m$, the value of $f_{s}$ and also the distance between the lower and the upper boundaries are decreasing.
+At $m = 32$, the condition of (\ref{eqn:fs_b}) is violated and at $m = 32$ the condition of (\ref{eqn:fs}), making $m = 31$ the last valid range.
+Choosing a sampling rate can now be done from this table while.
+A lower sampling rate effectively shrinks the requirements regarding computational power, memory size and the ADC's speed, but simultaneously decreases the
+distance between the lower and the upper boundaty of the sampling rate.
+This then leads to higher requirements regarding the correctness of the sampling rate.
+A choice providing a good tradeoff between these effects is $m = 7$ with $f_{s} = \SI{24}{\kilo\hertz}$, because it offers a distance of $\SI{2647}{\hertz}$
+the upper and lower boundary with the sampling frequency lying almost in the middle \cite{b10}.
+The DCF77 signal is then, as visible in Fig. \ref{fig:dcf77_bp_spectrum}, downconverted and centered at
+\begin{equation}
+    f_{c}^{'} = f_{c} - 3 \cdot f_{s} = \SI{77.5}{\kilo\hertz} - 3 \cdot \SI{24}{\kilo\hertz} = \SI{5.5}{\kilo\hertz}
+\end{equation}
+caused by the convolution of the initial spectrum with the dirac delta impulse, located at $-3 \cdot f_{s}$.
 
 %Needs to be placed here so it is in the left column and then on the bottom of the page
-\begin{figure*}[b]
+\begin{figure*}[h]
     \centering
@@
     \caption{Spectrum after bandpass sampling the DCF77 signal at $f_{s} = \SI{24}{\kilo\hertz}$}
+    \label{fig:dcf77_bp_spectrum}
 \end{figure*}
-
-Lowpass sampling is probably the most commonly used sampling technique.
-Stated by the Nyquist criterion, it requires the sampling rate $f_{s}$ to be at greater or equal to twice of the frequency of the highest frequency $f_{h}$ component in the signal to be sampled:
-\begin{equation}
-    f_{s} \geq 2 \cdot f_{h}
-\end{equation}
-Only when this condition is satisfied, the original signal can be reconstructed from the samples and it must be ensured that the signal contains no spectral elements that might violate the condition \cite{b6}.
-This is usually done by filtering the signal through a lowpass before sampling.
-\par
-Besides lowpass sampling, a signal can also be bandpass sampled if it is has a limited bandwidth $B$, defined by the frequency of the lowest spectral component $f_{l}$ and the highest spectral component $f_{h}$:
-\begin{equation}
-    B = f_{h} - f_{l}
-\end{equation}
-The center frequency $f_{c}$ is then located in the middle between $f_{l}$ and $f_{h}$:
-\begin{equation}
-    f_{c} = \frac{f_{l} + f_{h}}{2} = f_{l} + \frac{B}{2}
-\end{equation}
-Signals that fulfill this requirements can also be sampled with a lower $f_{s}$ and still be reconstructed, if special care is taken when selecting the actual value of $f_{s}$.
-The ranges of possible values for $f_{s}$ are defined by the equation
-\begin{equation}
-    \frac{2 \cdot f_{c} - B}{m} \geq f_{s} \geq \frac{2 \cdot f_{c} + B}{m + 1}
-\end{equation}
-and $f_{s} \geq 2 \cdot B$ hold true with $m$ being an arbitrary, positive integer \cite{b6}.
-During this sampling process, the signal is also shifted in frequency. This can be imagined
-by sum of convolutions of the initial spectrum with dirac delta functions, located at
-positive and negative integer multiples of $f_{s}$ \cite{b9}.
-
-Test
+\FloatBarrier
 
@@
 \end{tabular}
-\label{tab1}
+\label{tab}
 \end{center}
@@
 \bibitem{b9} J. Hoffmann, ``Sampling bandpass signals,'' 2021, Internet Article. [Online]. Available: https://www.dsprelated.com/showarticle/1407.php
+\bibitem{b10} F. Zaplata and M. Kasal, ``SDR Implementation for DCF77,'', 2013, IEEE Paper. [Online]. Available: https://ieeexplore.ieee.org/document/6530943
 \bibitem{b7} -, ``Goertzel algorithm,'' 2024, Wikipedia entry. [Online]. Available: https://en.wikipedia.org/wiki/Goertzel\_algorithm

### 2024-08-22 paper/main.tex
Detector chapter finished.

@@
 caused by the convolution of the initial spectrum with the dirac delta impulse, located at $-3 \cdot f_{s}$. 
+The following block, the Goertzel algorithm, therefore needs to analyze the spectral component at $f_{c}^{'} = \SI{5.5}{\kilo\hertz}$.
 
 %Needs to be placed here so it is in the left column and then on the bottom of the page
-\begin{figure*}[h]
+\begin{figure*}[t]
     \centering
@@
     }
-    \caption{Spectrum after bandpass sampling the DCF77 signal at $f_{s} = \SI{24}{\kilo\hertz}$}
+    \caption{Spectrum after bandpass sampling the DCF77 signal at $f_{s} = \SI{24}{\kilo\hertz}$. The original spectral parts are filled with blue dots.}
     \label{fig:dcf77_bp_spectrum}
 \end{figure*}
-\FloatBarrier
 
@@
 to leverage the DFT gain.
-The result is then passed to a detector to obtain the binary time signal from the analyzed
-amplitude.
+The square roots of the results are taken to finally calculate the magnitude of the DCF77 signal's amplitude and then passed to a detector to obtain the binary time signal.
+Because of the duration of the analyzation being equal to \SI{10}{\milli\second}, the sampling rate after the Goertzel algorithm is equal to:
+\begin{equation}
+    f_{s,g} = \frac{1}{\SI{10}{\milli\second}} = \SI{100}{\hertz}
+\end{equation}
+
+\subsection{The detector}
+The output of the Goertzel algorithm is already following the waveform of the binary time signal but still includes fluctuations due to noise and fading.
+To reconstruct the original waveform of the binary time signal, it is processed inside a detector.
+As the values of the Goertzel algorithm will follow the pattern of the signal's amplitude being switched between \SI{15}{\percent} and \SI{100}, the detection can be done by comparing the current value to a threshold.
+Because of the Goertzel algorithm delivering absolute values, whose magnitude depend on the current receiving situation, a Exponential Moving Average is calculated and used to normalize the values by using (\ref{eqn:ema}).
+\begin{equation}
+    y[t] = \alpha \cdot x[t] + (1 - \alpha) \cdot y[t-1]
+    \label{eqn:ema}
+\end{equation}
+This part can also be represented as an IIR-structure:
+\begin{figure}[h]
+    \centering
+    \resizebox{0.4\textwidth}{!}{
+        \begin{tikzpicture}[auto, node distance=2cm]
+            %Defining a cross set for the multiplication elements
+            \tikzset{cross/.style={path picture={ 
+            \draw[black]
+            (path picture bounding box.south east) -- (path picture bounding box.north west) (path picture bounding box.south west) -- (path picture bounding box.north east);
+            }}}
+
+            %Block styles
+            \tikzstyle{delay} = [draw, rectangle, minimum height=2em, minimum width=2em]
+            \tikzstyle{sum} = [draw, circle, minimum size=2em, node distance=1.5cm]
+            \tikzstyle{mult} = [draw, circle, minimum size=2em, node distance=1.5cm, cross]
+            \tikzstyle{state} = [draw, rectangle, rounded corners, minimum height=2em, minimum width=2em]
+
+            %Nodes
+            \node at (-1.5, 0) (x) {$x[n]$};
+            \node[mult] at (0,0) (mult1) {};
+            \node[sum] at (1.5,0) (sum1) {+};
+            \node[mult] at (3,-2) (mult2) {};
+            \node[delay] at (4.5,-1) (del1) {$z^{-1}$};
+            \node at (6, 0) (y) {$y[n]$};
+
+            \draw[->] (x.east) -- (mult1.west);
+            \draw[->] (mult1.east) -- (sum1.west);
+            \draw[->] (sum1.east) -- (y.west);
+            \draw[->] (mult2.west) -- (1.5, -2) -- (sum1.south);
+            \draw[->] (del1.south) -- (4.5, -2) -- (mult2.east);
+            \draw[->] (4.5, 0) -- (del1.north);
+            \draw[->] (0, 0.75) -- (mult1.north);
+            \draw[->] (3, -1.25) -- (mult2.north);
+            \node at (0, 1) {$\alpha$};
+            \node at (3, -1) {$1 - \alpha$};
+            \node[draw, shape=circle, fill=black, scale=0.3] at (4.5,0) {};
+        \end{tikzpicture}
+    }
+    \caption{IIR representation of the Exponential Moving Average}
+    \label{fig:ema_iir}
+\end{figure}
+\FloatBarrier\noindent
+The value of the smoothing factor $\alpha$ was calculated to take the samples of the last \SI{10}{\second} into account:
+\begin{equation}
+    \begin{split}
+        \alpha &= \frac{2}{N + 1} = \frac{2}{\SI{10}{\second} \cdot f_{s,g} + 1}\\
+        &= \frac{2}{\SI{10}{\second} \cdot \SI{100}{\hertz} + 1} \approx 0.001998
+    \end{split}
+\end{equation}
+This provides a stable and slowly changing average, as it is putting more weight on the past samples and leaves minimal influence to the most recent sample.
+The decision is then done by comparing the current sample to a threshold calculated by multiplying the current value of the average with $0.575$ (the middle bewteen \SI{15}{\percent} and \SI{100}{\percent}) and a scaling factor of $\frac{1}{0.8725}$.
+The scaling factor is needed as the average percentage of time where the signal where is equal to \SI{100}{percent} is \SI{87.25}{\percent} (assuming an equal distribution between symbols representing a 1 and a 0).
 

### 2024-08-22 paper/main.tex
Housekeeping, restructuring and simplifications. Fixed typos

@@
 Amplitude-Shift Keying (ASK). Every symbol has the duration of exactly \SI{1}{\second}, with a part that is either \SI{100}{\milli\second} or \SI{200}{\milli\second}
-long where it has a value to zero.
+long where it has a value equal to 0.
 This the duration of this "gap" is used to encode respectively a 0 or a 1 and effectively switches the strength of the carrier between \SI{15}{\percent} and \SI{100}{\percent} \cite{b5}.
@@
 To allow the detection of a new minute, the gap is left out between the last (59) second of the ongoing and the first (0) second of the next minute.
-By using this scheme, a dataframe consisting out \SI{59}{\Bit}, starting at second one, can be transmitted every minute.
+By using this scheme, a dataframe consisting out \SI{59}{\Bit}, starting at second 1, can be transmitted every minute.
 Bit \SIrange{0}{19}{} are used to send encrypted weather data, to notify the PTB in case of errors in the transmitter, to announce an upcoming
@@
 The effective bandwidth is much smaller in reality but \SI{2.4}{\kilo\hertz} will be used for finding a proper sampling frequency to provide enough safety margin.
-With (\ref{eqn:fs}), a table containing possible ranges for $f_{s}$ can be created.
+With \eqref{eqn:fs}, a table containing possible ranges for $f_{s}$ can be created.
 \begin{table}[htbp]
@@
 It is visible that with increasing values for $m$, the value of $f_{s}$ and also the distance between the lower and the upper boundaries are decreasing.
-At $m = 32$, the condition of (\ref{eqn:fs_b}) is violated and at $m = 32$ the condition of (\ref{eqn:fs}), making $m = 31$ the last valid range.
-Choosing a sampling rate can now be done from this table while.
+At $m = 32$, the condition of \eqref{eqn:fs_b} is violated and at $m = 32$ the condition of \eqref{eqn:fs}, making $m = 31$ the last valid range.
+Choosing a sampling rate can now be done with this table.
+\par
 A lower sampling rate effectively shrinks the requirements regarding computational power, memory size and the ADC's speed, but simultaneously decreases the
-distance between the lower and the upper boundaty of the sampling rate.
-This then leads to higher requirements regarding the correctness of the sampling rate.
-A choice providing a good tradeoff between these effects is $m = 7$ with $f_{s} = \SI{24}{\kilo\hertz}$, because it offers a distance of $\SI{2647}{\hertz}$
-the upper and lower boundary with the sampling frequency lying almost in the middle \cite{b10}.
+distance between the lower and the upper limits of the sampling rate.
+This then leads to higher requirements regarding the adherence to the exact sampling rate.
+A choice providing a good tradeoff between these effects $f_{s} = \SI{24}{\kilo\hertz}$ at $m = 7$, because it offers a distance of $\SI{2647}{\hertz}$ between the upper and lower limits with the sampling frequency lying almost in the middle \cite{b10}.
 The DCF77 signal is then, as visible in Fig. \ref{fig:dcf77_bp_spectrum}, downconverted and centered at
@@
 \end{equation}
-caused by the convolution of the initial spectrum with the dirac delta impulse, located at $-3 \cdot f_{s}$. 
+caused by the convolution of the initial spectrum with the dirac delta impulse located at $-3 \cdot f_{s}$. 
 The following block, the Goertzel algorithm, therefore needs to analyze the spectral component at $f_{c}^{'} = \SI{5.5}{\kilo\hertz}$.
@@
 the Fast Fourier Transform (FFT). This yields an analysis of the complete spectrum, producing $\frac{N}{2} + 1$ relevant results for equally distributed frequencies
-("frequency bins") within range from \SI{0}{\hertz} to $\frac{f_{s}}{2}$ where $N$ is the number of samples and $f_{s}$ the sampling frequency \cite{b6}.
-The signal strength, and therefore the binary time signal of the amplitude-modulated part, can then be examined by observing the value of the curresponding frequency bin
+("frequency bins") within a range from \SI{0}{\hertz} to $\frac{f_{s}}{2}$ where $N$ is the number of samples and $f_{s}$ is the sampling frequency \cite{b6}.
+The signal strength, and therefore the binary time signal of the amplitude-modulated part, can then be examined by observing the magnitude of the curresponding frequency bin
 over time. Because of only one frequency bin being relevant, it is obvious that a full FFT produces a lot of overhead and redundant calculation operations in this use-case. 
@@
 amount of needed calculations.
-It was invented in 1958 by Gerald Goertzel and since then is most commonly used in the detection tones employed in Dual-tone Multi-frequency (DTMF) signaling \cite{b7}.
-The working principle of the algorithm can be percieved as a second-order Infinite Impulse Response (IIR) filter where the results $y[n-1]$ and $y[n-2]$ of the output $y[n]$
-are stored in states $Q_{1}$ and $Q_{2}$, so they are still available after the execution of the filter \cite{b8}.
+It was invented in 1958 by Gerald Goertzel and since then is most commonly used in the detection of tones employed in Dual-tone Multi-frequency (DTMF) signaling \cite{b7}.
+The working principle of the algorithm can be percieved as a second-order Infinite Impulse Response (IIR) filter (see \eqref{eqn:goertzel}) where the results $y[n-1]$ and $y[n-2]$ of the output $y[n]$
+are stored in the states $Q_{1}$ and $Q_{2}$, so they are still available after the execution of the filter \cite{b8}.
 \begin{equation}
     y[n] = x[n] + 2 \cdot cos(\omega_{g}) \cdot y[n-1] - y[n-2]
+    \label{eqn:goertzel}
 \end{equation}
@@
     }
-    \caption{IIR representation of the Goertzel algorithm without the final calculation of the squared magnitude}
+    \caption{Block diagram of the Goertzel algorithm without the final calculation of the squared magnitude}
     \label{fig:goertzel_iir}
@@
 The system takes the input sequence $x[n]$ with length $N$ and is executed exactly $N$ times.
-After the execution, the squared magnitude of $f_{a}$, the frequency to be analyzed, inside $x[n]$ can be calculated using the two states $Q_{1}$ and $Q_{2}$:
+After the execution, the squared magnitude of $f_{a}$, the frequency to be analyzed inside $x[n]$, can be calculated using the values of the two states $Q_{1}$ and $Q_{2}$:
 \begin{equation}
@@
 The Value of $\omega_{g}$ itself is calculated based on a integer number $k$ and $N$.
-The integer number $k$ is a rounded fraction based on $N$, the frequency to be analyzed $f_{a}$, and the the sampling frequency $f_{s}$.
+The integer number $k$ is a rounded fraction based on $N$, the frequency to be analyzed $f_{a}$, and the the sampling frequency $f_{s}$:
 \begin{equation}
@@
 In total, $N + 1$ multiplications and $2 \cdot N + 2$ additions are needed, which can be seen from the formulas for the IIR-part and the final calculation of the squared magnitude.
-For example, a length of $N = 512$ requires in $513$ multiplications and $1026$ additions to calculate the squared magnitude of the desired frequency.
-In comparison, the typical radix-2 FFT, needs $\frac{N}{2} \cdot \log_{2}(N)$ complex multiplications and $N \cdot \log_{2}(N)$ complex additions.
+For example, a length of processing $N = 512$ samples requires in $513$ multiplications and $1026$ additions to calculate the squared magnitude of the desired frequency.
+In comparison, the typical radix-2 FFT, needs $\frac{N}{2} \cdot \log_{2}(N)$ complex multiplications and $N \cdot \log_{2}(N)$ complex additions to be completed.
 With $N = 512$ this would result in $2034$ complex multiplications and $4608$ complex additions.
@@
 To reconstruct the original waveform of the binary time signal, it is processed inside a detector.
-As the values of the Goertzel algorithm will follow the pattern of the signal's amplitude being switched between \SI{15}{\percent} and \SI{100}, the detection can be done by comparing the current value to a threshold.
-Because of the Goertzel algorithm delivering absolute values, whose magnitude depend on the current receiving situation, a Exponential Moving Average is calculated and used to normalize the values by using (\ref{eqn:ema}).
+As the values of the Goertzel algorithm will follow the pattern of the signal's amplitude being switched between \SI{15}{\percent} and \SI{100}{\percent}, the detection can be done by comparing the value of the current sample to a threshold.
+To compensate the changing of magnitude of the Goertzel algorithm's values that is caused by the current receiving situation, an Exponential Moving Average (EMA) is calculated by using \eqref{eqn:ema} and employed to create an adaptive threshold.
 \begin{equation}
@@
 \end{equation}
-This part can also be represented as an IIR-structure:
+This part can also be represented as a block diagram:
 \begin{figure}[h]
@@
     }
-    \caption{IIR representation of the Exponential Moving Average}
+    \caption{Block diagram showing the calculation of the EMA}
     \label{fig:ema_iir}
@@
 The decision is then done by comparing the current sample to a threshold calculated by multiplying the current value of the average with $0.575$ (the middle bewteen \SI{15}{\percent} and \SI{100}{\percent}) and a scaling factor of $\frac{1}{0.8725}$.
-The scaling factor is needed as the average percentage of time where the signal where is equal to \SI{100}{percent} is \SI{87.25}{\percent} (assuming an equal distribution between symbols representing a 1 and a 0).
+The scaling factor is needed as the average percentage of time where the signal where is equal to \SI{100}{percent} is \SI{87.25}{\percent} (assuming an equal distribution between symbols representing a binary 1 and a 0).
+If the value of the current sample is above this threshold, it is treated as a 1.
+Otherwise it is treated as a 0.
+The series of ones and zeros is then following the waveform shown in Fig. \ref{fig:dcf77_symbol_encoding} and can be used to decode the current time.
 
-\subsection{Maintaining the Integrity of the Specifications}
-
-The IEEEtran class file is used to format your paper and style the text. All margins, 
-column widths, line spaces, and text fonts are prescribed; please do not 
-alter them. You may note peculiarities. For example, the head margin
-measures proportionately more than is customary. This measurement 
-and others are deliberate, using specifications that anticipate your paper 
-as one part of the entire proceedings, and not as an independent document. 
-Please do not revise any of the current designations.
-
-\section{Prepare Your Paper Before Styling}
-Before you begin to format your paper, first write and save the content as a 
-separate text file. Complete all content and organizational editing before 
-formatting. Please note sections \ref{AA} to \ref{FAT} below for more information on 
-proofreading, spelling and grammar.
-
-Keep your text and graphic files separate until after the text has been 
-formatted and styled. Do not number text heads---{\LaTeX} will do that 
-for you.
-
-\subsection{Abbreviations and Acronyms}\label{AA}
-Define abbreviations and acronyms the first time they are used in the text, 
-even after they have been defined in the abstract. Abbreviations such as 
-IEEE, SI, MKS, CGS, ac, dc, and rms do not have to be defined. Do not use 
-abbreviations in the title or heads unless they are unavoidable.
-
-\subsection{Units}
-\begin{itemize}
-\item Use either SI (MKS) or CGS as primary units.
-(SI units are encouraged.) English units may be used as secondary units (in parentheses).
-An exception would be the use of English units as identifiers in trade, such as ``3.5-inch disk drive''.
-\item Avoid combining SI and CGS units, such as current in amperes and magnetic field in oersteds.
-This often leads to confusion because equations do not balance dimensionally.
-If you must use mixed units, clearly state the units for each quantity that you use in an equation.
-\item Do not mix complete spellings and abbreviations of units: ``Wb/m\textsuperscript{2}'' or ``webers per square meter'', not ``webers/m\textsuperscript{2}''.
-Spell out units when they appear in text: ``.
-.
-.
-a few henries'', not ``.
-.
-.
-a few H''.
-\item Use a zero before decimal points: ``0.25'', not ``.25''. Use ``cm\textsuperscript{3}'', not ``cc''.)
-\end{itemize}
-
-\subsection{Equations}
-Number equations consecutively. To make your 
-equations more compact, you may use the solidus (~/~), the exp function, or 
-appropriate exponents. Italicize Roman symbols for quantities and variables, 
-but not Greek symbols. Use a long dash rather than a hyphen for a minus 
-sign. Punctuate equations with commas or periods when they are part of a 
-sentence, as in:
-\begin{equation}
-a+b=\gamma\label{eq}
-\end{equation}
-
-Be sure that the 
-symbols in your equation have been defined before or immediately following 
-the equation. Use ``\eqref{eq}'', not ``Eq.~\eqref{eq}'' or ``equation \eqref{eq}'', except at 
-the beginning of a sentence: ``Equation \eqref{eq} is . . .''
-
-\subsection{\LaTeX-Specific Advice}
-
-Please use ``soft'' (e.g., \verb|\eqref{Eq}|) cross references instead
-of ``hard'' references (e.g., \verb|(1)|). That will make it possible
-to combine sections, add equations, or change the order of figures or
-citations without having to go through the file line by line.
-
-Please don't use the \verb|{eqnarray}| equation environment. Use
-\verb|{align}| or \verb|{IEEEeqnarray}| instead. The \verb|{eqnarray}|
-environment leaves unsightly spaces around relation symbols.
-
-Please note that the \verb|{subequations}| environment in {\LaTeX}
-will increment the main equation counter even when there are no
-equation numbers displayed. If you forget that, you might write an
-article in which the equation numbers skip from (17) to (20), causing
-the copy editors to wonder if you've discovered a new method of
-counting.
-
-{\BibTeX} does not work by magic. It doesn't get the bibliographic
-data from thin air but from .bib files. If you use {\BibTeX} to produce a
-bibliography you must send the .bib files.
-
-{\LaTeX} can't read your mind. If you assign the same label to a
-subsubsection and a table, you might find that Table I has been cross
-referenced as Table IV-B3.
-
-{\LaTeX} does not have precognitive abilities. If you put a
-\verb|\label| command before the command that updates the counter it's
-supposed to be using, the label will pick up the last counter to be
-cross referenced instead. In particular, a \verb|\label| command
-should not go before the caption of a figure or a table.
-
-Do not use \verb|\nonumber| inside the \verb|{array}| environment. It
-will not stop equation numbers inside \verb|{array}| (there won't be
-any anyway) and it might stop a wanted equation number in the
-surrounding equation.
-
-\subsection{Some Common Mistakes}\label{SCM}
-\begin{itemize}
-\item The word ``data'' is plural, not singular.
-\item The subscript for the permeability of vacuum $\mu_{0}$, and other common scientific constants, is zero with subscript formatting, not a lowercase letter ``o''.
-\item In American English, commas, semicolons, periods, question and exclamation marks are located within quotation marks only when a complete thought or name is cited, such as a title or full quotation.
-When quotation marks are used, instead of a bold or italic typeface, to highlight a word or phrase, punctuation should appear outside of the quotation marks.
-A parenthetical phrase or statement at the end of a sentence is punctuated outside of the closing parenthesis (like this).
-(A parenthetical sentence is punctuated within the parentheses.)
-\item A graph within a graph is an ``inset'', not an ``insert''. The word alternatively is preferred to the word ``alternately'' (unless you really mean something that alternates).
-\item Do not use the word ``essentially'' to mean ``approximately'' or ``effectively''.
-\item In your paper title, if the words ``that uses'' can accurately replace the word ``using'', capitalize the ``u''; if not, keep using lower-cased.
-\item Be aware of the different meanings of the homophones ``affect'' and ``effect'', ``complement'' and ``compliment'', ``discreet'' and ``discrete'', ``principal'' and ``principle''.
-\item Do not confuse ``imply'' and ``infer''.
-\item The prefix ``non'' is not a word; it should be joined to the word it modifies, usually without a hyphen.
-\item There is no period after the ``et'' in the Latin abbreviation ``et al.''.
-\item The abbreviation ``i.e.'' means ``that is'', and the abbreviation ``e.g.'' means ``for example''.
-\end{itemize}
-An excellent style manual for science writers is \cite{b7}.
-
-\subsection{Authors and Affiliations}\label{AAA}
-\textbf{The class file is designed for, but not limited to, six authors.} A 
-minimum of one author is required for all conference articles. Author names 
-should be listed starting from left to right and then moving down to the 
-next line. This is the author sequence that will be used in future citations 
-and by indexing services. Names should not be listed in columns nor group by 
-affiliation. Please keep your affiliations as succinct as possible (for 
-example, do not differentiate among departments of the same organization).
-
-\subsection{Identify the Headings}\label{ITH}
-Headings, or heads, are organizational devices that guide the reader through 
-your paper. There are two types: component heads and text heads.
-
-Component heads identify the different components of your paper and are not 
-topically subordinate to each other. Examples include Acknowledgments and 
-References and, for these, the correct style to use is ``Heading 5''. Use 
-``figure caption'' for your Figure captions, and ``table head'' for your 
-table title. Run-in heads, such as ``Abstract'', will require you to apply a 
-style (in this case, italic) in addition to the style provided by the drop 
-down menu to differentiate the head from the text.
-
-Text heads organize the topics on a relational, hierarchical basis. For 
-example, the paper title is the primary text head because all subsequent 
-material relates and elaborates on this one topic. If there are two or more 
-sub-topics, the next level head (uppercase Roman numerals) should be used 
-and, conversely, if there are not at least two sub-topics, then no subheads 
-should be introduced.
-
-\subsection{Figures and Tables}\label{FAT}
-\paragraph{Positioning Figures and Tables} Place figures and tables at the top and 
-bottom of columns. Avoid placing them in the middle of columns. Large 
-figures and tables may span across both columns. Figure captions should be 
-below the figures; table heads should appear above the tables. Insert 
-figures and tables after they are cited in the text. Use the abbreviation 
-``Fig.~\ref{fig}'', even at the beginning of a sentence.
-
-\begin{table}[htbp]
-\caption{Table Type Styles}
-\begin{center}
-\begin{tabular}{|c|c|c|c|}
-\hline
-\textbf{Table}&\multicolumn{3}{|c|}{\textbf{Table Column Head}} \\
-\cline{2-4} 
-\textbf{Head} & \textbf{\textit{Table column subhead}}& \textbf{\textit{Subhead}}& \textbf{\textit{Subhead}} \\
-\hline
-copy& More table copy$^{\mathrm{a}}$& &  \\
-\hline
-\multicolumn{4}{l}{$^{\mathrm{a}}$Sample of a Table footnote.}
-\end{tabular}
-\label{tab}
-\end{center}
-\end{table}
-
-Figure Labels: Use 8 point Times New Roman for Figure labels. Use words 
-rather than symbols or abbreviations when writing Figure axis labels to 
-avoid confusing the reader. As an example, write the quantity 
-``Magnetization'', or ``Magnetization, M'', not just ``M''. If including 
-units in the label, present them within parentheses. Do not label axes only 
-with units. In the example, write ``Magnetization (A/m)'' or ``Magnetization 
-\{A[m(1)]\}'', not just ``A/m''. Do not label axes with a ratio of 
-quantities and units. For example, write ``Temperature (K)'', not 
-``Temperature/K''.
+\section{MATLAB Simulation of the Receiver}
+To verify and underline the working principle of the receiver, a simulation of the whole system was created using MATLAB.
+The whole simulation was divided into five sections to allow for a clear structure:
+\begin{enumerate}
+    \item Simulation Parameter Section
+    \item Signal Creation Section
+    \item Goertzel Algorithm Section
+    \item Detection Section
+    \item FFT and Plot Section
+\end{enumerate}
 
 \section*{Acknowledgment}
-
 The preferred spelling of the word ``acknowledgment'' in America is without 
@@
 acknowledgments in the unnumbered footnote on the first page.
-
-\section*{References}
-
-Please number citations consecutively within brackets \cite{b1}. The 
-sentence punctuation follows the bracket \cite{b2}. Refer simply to the reference 
-number, as in \cite{b3}---do not use ``Ref. \cite{b3}'' or ``reference \cite{b3}'' except at 
-the beginning of a sentence: ``Reference \cite{b3} was the first $\ldots$''
-
-Number footnotes separately in superscripts. Place the actual footnote at 
-the bottom of the column in which it was cited. Do not put footnotes in the 
-abstract or reference list. Use letters for table footnotes.
-
-Unless there are six authors or more give all authors' names; do not use 
-``et al.''. Papers that have not been published, even if they have been 
-submitted for publication, should be cited as ``unpublished'' \cite{b4}. Papers 
-that have been accepted for publication should be cited as ``in press'' \cite{b5}. 
-Capitalize only the first word in a paper title, except for proper nouns and 
-element symbols.
-
-For papers published in translation journals, please give the English 
-citation first, followed by the original foreign-language citation \cite{b6}.
 
@@
 \bibitem{b8} K. Banks, ``The Goertzel Algorithm,'' 2002, Internet Article. [Online]. Available: https://courses.cs.washington.edu/courses/cse466/12au/calendar/Goertzel-EETimes.pdf
-%\bibitem{b3} I. S. Jacobs and C. P. Bean, ``Fine particles, thin films and exchange anisotropy,'' in Magnetism, vol. III, G. T. Rado and H. Suhl, Eds. New York: Academic, 1963, pp. 271--350.
-%\bibitem{b4} K. Elissa, ``Title of paper if known,'' unpublished.
-%\bibitem{b5} R. Nicole, ``Title of paper with only first word capitalized,'' J. Name Stand. Abbrev., in press.
-%\bibitem{b6} Y.
-Yorozu, M.
-Hirano, K.
-Oka, and Y.
-Tagawa, ``Electron spectroscopy studies on magneto-optical media and plastic substrate interface,'' IEEE Transl.
-J.
-Magn.
-Japan, vol.
-2, pp.
-740--741, August 1987 [Digests 9th Annual Conf.
-Magnetics Japan, p.
-301, 1982].
-%\bibitem{b7} M. Young, The Technical Writer's Handbook. Mill Valley, CA: University Science, 1989.
-%\bibitem{b9} S. Liu, ``Wi-Fi Energy Detection Testbed (12MTC),'' 2023, gitHub repository. [Online]. Available: https://github.com/liustone99/Wi-Fi-Energy-Detection-Testbed-12MTC
-%\bibitem{b10} ``Treatment episode data set: discharges (TEDS-D): concatenated, 2006 to 2009.'' U.S.
-Department of Health and Human Services, Substance Abuse and Mental Health Services Administration, Office of Applied Studies, August, 2013, DOI:10.3886/ICPSR30122.v2
-%\bibitem{b11} K. Eves and J. Valasek, ``Adaptive control for singularly perturbed systems examples,'' Code Ocean, Aug. 2023. [Online]. Available: https://codeocean.com/capsule/4989235/tree
 \end{thebibliography}
-
 \end{document}

### 2024-08-22 matlab_scripts/adaptive_threshold1.m

@@ -1,58 +1,0 @@
-clear;
-close all;
-clc;
-
-
-
-% Generate a longer sample signal
-rng(0);  % For reproducibility
-N = 1000;  % Length of the signal
-signal = [randn(1, 300) * 0.1, randn(1, 200) * 0.1 + 1, randn(1, 300) * 0.1, randn(1, 200) * 0.1 + 1];
-
-% Initialize parameters
-threshold = 0.5;  % Initial threshold
-output = zeros(1, length(signal));  % Initialize output array
-alpha = 0.001;  % Learning rate for adaptive threshold
-
-% Adaptive thresholding
-for i = 1:length(signal)
-    % Determine output based on current threshold
-    if signal(i) > threshold
-        output(i) = 1;
-    else
-        output(i) = 0;
-    end
-    
-    % Update the threshold based on the current sample
-    % If output is 1, threshold should move closer to the current sample if it is 1
-    % If output is 0, threshold should move closer to the current sample if it is 0
-    if output(i) == 1
-        threshold = threshold + alpha * (signal(i) - threshold);
-    else
-        threshold = threshold - alpha * (threshold - signal(i));
-    end
-end
-
-% Display results
-disp('Final Threshold:');
-disp(threshold);
-
-% Plot the signal, threshold, and output
-figure;
-subplot(3,1,1);
-plot(signal, '-o');
-title('Input Signal');
-ylabel('Amplitude');
-xlabel('Sample');
-
-subplot(3,1,2);
-plot(output, '-o');
-title('Output Signal');
-ylabel('Binary Output');
-xlabel('Sample');
-
-subplot(3,1,3);
-plot(1:length(signal), threshold * ones(1,length(signal)), '--');
-title('Adaptive Threshold');
-ylabel('Threshold');
-xlabel('Sample');

### 2024-08-22 matlab_scripts/derivative_ramps.m

@@ -1,45 +1,0 @@
-clear;
-close all;
-clc;
-
-
-
-% Define the time vector
-t = 0:0.01:10; % from 0 to 10 seconds with a step of 0.01 seconds
-
-% Define the ramp signal
-ramp1 = t(t<=2);         % Ramp from 0 to 2 seconds
-ramp2 = 2*ones(size(t(t>2 & t<=4))); % Constant from 2 to 4 seconds
-ramp3 = (t(t>4 & t<=6)-4) + 2; % Ramp from 4 to 6 seconds starting from 2
-ramp4 = 4*ones(size(t(t>6 & t<=8))); % Constant from 6 to 8 seconds
-ramp5 = (t(t>8 & t<=10)-8) + 4; % Ramp from 8 to 10 seconds starting from 4
-
-% Concatenate all parts to form the complete signal
-signal = [ramp1, ramp2, ramp3, ramp4, ramp5];
-
-% Calculate the derivative using numerical differentiation
-dt = t(2) - t(1); % time step
-derivative = diff(signal) / dt; % numerical derivative
-t_derivative = t(1:end-1); % time vector for the derivative
-
-% Plot the original signal and its derivative
-figure;
-
-% Plot original signal
-subplot(2,1,1);
-plot(t, signal, 'b', 'LineWidth', 1.5);
-title('Original Signal (Series of Ramps)');
-xlabel('Time (s)');
-ylabel('Amplitude');
-grid on;
-
-% Plot derivative of the signal
-subplot(2,1,2);
-plot(t_derivative, derivative, 'r', 'LineWidth', 1.5);
-title('Derivative of the Signal');
-xlabel('Time (s)');
-ylabel('Amplitude');
-grid on;
-
-% Adjust plot spacing
-tight_layout();

### 2024-08-22 matlab_scripts/goertzel_test1.m

@@ -1,41 +1,0 @@
-clear;
-close all;
-clc;
-
-
-% Parameters
-fs = 8000;  % Sampling frequency
-f = 1000;   % Frequency to detect
-N = 256;    % Number of samples
-n = 0:N-1;  % Sample index
-
-% Generate a test signal (sine wave at 1 kHz)
-x = sin(2 * pi * f * n / fs);
-
-% Apply the Goertzel Algorithm
-k = round((f / fs) * N);  % Bin index for target frequency
-result = goertzel(x, k);
-
-% Display result
-disp(['Magnitude at ', num2str(f), ' Hz: ', num2str(abs(result))]);
-
-function magnitude = goertzel(x, k)
-    N = length(x);
-    omega = 2 * pi * k / N;
-    cos_omega = cos(omega);
-    sin_omega = sin(omega);
-    coeff = 2 * cos_omega;
-
-    Q1 = 0;
-    Q2 = 0;
-    for n = 1:N
-        Q0 = x(n) + coeff * Q1 - Q2;
-        Q2 = Q1;
-        Q1 = Q0;
-    end
-
-    real_part = (Q1 - Q2 * cos_omega);
-    imag_part = (Q2 * sin_omega);
-
-    magnitude = real_part + 1i * imag_part;
-end

### 2024-08-22 matlab_scripts/goertzel_test2.m

@@ -1,57 +1,0 @@
-clear;
-close all;
-clc;
-
-
-% Parameters
-fs = 1000;            % Sampling frequency
-f = 100;              % Carrier frequency
-duration = 4;         % Duration of the signal in seconds
-N = fs * duration;    % Total number of samples
-t = (0:N-1)/fs;       % Time vector
-
-% Create a signal with amplitude switching
-signal = [sin(2*pi*f*t(1:N/4)), 0.5*sin(2*pi*f*t(N/4+1:N/2)), ...
-          sin(2*pi*f*t(N/2+1:3*N/4)), 0.5*sin(2*pi*f*t(3*N/4+1:end))];
-
-% Initialize Goertzel algorithm parameters
-k = round(f*duration);            % Frequency bin
-omega = 2 * pi * k / N;
-coeff = 2 * cos(omega);
-s_prev = 0;
-s_prev2 = 0;
-
-% Segment size for analysis (e.g., 1 second)
-segment_size = fs;
-
-% Initialize array to store power of the carrier frequency
-power = zeros(1, duration);
-
-for i = 1:duration
-    s_prev = 0;
-    s_prev2 = 0;
-    for j = 1:segment_size
-        s = signal((i-1)*segment_size + j) + coeff * s_prev - s_prev2;
-        s_prev2 = s_prev;
-        s_prev = s;
-    end
-    % Calculate power
-    power(i) = s_prev2^2 + s_prev^2 - coeff * s_prev * s_prev2;
-end
-
-% Normalize power to see the variations clearly
-normalized_power = power / max(power);
-
-% Plot the results
-figure;
-subplot(2,1,1);
-plot(t, signal);
-title('Signal with Amplitude Switching');
-xlabel('Time (s)');
-ylabel('Amplitude');
-
-subplot(2,1,2);
-stem(1:duration, normalized_power);
-title('Normalized Power of Carrier Frequency over Time');
-xlabel('Time (s)');
-ylabel('Normalized Power');

### 2024-08-22 matlab_scripts/goertzel_test3.m

@@ -1,61 +1,0 @@
-clear;
-close all;
-clc;
-
-
-
-% Parameters
-fs = 1000;            % Sampling frequency
-f = 100;              % Carrier frequency
-total_duration = 8;   % Total duration of the signal in seconds
-N = fs * total_duration;  % Total number of samples
-t = (0:N-1)/fs;       % Time vector
-
-% Create a signal with amplitude switching every second
-signal = [sin(2*pi*f*t(1:N/4)), 0.5*sin(2*pi*f*t(N/4+1:N/2)), ...
-          sin(2*pi*f*t(N/2+1:3*N/4)), 0.5*sin(2*pi*f*t(3*N/4+1:end))];
-
-% Parameters for Goertzel algorithm
-segment_duration = 0.5;   % Duration of each segment in seconds
-segment_size = fs * segment_duration; % Segment size in samples
-num_segments = total_duration / segment_duration; % Number of segments
-
-% Initialize Goertzel algorithm parameters
-k = round(f*segment_duration);  % Frequency bin for the segment
-omega = 2 * pi * k / segment_size;
-coeff = 2 * cos(omega);
-
-% Initialize array to store power of the carrier frequency
-power = zeros(1, num_segments);
-
-% Loop through each segment and apply Goertzel algorithm
-for seg = 1:num_segments
-    s_prev = 0;
-    s_prev2 = 0;
-    start_idx = (seg-1)*segment_size + 1;
-    end_idx = seg*segment_size;
-    for j = start_idx:end_idx
-        s = signal(j) + coeff * s_prev - s_prev2;
-        s_prev2 = s_prev;
-        s_prev = s;
-    end
-    % Calculate power
-    power(seg) = s_prev2^2 + s_prev^2 - coeff * s_prev * s_prev2;
-end
-
-% Normalize power to see the variations clearly
-normalized_power = power / max(power);
-
-% Plot the results
-figure;
-subplot(2,1,1);
-plot(t, signal);
-title('Signal with Amplitude Switching');
-xlabel('Time (s)');
-ylabel('Amplitude');
-
-subplot(2,1,2);
-stem((1:num_segments)*segment_duration, normalized_power);
-title('Normalized Power of Carrier Frequency over Time');
-xlabel('Time (s)');
-ylabel('Normalized Power');

### 2024-08-22 matlab_scripts/goertzel_test4.m

@@ -1,91 +1,0 @@
-clear;
-close all;
-clc;
-
-
-
-
-% Parameters
-fs = 1000;            % Sampling frequency
-f = 100;              % Carrier frequency
-total_duration = 8;   % Total duration of the signal in seconds
-N = fs * total_duration;  % Total number of samples
-t = (0:N-1)/fs;       % Time vector
-
-% Create a signal with amplitude switching every second
-signal = [sin(2*pi*f*t(1:N/4)), 0.5*sin(2*pi*f*t(N/4+1:N/2)), ...
-          sin(2*pi*f*t(N/2+1:3*N/4)), 0.5*sin(2*pi*f*t(3*N/4+1:end))];
-
-% Parameters for Goertzel algorithm
-segment_duration = 1;   % Duration of each segment in seconds
-segment_size = fs * segment_duration; % Segment size in samples
-num_segments = total_duration / segment_duration; % Number of segments
-
-% Initialize Goertzel algorithm parameters
-k = round(f*segment_duration);  % Frequency bin for the segment
-omega = 2 * pi * k / segment_size;
-coeff = 2 * cos(omega);
-
-% Initialize array to store power of the carrier frequency
-power = zeros(1, num_segments);
-
-% Loop through each segment and apply Goertzel algorithm
-for seg = 1:num_segments
-    s_prev = 0;
-    s_prev2 = 0;
-    start_idx = (seg-1)*segment_size + 1;
-    end_idx = seg*segment_size;
-    for j = start_idx:end_idx
-        s = signal(j) + coeff * s_prev - s_prev2;
-        s_prev2 = s_prev;
-        s_prev = s;
-    end
-    % Calculate power
-    power(seg) = s_prev2^2 + s_prev^2 - coeff * s_prev * s_prev2;
-end
-
-% Normalize power to see the variations clearly
-normalized_power = power / max(power);
-
-% Parameters for adaptive threshold
-window_size = 3; % Size of the moving window
-alpha = 1.5;    % Multiplier for standard deviation to define the threshold
-
-% Initialize array to store adaptive thresholds
-adaptive_threshold = zeros(1, num_segments);
-
-% Calculate adaptive thresholds
-for i = window_size:num_segments
-    window_data = normalized_power(i-window_size+1:i);
-    moving_avg = mean(window_data);
-    moving_std = std(window_data);
-    adaptive_threshold(i) = moving_avg - alpha * moving_std;
-end
-
[…]

### 2024-08-22 matlab_scripts/main_goertzel_derivative_running.m

@@ -1,142 +1,0 @@
-clear;
-close all;
-clc;
-
-%% Parameter Section
-
-%Sampling parameters
-fs = 200e3; %Sampling frequency in Hz
-duration = 5; %Sampling duration in s
-
-%AWGN-Channel parameters
-awgn_snr = 0; %SNR of the AWGN-channel in dB
-
-
-
-%% Signal Creation Section
-
-%Create time vector
-t = 0:1/fs:duration;
-
-%Create a variable with the number of samples
-N_samples = length(t);
-
-%Carrier signal (cos at 77.5kHz)
-fc = 77.5e3; %Carrier frequency of the DCF77 transmitter in Hz (77.5kHz)
-carrier_signal = cos(2*pi*fc*t);
-
-%Time signal (square wave with frequency of 1Hz, 80% duty cycle, and a range from 0 to 1)
-time_signal = 0.5*(square(-2*pi*1*t, 80) + 1);
-
-%Create the DCF77 signal by using Amplitude Modulation (carrier is reduced to 15% during the gap)
-dcf77_signal = (0.85*time_signal + 0.15) .* carrier_signal;
-
-
-
-%% AWGN-Channel Section
-
-%Add noise by passing the DCF77 signal through an AWGN-Channel
-dcf77_signal_noise = awgn(dcf77_signal, awgn_snr, 'measured');
-
-
-
-%% Goertzel Section
-
-%Goertzel parameters
-goertzel_N = N_samples;                             % Length of signal
-goertzel_k = round(fc * goertzel_N / fs);           % Bin index corresponding to carrier frequency
-goertzel_omega = (2*pi*goertzel_k) / goertzel_N;    % Frequency bin
-goertzel_coeff = 2*cos(goertzel_omega);             % Goertzel coefficient
-
-%Initialize Goertzel variables
-s_prev = 0;
-s_prev2 = 0;
-goertzel_magnitude_vec = zeros(1, goertzel_N);
-
-%Goertzel algorithm execution
-for n = 1:goertzel_N
-    s = dcf77_signal_noise(n) + goertzel_coeff * s_prev - s_prev2;
-    s_prev2 = s_prev;
-    s_prev = s;
[…]

### 2024-08-22 matlab_scripts/main_script_bandpass_sampling_adaptive_threshold.m

@@ -5,17 +5,19 @@ clc;
 %% Simulation Parameter Section
 
 %Sampling parameters
-fs = 200e3; %Sampling frequency in Hz
-duration = 5; %Overall sampling duration in s (duration of the simulation)
+fs = 24e3; %Sampling frequency in Hz
+duration = 24; %Overall sampling duration in s (duration of the simulation)
 
 %AWGN-Channel parameters
-awgn_snr = -15; %SNR after the AWGN-channel in dB
+awgn_snr = -5; %SNR after the AWGN-channel in dB
 
 %Goertzel Macro parameters
 goertzel_segment_duration = 0.01; %Duration of the Goertzel algorithm segment in s
 
 %Detector parameters
-det_threshold = 0.15; %Threshold for the detector
+det_avg_time = 10; %Time of the Exponential Moving Average in s
+
+
 
 %% Signal Creation Section
 
@@ -30,21 +32,32 @@ fc = 77.5e3; %Storing the carrier frequency of the DCF77 transmitter in Hz (77.5
 carrier_signal = cos(2*pi*fc*t);
 
 %Time signal (square wave with frequency of 1Hz, 80% duty cycle, and a range from 0 to 1)
-time_code_signal = 0.5*(square(-2*pi*1*t, 80) + 1);
+one_samples_80 = round(0.8 * fs);
+one_samples_90 = round(0.9 * fs);
+
+rect_duty_80 = [zeros(1, fs - one_samples_80), ones(1, one_samples_80)]; %Rect, duty-cycle 80%, starting at 0
+rect_duty_90 = [zeros(1, fs - one_samples_90), ones(1, one_samples_90)]; %Rect, duty-cycle 90%, starting at 0
+
+time_code_signal = [];
+for i = 1:ceil(duration)
+    if mod(i, 3) == 0
+        time_code_signal = [time_code_signal, rect_duty_90];
+    else
+        time_code_signal = [time_code_signal, rect_duty_80];
+    end
+end
+time_code_signal = time_code_signal(1:N_samples-1);
+time_code_signal = [zeros(1, 1), time_code_signal];
 
 %Creating the DCF77 signal by using Amplitude Modulation (carrier is reduced to 15% during the gap)
 dcf77_signal = (0.85*time_code_signal + 0.15) .* carrier_signal;
-
-
-
-%% AWGN-Channel Section
 
 %Add noise by passing the DCF77 signal through an AWGN-Channel
[…]

### 2024-08-22 matlab_scripts/main_script_dynamic_detection.m

@@ -1,212 +1,0 @@
-clear;
-close all;
-clc;
-
-%% Simulation Parameter Section
-
-%Sampling parameters
-fs = 200e3; %Sampling frequency in Hz
-duration = 24; %Overall sampling duration in s (duration of the simulation)
-
-%AWGN-Channel parameters
-awgn_snr = -10; %SNR after the AWGN-channel in dB
-
-%Goertzel Macro parameters
-goertzel_segment_duration = 0.01; %Duration of the Goertzel algorithm segment in s
-
-%Detector parameters
-det_threshold = 0.15; %Threshold for the detector
-
-%% Signal Creation Section
-
-%Creating a time vector for the duration of the simulation
-t = 0:1/fs:duration;
-
-%Creating a variable with the number of samples
-N_samples = length(t);
-
-%Carrier signal (cos at 77.5kHz)
-fc = 77.5e3; %Storing the carrier frequency of the DCF77 transmitter in Hz (77.5kHz)
-carrier_signal = cos(2*pi*fc*t);
-
-%Time signal (square wave with frequency of 1Hz, 80% duty cycle, and a range from 0 to 1)
-one_samples_80 = round(0.8 * fs);
-one_samples_90 = round(0.9 * fs);
-
-rect_duty_80 = [zeros(1, fs - one_samples_80), ones(1, one_samples_80)]; %Rect, duty-cycle 80%, starting at 0
-rect_duty_90 = [zeros(1, fs - one_samples_90), ones(1, one_samples_90)]; %Rect, duty-cycle 90%, starting at 0
-
-time_code_signal = [];
-for i = 1:ceil(duration)
-    if mod(i, 3) == 0
-        time_code_signal = [time_code_signal, rect_duty_90];
-    else
-        time_code_signal = [time_code_signal, rect_duty_80];
-    end
-end
-time_code_signal = time_code_signal(1:N_samples-1);
-time_code_signal = [zeros(1, 1), time_code_signal];
-
-%Creating the DCF77 signal by using Amplitude Modulation (carrier is reduced to 15% during the gap)
-dcf77_signal = (0.85*time_code_signal + 0.15) .* carrier_signal;
-
-
-
-%% AWGN-Channel Section
-
-%Add noise by passing the DCF77 signal through an AWGN-Channel
-dcf77_signal_noise = awgn(dcf77_signal, awgn_snr, 'measured');
-
-
-
[…]

### 2024-08-22 matlab_scripts/main_script_normalized_detection.m

@@ -1,198 +1,0 @@
-clear;
-close all;
-clc;
-
-%% Simulation Parameter Section
-
-%Sampling parameters
-fs = 200e3; %Sampling frequency in Hz
-duration = 6; %Overall sampling duration in s (duration of the simulation)
-
-%AWGN-Channel parameters
-awgn_snr = -15; %SNR after the AWGN-channel in dB
-
-%Goertzel Macro parameters
-goertzel_segment_duration = 0.01; %Duration of the Goertzel algorithm segment in s
-
-%Detector parameters
-det_threshold = 0.15; %Threshold for the detector
-
-%% Signal Creation Section
-
-%Creating a time vector for the duration of the simulation
-t = 0:1/fs:duration;
-
-%Creating a variable with the number of samples
-N_samples = length(t);
-
-%Carrier signal (cos at 77.5kHz)
-fc = 77.5e3; %Storing the carrier frequency of the DCF77 transmitter in Hz (77.5kHz)
-carrier_signal = cos(2*pi*fc*t);
-
-%Time signal (square wave with frequency of 1Hz, 80% duty cycle, and a range from 0 to 1)
-one_samples_80 = round(0.8 * fs);
-one_samples_90 = round(0.9 * fs);
-
-rect_duty_80 = [zeros(1, fs - one_samples_80), ones(1, one_samples_80)]; %Rect, duty-cycle 80%, starting at 0
-rect_duty_90 = [zeros(1, fs - one_samples_90), ones(1, one_samples_90)]; %Rect, duty-cycle 90%, starting at 0
-
-time_code_signal = [];
-for i = 1:ceil(duration)
-    if mod(i, 3) == 0
-        time_code_signal = [time_code_signal, rect_duty_90];
-    else
-        time_code_signal = [time_code_signal, rect_duty_80];
-    end
-end
-time_code_signal = time_code_signal(1:N_samples-1);
-time_code_signal = [zeros(1, 1), time_code_signal];
-
-%Creating the DCF77 signal by using Amplitude Modulation (carrier is reduced to 15% during the gap)
-dcf77_signal = (0.85*time_code_signal + 0.15) .* carrier_signal;
-
-
-
-%% AWGN-Channel Section
-
-%Add noise by passing the DCF77 signal through an AWGN-Channel
-dcf77_signal_noise = awgn(dcf77_signal, awgn_snr, 'measured');
-
-
-
[…]

### 2024-08-22 matlab_scripts/test_signal.m

@@ -1,35 +1,0 @@
-clear;
-close all;
-clc;
-
-% Parameters
-fs = 1000; % Sampling frequency in Hz
-duration = 1; % Duration of the signal in seconds
-duty_cycle = 0.8; % Duty cycle (80%)
-
-% Time vector
-t = 0:1/fs:duration;
-
-% Number of samples
-num_samples = length(t);
-
-% Calculate the number of samples for the pulse width and gap
-pulse_width_samples = round(duty_cycle * num_samples);
-gap_samples = num_samples - pulse_width_samples;
-
-% Create the rectangular pulse with the gap at the beginning
-rect_signal = [zeros(1, gap_samples), ones(1, pulse_width_samples)];
-
-% Truncate or extend the signal to match the duration exactly
-rect_signal = rect_signal(1:num_samples);
-
-% Plot the signal
-figure;
-plot(t, rect_signal, 'LineWidth', 1.5);
-xlabel('Time (s)');
-ylabel('Amplitude');
-title('Rectangular Pulse with 80% Duty Cycle and Gap at Beginning');
-grid on;
-
-% Optionally, you can save the signal to a file
-audiowrite('rect_signal.wav', rect_signal, fs);

### 2024-08-22 paper/main.tex
Added comments to the script. Added reference for EMA to the paper

@@
 As the values of the Goertzel algorithm will follow the pattern of the signal's amplitude being switched between \SI{15}{\percent} and \SI{100}{\percent}, the detection can be done by comparing the value of the current sample to a threshold.
-To compensate the changing of magnitude of the Goertzel algorithm's values that is caused by the current receiving situation, an Exponential Moving Average (EMA) is calculated by using \eqref{eqn:ema} and employed to create an adaptive threshold.
+To compensate the changing of magnitude of the Goertzel algorithm's values that is caused by the current receiving situation, an Exponential Moving Average (EMA) is calculated by using \eqref{eqn:ema} and employed to create an adaptive threshold \cite{b11}.
 \begin{equation}
@@
 \end{enumerate}
+These sections will be discussed in the following.
+
+\subsection{Simulation Parameter Section}
+In the Simulation Parameter Section,
 
@@
 \bibitem{b8} K. Banks, ``The Goertzel Algorithm,'' 2002, Internet Article. [Online]. Available: https://courses.cs.washington.edu/courses/cse466/12au/calendar/Goertzel-EETimes.pdf
+\bibitem{b11} R. G. Lyons, ``Setting the 3-dB Cutoff Frequency of an Exponential Averager,'' 2012, Internet Article. [Online]. Available: https://www.dsprelated.com/showarticle/182.php
 \end{thebibliography}

### 2024-08-22 matlab_scripts/main_script_bandpass_sampling_adaptive_threshold.m

@@ -11,7 +11,7 @@ duration = 24; %Overall sampling duration in s (duration of the simulation)
 %AWGN-Channel parameters
 awgn_snr = -5; %SNR after the AWGN-channel in dB
 
-%Goertzel Macro parameters
+%Goertzel macro parameters
 goertzel_segment_duration = 0.01; %Duration of the Goertzel algorithm segment in s
 
 %Detector parameters
@@ -46,8 +46,8 @@ for i = 1:ceil(duration)
         time_code_signal = [time_code_signal, rect_duty_80];
     end
 end
-time_code_signal = time_code_signal(1:N_samples-1);
-time_code_signal = [zeros(1, 1), time_code_signal];
+time_code_signal = time_code_signal(1:N_samples-1); %Cutting to size
+time_code_signal = [zeros(1, 1), time_code_signal]; %Inserting a zero at the beginning
 
 %Creating the DCF77 signal by using Amplitude Modulation (carrier is reduced to 15% during the gap)
 dcf77_signal = (0.85*time_code_signal + 0.15) .* carrier_signal;
@@ -155,7 +155,7 @@ ylabel('Amplitude');
 
 subplot(7,1,2);
 plot(t, time_code_signal);
-title('Time-Code signal');
+title('Time-Code Signal');
 xlabel('Time (s)');
 ylabel('Amplitude');
 
@@ -175,20 +175,20 @@ subplot(7,1,5);
 stem(t_goertzel_segments_results, goertzel_segments_magnitudes);
 hold on;
 stairs(t_goertzel_segments_results, detector_threshold, 'Color', 'red');
-title('Result Goertzel algorithm and detector threshold');
+title('Result Goertzel algorithm and Detector Threshold');
 xlabel('Time (s)');
 ylabel('Magnitude');
 hold off;
 
 subplot(7,1,6);
 stairs(t_goertzel_segments_results, exp_mov_avg);
-title('Rolling average of the detector');
+title('EMA of the detector');
 xlabel('Time (s)');
 ylabel('Value');
 
 subplot(7,1,7);
 stairs(t_goertzel_segments_results, dcf77_reconstructed);
-title('Time-Code signal after detector');
+title('Time-Code Signal after detector');
 xlabel('Time (s)');
 ylabel('Value');
 
@@ -197,12 +197,12 @@ ylabel('Value');
 figure
[…]

### 2024-08-22 paper/main.tex
Added first section of the description of the matlab script

@@
 \usepackage{tabularray}
+\usepackage{matlab-prettifier}
 
@@
 \subsection{Simulation Parameter Section}
-In the Simulation Parameter Section,
+In the Simulation Parameter Section, static parameters for the following sections are defined.
+These include the sampling frequency $f_{s}$, the duration of the whole simulation, the wanted SNR that the signal should have after passing the Additive White Gaussian Noise (AWGN)-Channel, the duration of the Goertzel algorithm segments, and the time that should
+be taken into account by the EMA.
+By adjusting these parameters, the behavior of the receiver can be altered to, e.g. to simulate different receiving conditions.
+
+\subsection{Signal Creation Section}
+
+\begin{lstlisting}[style=Matlab-editor]
+    %Creating the DCF77 signal by using Amplitude Modulation (carrier is reduced to 15% during the gap)
+    dcf77_signal = (0.85*time_code_signal + 0.15) .* carrier_signal;
+
+    %Add noise by passing the DCF77 signal through an AWGN-Channel
+    dcf77_signal_noise = awgn(dcf77_signal, awgn_snr, 'measured');
+\end{lstlisting}
 

### 2024-08-22 paper/main.tex
Re-formatted hyperlinks in references.

@@
 \usepackage{tabularray}
+\usepackage[hyphens]{url}
 \usepackage{matlab-prettifier}
@@
 
+\Urlmuskip=0mu plus 1mu
 \begin{thebibliography}{00}
-\bibitem{b1} -, ``DCF77,'' 2024, Wikipedia entry. [Online]. Available: https://de.wikipedia.org/wiki/DCF77
+\bibitem{b1} -, ``DCF77,'' 2024, Wikipedia entry. [Online]. Available: \url{https://de.wikipedia.org/wiki/DCF77}
 \bibitem{b2} D.
@@
 Bauch, ``Zeit- und Normalfrequenzverbreitung mit DCF77,'' PTB Mitteilungen, 2004, [Online].
-Available: https://www.ptb.de/cms/fileadmin/internet/fachabteilungen/abteilung\_4/4.4\_zeit\_und\_frequenz/4.42/dcf77.pdf
+Available: \url{https://www.ptb.de/cms/fileadmin/internet/fachabteilungen/abteilung_4/4.4_zeit_und_frequenz/4.42/dcf77.pdf}
 \bibitem{b3} D.
@@
 Bauch, ``Zeit- und Normalfrequenzverbreitung mit DCF77: 1959-2009 und darüber hinaus,'' PTB Mitteilungen, 2009, [Online].
-Available: https://www.ptb.de/cms/fileadmin/internet/fachabteilungen/abteilung\_4/4.4\_zeit\_und\_frequenz/pdf/2009\_Bauch\_PTBM\_\_DCF77.pdf
+Available: \url{https://www.ptb.de/cms/fileadmin/internet/fachabteilungen/abteilung_4/4.4_zeit_und_frequenz/pdf/2009_Bauch_PTBM__DCF77.pdf}
 \bibitem{b4} P.
 Hetzel, ``Time dissemination via the LF transmitter DCF77 using a pseudo-random phase-shift keying of the carrier,'' PTB Braunschweig, 1988, [Online].
-Available: https://www.ptb.de/cms/fileadmin/internet/fachabteilungen/abteilung\_4/4.4\_zeit\_und\_frequenz/pdf/5\_1988\_Hetzel\_-\_Proc\_EFTF\_88.pdf
-\bibitem{b5} -, ``DCF77 webpage,'' 2024, Official page of the PTB [Online]. Available: https://www.ptb.de/cms/en/ptb/fachabteilungen/abt4/fb-44/ag-442/dissemination-of-legal-time/dcf77.html
+Available: \url{https://www.ptb.de/cms/fileadmin/internet/fachabteilungen/abteilung_4/4.4_zeit_und_frequenz/pdf/5_1988_Hetzel_-_Proc_EFTF_88.pdf}
+\bibitem{b5} -, ``DCF77 webpage,'' 2024, Official page of the PTB [Online]. Available: \url{https://www.ptb.de/cms/en/ptb/fachabteilungen/abt4/fb-44/ag-442/dissemination-of-legal-time/dcf77.html}
 \bibitem{b6} R. G. Lyons, ``Understanding Digital Signal Processing,'' Third Edition, Prentice Hall, 2010.
-\bibitem{b9} J. Hoffmann, ``Sampling bandpass signals,'' 2021, Internet Article. [Online]. Available: https://www.dsprelated.com/showarticle/1407.php
-\bibitem{b10} F. Zaplata and M. Kasal, ``SDR Implementation for DCF77,'', 2013, IEEE Paper. [Online]. Available: https://ieeexplore.ieee.org/document/6530943
-\bibitem{b7} -, ``Goertzel algorithm,'' 2024, Wikipedia entry. [Online]. Available: https://en.wikipedia.org/wiki/Goertzel\_algorithm
-\bibitem{b8} K. Banks, ``The Goertzel Algorithm,'' 2002, Internet Article. [Online]. Available: https://courses.cs.washington.edu/courses/cse466/12au/calendar/Goertzel-EETimes.pdf
-\bibitem{b11} R. G. Lyons, ``Setting the 3-dB Cutoff Frequency of an Exponential Averager,'' 2012, Internet Article. [Online]. Available: https://www.dsprelated.com/showarticle/182.php
+\bibitem{b9} J. Hoffmann, ``Sampling bandpass signals,'' 2021, Internet Article. [Online]. Available: \url{https://www.dsprelated.com/showarticle/1407.php}
+\bibitem{b10} F. Zaplata and M. Kasal, ``SDR Implementation for DCF77,'', 2013, IEEE Paper. [Online]. Available: \url{https://ieeexplore.ieee.org/document/6530943}
+\bibitem{b7} -, ``Goertzel algorithm,'' 2024, Wikipedia entry. [Online]. Available: \url{https://en.wikipedia.org/wiki/Goertzel_algorithm}
+\bibitem{b8} K. Banks, ``The Goertzel Algorithm,'' 2002, Internet Article. [Online]. Available: \url{https://courses.cs.washington.edu/courses/cse466/12au/calendar/Goertzel-EETimes.pdf}
+\bibitem{b11} R. G. Lyons, ``Setting the 3-dB Cutoff Frequency of an Exponential Averager,'' 2012, Internet Article. [Online]. Available: \url{https://www.dsprelated.com/showarticle/182.php}
 \end{thebibliography}

### 2024-08-24 paper/main.tex
Progress in explaining the simulation

@@
 
-\section{MATLAB Simulation of the Receiver}
-To verify and underline the working principle of the receiver, a simulation of the whole system was created using MATLAB.
+\section{Simulation of the receiver in MATLAB}
+To verify and further explain the working principle of the receiver, a simulation of the whole system was created using MATLAB.
 The whole simulation was divided into five sections to allow for a clear structure:
@@
 \subsection{Simulation Parameter Section}
-In the Simulation Parameter Section, static parameters for the following sections are defined.
-These include the sampling frequency $f_{s}$, the duration of the whole simulation, the wanted SNR that the signal should have after passing the Additive White Gaussian Noise (AWGN)-Channel, the duration of the Goertzel algorithm segments, and the time that should
-be taken into account by the EMA.
-By adjusting these parameters, the behavior of the receiver can be altered to, e.g. to simulate different receiving conditions.
+In the Simulation Parameter Section, static parameters for the following sections of the simulation are defined.
+These include the sampling frequency $f_{s}$, the duration of the whole simulation, the SNR that the signal should have after passing the Additive White Gaussian Noise (AWGN)-Channel, the frequency to be analyzed by the Goertzel algoritm, the duration of the Goertzel algorithm segments, and the time that should be taken into account by the EMA.
+By adjusting these parameters, the receiving situation and the receiver's behavior can be altered to, e.g. to simulate different receiving conditions and examine the system's performance.
 
 \subsection{Signal Creation Section}
+The Signal Creation Section implements the creation of the amplitude-modulated DCF77 signal.
+First, a time vector with the length of the simulation's duration and a step size that depends on $f_{s}$ is created and its length stored in a variable.
+A vector containing the carrier signal at $f_{c} = \SI{77.5}{\kilo\hertz}$ by using this time vector is created afterwards.
+For the amplitude modulation of the carrier, the time code signal containing the binary encoded symbols needs to be created.
+As this signal is used for multiplication with the carrier, it needs to consist of rects with a period length of \SI{1}{\second} and a gap of either \SI{200}{\milli\second} or \SI{100}{\milli\second} at the beginning.
+These rects are prepared by creating and filling two vectors with the matching amount of zeros followed and filling the rest with ones.
+A vector containing the time code signal with alternating symbols is created by concatenating these vectors inside a for loop.
+The number of iterations is given by rounding up the simulation's duration, because each symbol has the duration of \SI{1}{\second}.
+The vector is then cut down afterwards to exactly match the length of the time vector and therefore the duration of the simulation.
+To finally create the DCF77 signal, the vector with the time code signal is scaled and multiplied element-wise with the vector containing the carrier signal.
+This signal is then passed through a AWGN-Channel, creating a signal with a defined SNR to allow the simulation of different receiving conditions.
+
+\subsection{Goertzel Algorithm Section}
 

### 2024-08-24 matlab_scripts/main_script_bandpass_sampling_adaptive_threshold.m

@@ -12,6 +12,7 @@ duration = 24; %Overall sampling duration in s (duration of the simulation)
 awgn_snr = -5; %SNR after the AWGN-channel in dB
 
 %Goertzel macro parameters
+goertzel_analyzation_freq = 5.5e3; %Analyzation frequency of the Goertzel algorithm in Hz
 goertzel_segment_duration = 0.01; %Duration of the Goertzel algorithm segment in s
 
 %Detector parameters
@@ -38,9 +39,10 @@ one_samples_90 = round(0.9 * fs);
 rect_duty_80 = [zeros(1, fs - one_samples_80), ones(1, one_samples_80)]; %Rect, duty-cycle 80%, starting at 0
 rect_duty_90 = [zeros(1, fs - one_samples_90), ones(1, one_samples_90)]; %Rect, duty-cycle 90%, starting at 0
 
+%Concatenating the symbols after each other to create the time code signal
 time_code_signal = [];
 for i = 1:ceil(duration)
-    if mod(i, 3) == 0
+    if mod(i, 2) == 0 %Alternating the symbols
         time_code_signal = [time_code_signal, rect_duty_90];
     else
         time_code_signal = [time_code_signal, rect_duty_80];
@@ -65,7 +67,7 @@ goertzel_num_segments = duration / goertzel_segment_duration; %Calculating the n
 t_goertzel_segments_results = (1:goertzel_num_segments)*goertzel_segment_duration; %Create a time vector for the results for plotting
 
 %Goertzel parameters
-goertzel_k = round(5500 * goertzel_segment_duration);
+goertzel_k = round(goertzel_analyzation_freq * goertzel_segment_duration);
 goertzel_omega = 2 * pi * goertzel_k / goertzel_segment_size;
 goertzel_coeff = 2 * cos(goertzel_omega);
 

### 2024-08-24 paper/main.tex
Explaination of the Goertzel algorithm in matlab finished

@@
     |X(f_{a})|^2 = Q_{1}^2 + Q_{2}^2 - Q_{1} \cdot Q_{2} \cdot 2 \cdot \cos(\omega_{g})
+    \label{eqn:goertzel-mag}
 \end{equation}
@@
     k = \left\lfloor \frac{N \cdot f_{a}}{f_{s}} \right\rceil
+    \label{eqn:goertzel-k}
 \end{equation}
@@
     w_g = \frac{2\pi \cdot k}{N}
+    \label{eqn:goertzel-omega}
 \end{equation}
@@
 \subsection{Goertzel Algorithm Section}
+As described in the chapter explaining the receiver's working principle, the samples are processed in batches whose size is defined by the duration of the Goertzel algorithm's execution.
+Before its execution, the parameters needed for the segment-wise execution, such as the segment size, the number of segments, and a time vector containing the exact points in time where results were available (later used for plotting), are calculated based on the
+sampling rate $f_{s}$, and the pre-defined duration of analyzation.
+The parameters for the Goertzel algorithm itself, $k$, $\omega_{g}$ and $2 \cdot cos(\omega_{g})$ are then calculated by using the formulas \eqref{eqn:goertzel-k} and \eqref{eqn:goertzel-omega}.
+\par
+Three variables Q\_0, Q\_1, and Q\_2 for the implementation of the Goertzel algorithm's formula (see \eqref{eqn:goertzel} and \eqref{eqn:goertzel-mag}) and a vector for storing the segments' results are initialized.
+The segment-wise analyzation is then implemented by using an outer and an inner for-loop.
+The outer for-loop iterates over the number of segments, resetting Q\_0, Q\_1, and Q\_2 followed by calculating the index of the first and the last sample of the current segment, providing the limits for the inner for-loop.
+Inside the inner for-loop, the formula \eqref{eqn:goertzel} of the IIR-Part is implemented by calculating the new output of the structure and shifting the previous results for the next iteration.
+After all samples of the segment were processed, the magnitude is calculated by the implementation of \eqref{eqn:goertzel-mag} using the values stored in Q\_1 and Q\_2 and taking the square root of the result.
+The result is then stored inside the prepared vector for the segments' results.
 

### 2024-08-25 paper/main.tex
Progress last section

--- 2024-08-24 paper/main.tex
@@
     \end{split}
+    \label{eqn:ema-alpha}
 \end{equation}
 This provides a stable and slowly changing average, as it is putting more weight on the past samples and leaves minimal influence to the most recent sample.
-The decision is then done by comparing the current sample to a threshold calculated by multiplying the current value of the average with $0.575$ (the middle bewteen \SI{15}{\percent} and \SI{100}{\percent}) and a scaling factor of $\frac{1}{0.8725}$.
+The decision is then done by comparing the current sample to a threshold calculated by multiplying the current value of the average with $0.575$ (the middle bewteen \SI{15}{\percent} and \SI{100}{\percent}) and a scaling factor of $\frac{1}{0.8725}$:
+\begin{equation}
+    threshold = 0.575 \cdot \frac{1}{0.8725} \cdot y[t]
+    \label{eqn:thresh}
+\end{equation}
 The scaling factor is needed as the average percentage of time where the signal where is equal to \SI{100}{percent} is \SI{87.25}{\percent} (assuming an equal distribution between symbols representing a binary 1 and a 0).
@@
 \subsection{Goertzel Algorithm Section}
+As described in the chapter explaining the receiver's working principle, the sampled DCF77 signal is processed in segments whose size is defined by the duration of the Goertzel algorithm's execution.
+Before processing the samples, the parameters needed for the segment-wise execution are prepared.
+These include the segment size, the number of segments, and a time vector containing the exact points in time where segments' results were available (later used for plotting).
+The parameters for the Goertzel algorithm itself, $k$, $\omega_{g}$ and $2 \cdot cos(\omega_{g})$ are then calculated by using the formulas \eqref{eqn:goertzel-k} and \eqref{eqn:goertzel-omega}.
+\par
+Three variables, Q\_0, Q\_1, and Q\_2, are initialized for the implementation of the Goertzel algorithm's formula (see \eqref{eqn:goertzel} and \eqref{eqn:goertzel-mag}) and vector for storing the segments' results is prepared.
+The segment-wise analyzation is then implemented by using an outer and an inner for-loop.
+The outer for-loop iterates over the number of segments, first resetting Q\_0, Q\_1, and Q\_2 followed by calculating the index of the first and the last sample of the current segment to provide the limits for the inner for-loop.
+Inside the inner for-loop, the formula \eqref{eqn:goertzel} of the IIR-Part is implemented by calculating the new output of the structure and shifting the previous results in each iteration.
+After all samples of the segment were processed (the inner for-loop finished), the magnitude is calculated by the implementation of \eqref{eqn:goertzel-mag}, using the values stored in Q\_1 and Q\_2 and taking the square root of the result.
+The result is then stored inside the prepared vector for the segments' results.
 
-\begin{lstlisting}[style=Matlab-editor]
-    %Creating the DCF77 signal by using Amplitude Modulation (carrier is reduced to 15% during the gap)
-    dcf77_signal = (0.85*time_code_signal + 0.15) .* carrier_signal;
+\subsection{Detection Section}
+The Detection Section processes the Goertzel algorithm's results of the segments to retrieve back the time code signal.
+At the beginning, three vectors are initialized to store the value of the EMA, the detector's threshold, and the time code signal.
+The parameter $\alpha$ of the EMA is calculated by the implementation of \eqref{eqn:ema-alpha} and stored in a variable.
+The segments are then processed inside a for-loop.
+First, the EMA is calculated by the implementation of \eqref{eqn:ema} and stored inside a vector.
+Then, the threshold is calculated based on the value of the EMA and the scaling factor (see \eqref{eqn:thresh}) and stored inside a vector.
+The decision whether the result of the current section was caused by the signal's amplitude being equal to either \SI{15}{\percent} or
+\SI{100}{\percent} is done by comparing the value of the result to the calculated threshold.
+If the value is smaller than the threshold, it is assumed that it was caused by the transmitter's amplitude being equal to \SI{15}{\percent} and
+a 0 is stored in the vector of the reconstructed time code signal.
+If the value is bigger than the threshold, it is assumed that it was caused by the transmitter's amplitude being equal to \SI{100}{\percent} and a 1 is stored in the vector of the reconstructed time code signal.
 
-    %Add noise by passing the DCF77 signal through an AWGN-Channel
-    dcf77_signal_noise = awgn(dcf77_signal, awgn_snr, 'measured');
-\end{lstlisting}
+\subsection{FFT and Plot Section}
+To allow the a visualization and verification of the simulation's results, a section for plotting was added.
+This also includes two FFTs, analyzing signal before and after passing the AWGN-Channel to allow the obervation of the SNR.
+The FFTs are prepared before the plotting takes place by using MATLAB's internal functions for calculating and shifting the results.
+The scaling is adjusted to normalize the DFT gain and the logarithm of the results is calculated.
+Besides the calculation of the FFTs themselves, a vector containing the bins' frequencies is prepared for plotting.
+The results of the two FFTs are then plotted in figure.
+\par
+In a second figure, multiple time domain plots are arranged to allow the observation of the receiver's stages.
+These include plots of the time code signal, the DCF77 signal with and without noise, the results of the Goertzel algorithm's segments together with the threshold of the detector, the value of the EMA, and the reconstructed time-code signal.
+
+\subsection{Results}
+Multiple simulations with different values for the SNR starting from \SIrange{5}{-7}{\deci\bel} were executed to verify and evaluate the receiver's capabilities to reconstruct the DCF77's time code signal in different receiving conditions.
+From these simulations, the most relevant results occured in the case where the SNR was equal to \SI{-5}{\deci\bel}, because this was the lowest SNR where the reciver was still able to
+retrieve back the time code signal without errors.
+The frequency domain plots of the two FFTs, shown in Fig. \ref{fig:sim_fd_m5dB}, verify the DCF77 signal's aliases to show up exactly at \SI{\pm 5.5}{\kilo\hertz}.
+From the plot showing the DCF77 signal after passing the AWGN-channel, it can be seen that the noise floor is located at approximately \SI{-50}{\deci\bel} while the peaks
+of the DCF77 signaö have a value of approximately \SI{-8}{\deci\bel}.
+The difference of \SI{42}{\deci\bel} should not be confused with the SNR, as the power of the noise added by the AWGN-Channel is spread evenly over all frequencies.
+The correct SNR was verified to be exactly \SI{-5}{\deci\bel} by using MATLAB's built-in command "snr()" to calculate the SNR by comparing the before and after adding noise.
+\begin{figure}[!htbp]
+    \centerline{\includegraphics[width=0.4\textwidth]{img/sim_fd_m5dB.eps}}
+    \caption{Plots of the frequency domain at a SNR of \SI{-5}{\deci\bel}}
+    \label{fig:sim_fd_m5dB}
+\end{figure}
+\FloatBarrier
+The time domain plots of Fig. \ref{fig:sim_td_m5dB} show the creation of the DCF77 signal and the internal operation of the receiver.
+The first plot shows the time code signal that should be retrieved back by the receiver to allow a visual verification that the DCF77 signal is modulated retrieved back correctly.
+It can be seen that each symbol has a length of \SI{1}{\second} with a gap of either \SI{200}{\milli\second} or \SI{100}{\milli\second} at the beginning.
+From the second plot, the amplitude can be seen to switch between $0.15$ and $1$, representing the changes between \SI{15}{\percent} and \SI{100}{\percent}.
+The third plot shows the DCF77 signal with added noise and an average amplitude of approximately $3.5$ with the orignal waveform not being visible anymore.
+The fourth plot shows the results of the Goertzel algorithm segments together wit the value of the calculated threshold.
+The operation of the Goertzel algorithm can be verified, as the calculated magnitude of the frequency bin is clearly following the waveform of the time code signal.
+The value propagation of the threshold is as slow as expected with the value only experiencing minor drops during the gaps of the signal.
+A value where the detector starts to take valid decisions is reached after approximately \SI{5}{\second}.
+The threshold then approaches asymptotically the value where it is exactly located in the middle between the area of values representing an apmlitude of \SI{15}{\percent} and
+the area of values representing \SI{100}{\percent}.
+
+All simulation runs with a smaller SNR contained an increasing amount of errors, caused by the noise to raise exceed the
+
+\begin{figure*}[!htbp]
+    \centerline{\includegraphics[width=1.1\textwidth]{img/sim_td_m5dB.eps}}
+    \caption{Plots of the time domain at a SNR of \SI{-5}{\deci\bel}}
+    \label{fig:sim_td_m5dB}
+\end{figure*}
 

### 2024-08-25 matlab_scripts/main_script_bandpass_sampling_adaptive_threshold.m

@@ -6,7 +6,7 @@ clc;
 
 %Sampling parameters
 fs = 24e3; %Sampling frequency in Hz
-duration = 24; %Overall sampling duration in s (duration of the simulation)
+duration = 30; %Overall sampling duration in s (duration of the simulation)
 
 %AWGN-Channel parameters
 awgn_snr = -5; %SNR after the AWGN-channel in dB
@@ -57,6 +57,9 @@ dcf77_signal = (0.85*time_code_signal + 0.15) .* carrier_signal;
 %Add noise by passing the DCF77 signal through an AWGN-Channel
 dcf77_signal_noise = awgn(dcf77_signal, awgn_snr, 'measured');
 
+%Verifying SNR by measuring again
+snr_measured = snr(dcf77_signal, dcf77_signal_noise - dcf77_signal);
+
 
 
 %% Goertzel Algoritm Section
@@ -102,17 +105,20 @@ end
 
 %% Detection Section
 
-%Preparing vectors for the reconstructed signal and a rolling average 
+%Preparing vectors for the reconstructed signal and the Exponential Moving Average (EMA)
 exp_mov_avg = zeros(1, goertzel_num_segments);
 detector_threshold = zeros(1, goertzel_num_segments);
 dcf77_reconstructed = zeros(1, goertzel_num_segments);
 
+%Calculating the parameter alpha of the EMA
 exp_mov_avg_alpha = 2 / (det_avg_time * (1 / goertzel_segment_duration) + 1);
 
 for seg = 1:goertzel_num_segments
     %Calculating the Exponential Moving Average
-    if seg > 1
-        exp_mov_avg(seg) = (1 - exp_mov_avg_alpha) * exp_mov_avg(seg - 1) + exp_mov_avg_alpha * goertzel_segments_magnitudes(seg); %Calculate a weighted average otherwise
+    if seg == 1 %Check if it is the first segment
+        exp_mov_avg(seg) = exp_mov_avg_alpha * goertzel_segments_magnitudes(seg); %Adapt calulation as there is no element at index -1
+    else
+        exp_mov_avg(seg) = (1 - exp_mov_avg_alpha) * exp_mov_avg(seg - 1) + exp_mov_avg_alpha * goertzel_segments_magnitudes(seg); %Calculate EMA normally
     end
 
[…]

### 2024-08-25 paper/main.tex
Discussion of results finished.

@@
 From the second plot, the amplitude can be seen to switch between $0.15$ and $1$, representing the changes between \SI{15}{\percent} and \SI{100}{\percent}.
-The third plot shows the DCF77 signal with added noise and an average amplitude of approximately $3.5$ with the orignal waveform not being visible anymore.
+The third plot shows the DCF77 signal with added noise and an average amplitude of approximately $3.6$ with the orignal waveform not being visible anymore.
 The fourth plot shows the results of the Goertzel algorithm segments together wit the value of the calculated threshold.
@@
 the area of values representing \SI{100}{\percent}.
-
-All simulation runs with a smaller SNR contained an increasing amount of errors, caused by the noise to raise exceed the
+As the value of the EMA is proportional to the threshold, the plot is left out.
+In the fifth plot, the retrieved time code signal is visualized.
+It is obvious that the signal contains errors until the threshold has reached a level where valid decisions are taken by the detector.
+After \SI{5}{\second}, when the threshold reached this value, no more errors are visible.
+\par
+All simulation runs with a smaller SNR contained an increasing amount of errors, caused by the noise to raise or drop single points above or below the threshold, placing them in the
+area where they were detected to correspond to the opposite symbol.
+This effect can be imagined by thinking of the height of the area where the results are distributed by the noise is increased until both areas touch the threshold and start to overlap.
+Single points ending up in the other area are then interpreted as the wrong symbol.
 

### 2024-08-25 matlab_scripts/main_script_bandpass_sampling_adaptive_threshold.m

@@ -171,25 +171,25 @@ ylabel('20*log_{10}(|DCF77_{AWGN}(f)|)');
 %Time domain plots
 figure
 
-subplot(6,1,1);
+subplot(5,1,1);
 plot(t, time_code_signal);
 title('Time-Code Signal');
 xlabel('Time (s)');
 ylabel('Amplitude');
 
-subplot(6,1,2);
+subplot(5,1,2);
 plot(t, dcf77_signal);
 title('DCF77 Signal');
 xlabel('Time (s)');
 ylabel('Amplitude');
 
-subplot(6,1,3);
+subplot(5,1,3);
 plot(t, dcf77_signal_noise);
 title('DCF77 Signal with noise');
 xlabel('Time (s)');
 ylabel('Amplitude');
 
-subplot(6,1,4);
+subplot(5,1,4);
 stem(t_goertzel_segments_results, goertzel_segments_magnitudes);
 hold on;
 stairs(t_goertzel_segments_results, detector_threshold, 'Color', 'red');
@@ -198,13 +198,13 @@ xlabel('Time (s)');
 ylabel('Magnitude');
 hold off;
 
-subplot(6,1,5);
-stairs(t_goertzel_segments_results, exp_mov_avg);
-title('EMA of the detector');
-xlabel('Time (s)');
-ylabel('Value');
+% subplot(5,1,5);
+% stairs(t_goertzel_segments_results, exp_mov_avg);
+% title('EMA of the detector');
+% xlabel('Time (s)');
+% ylabel('Value');
 
-subplot(6,1,6);
+subplot(5,1,5);
 stairs(t_goertzel_segments_results, dcf77_reconstructed);
 title('Time-Code Signal after detector');
 xlabel('Time (s)');

### 2024-08-29 paper/main.tex
Demo implementation

@@
 It is obvious that the signal contains errors until the threshold has reached a level where valid decisions are taken by the detector.
-After \SI{5}{\second}, when the threshold reached this value, no more errors are visible.
+After \SI{5}{\second}, when the threshold reached this value, no more errors occured.
 \par
@@
 \end{figure*}
+
+\section{Demo implementation}
+The receiver's structure, shown in Fig. \ref{fig:block_diag_receiver}, was implemented on a STM32F103C8T6, an Arm Cortex-M3 microcontroller, to provide a brief proof of concept.
+To for an optical verification, the obtained time code signal is used to turn on and off a Light-Emitting Diode (LED), but this signal
+could also be used to decode the DCF77's transmitted time data.
+As a tuned antenna together with a pre-amplifier is needed to filter out the DCF77 signal and amplify it to a level where it can be measured by the microcontroller's internal ADC, a minimalistic circuit
+consisting of a tank circuit tuned to \SI{77.5}{\kilo\hertz} and a two-stage transistor amplifier was built based on the circuit shown in \cite{b12}.
+The rest of the of the receiver's structure was implemented in software using C and single-precision floating-point for the caluclations.
+\par
+A timer was set up to create an internal Pulse Width Modulation (PWM) signal to trigger the conversion of the microcontroller's internal ADC at the sampling frequency of \SI{24}{\kilo\hertz}.
+The samples are transferred using circular Direct Memory Access (DMA) into a buffer of the size of $480$.
+This size was chosen because it is equal to twice the amount of samples that are needed for the analyzation of one segment.
+During runtime, the DMA hardware module fills this buffer and two interrupts are executed when the buffer was filled half way and when it is completely full.
+Because of the circular setup of the DMA, it fills the buffer continuously and wraps around back to the first address, after reaching the buffer's end.
+This allows a continuous operation of the application with a precise sampling frequency while eliminating the need to handle ADC conversions manually. 
+As a segment is ready to be analyzed with every interrupt, the operations needed to process the signal processing are executed inside this Interrupt Service Routine (ISR).
+The result of each segment after the detector is then used to turn on or off a General Purpose Input Output (GPIO) that is connected to a LED.
+\par
+Although its rather simplistic implementation, the demo implementation worked right away.
+The observed effect of the receiver to adapt to the current receiving conditions by first outputting wrong results because of a
+not matching threshold is also noticeable when running the demo application.
+After powerup and changes in the environment and therefore during the adaption of the threshold to its new value, the LED shows
+arrythmic behavior.
+This
+
+The demo implementation worked right away, showing a good sensitivity
 
@@
 \bibitem{b11} R. G. Lyons, ``Setting the 3-dB Cutoff Frequency of an Exponential Averager,'' 2012, Internet Article. [Online]. Available: \url{https://www.dsprelated.com/showarticle/182.php}
+\bibitem{b12} -, ``ATTINY85 als DCF77-Empfänger,'' 2021, Board Entry. [Online]. Available: \url{https://www.mikrocontroller.net/topic/529477}
 \end{thebibliography}

### 2024-08-29 paper/main.tex
Started with summary

@@
 Although its rather simplistic implementation, the demo implementation worked right away.
-The observed effect of the receiver to adapt to the current receiving conditions by first outputting wrong results because of a
-not matching threshold is also noticeable when running the demo application.
-After powerup and changes in the environment and therefore during the adaption of the threshold to its new value, the LED shows
-arrythmic behavior.
-This
+The behavior of the receiver that was observed in the simulation, first outputting a series of wrong results when adapting to the
+current receiving conditions, is also noticable when running the demo application.
+After powerup or changes in the environment and therefore during the stabilization of the threshold to its new value, the LED shows
+arrythmic behavior for approximately \SI{5}{\second} before the application continues to operate correctly.
+Other than that, the demo implementation shows that the presented principle also works in reality and that it can be implemented
+with low effort.
+Based on this structure, the code can be expanded to a full clock by decoding the information from the retrieved time code signal.
+The code is available in the paper's GitHub repository \cite{b13}.
 
-The demo implementation worked right away, showing a good sensitivity
+\section{Summary}
+After the theoretical discussion, the simulation and the proof of concept  presented principle
 
@@
 \bibitem{b12} -, ``ATTINY85 als DCF77-Empfänger,'' 2021, Board Entry. [Online]. Available: \url{https://www.mikrocontroller.net/topic/529477}
+\bibitem{b13} L. Hackmann, ``SiCo1\_Project,'' 2024, GitHub Repository. [Online]. Available: \url{https://github.com/lhckmn/SiCo1_Project}
 \end{thebibliography}

### 2024-08-29 paper/main.tex
First version ready for correction

@@
 \begin{document}
-\title{Decoding the Amplitude-Modulated Part the DCF77 Longwave Time Signal by using the Goertzel Algorithm}
+\title{Decoding the Amplitude-Modulated Part of the DCF77 Longwave Time Signal by using the Goertzel Algorithm}
 
@@
     radio-controlled clocks in Europe. Its signal consists of a phase and an amplitude-modulated part, both containing the time information.
-    Devices that use the signal usually consist of an amplitude modulation long wave receiver, often realized by using a dedicated integrated circuit, and an
+    Devices that use the signal usually consist of an amplitude modulation long wave receiver, often realized by using a dedicated integrated circuit and an
     application processor. In this paper, an alternative approach for the demodulation of the amplitude-modulated part of the signal, without the need for specialized
-    analog cicruitry and only a minimal amount of simple hardware components, is presented.
+    analog cicruitry and with only a minimal amount of simple hardware components, is presented.
     This is done by utilizing direct-sampling software-defined radio techniques together with leveraging the efficiency of the Goertzel algorithm.
@@
 Radio controlled clocks are very popular because they dont require periodical re-adjustment in comparison to common mechanical or quartz-powered clocks.
-Instead, the information about the current time is obtained from a RF-signal that is transmitted by an official authority that ensures its availability and
-correctness.
+Instead, the information about the current time is obtained from a RF-signal, transmitted by an official authority that ensures its availability and correctness.
 The probably most important time signal in Europe is transmitted by the station DCF77 from Mainflingen, a city in Germany that is close to Frankfurt am Main.
 The station is operated by a private company that is commissioned by the Physikalisch-Technische Bundesanstalt (PTB) which also supplies the current time information,
-generated by two caesium clocks and two caesium fountains. Its operating frequency lies in the long wave area at \SI{77.5}{\kilo\hertz} and the time signal
-uses simple modulation techniques (amplitude and phase-modulation) and transmits with \SI{100}{\kilo\watt} Effective Isotropic Radiated Power (EIRP) to enable the reception of the
+generated by two caesium clocks and two caesium fountains.
+The time signal's operating frequency lies in the long wave area at \SI{77.5}{\kilo\hertz}, simple modulation techniques (amplitude and phase-modulation) are used and it is transmitted with \SI{100}{\kilo\watt} Effective Isotropic Radiated Power (EIRP) to enable the reception of the
 signal in relatively close distances (up to \SI{2000}{\kilo\meter}) with simple technical equipment \cite{b2}.
@@
 \FloatBarrier
-End-user devices usually make use of the amplitude-modulated part of the signal by using an amplitude modulation receiver, often a by employing specialized integrated circuit,
-together with a rather big ferrite-rod antenna to obtain the time signal.
-This time signal then needs further hardware, often in form of a microcontroller used as the applicaton processor, to decode and retrieve the actual time information.
+End-user devices usually make use of the amplitude-modulated part of the signal by using an amplitude modulation receiver, often a by employing specialized integrated circuits,
+together with a rather big ferrite-rod antenna to obtain the time code signal.
+This time code signal then needs further hardware, often in form of a microcontroller used as the applicaton processor, to decode and retrieve the actual time information.
 With the increasing availability of computation power and Digital Signal Processing (DSP) capabilities inside cheap mixed-signal microcontrollers, which are already used
@@
 external analog circuitry. In fact, only a tuned antenna with a basic pre-amplifier is needed.
-
+\par
 In this paper, a straightfoward principle for designing a lightweight receiver for the DCF77, based on SDR-techniques, is presented.
@@
 amplitude-modulated part it is still well below \SI{1}{\second}, being \SI{100}{\milli\second} \cite{b2}.
-When using the phase-modulated part, a standard deviation of \SIrange{\pm 2}{\pm 22}{\micro\second} from the atomic clock to the receving device can be observed \cite{b4}.
+When using the phase-modulated part, a standard deviation of \SIrange{\pm 2}{\pm 22}{\micro\second} from the time of the atomic clock to the time of the receving device can be observed \cite{b4}.
 \par
@@
 
-\section{Summary}
-After the theoretical discussion, the simulation and the proof of concept  presented principle
+\section{Conclusion}
+After the theoretical discussion, the simulation, and the proof of concept by showing a demo implementation, it can be seen that the presented principle can be used to realize a receiver for the DCF77 time signal with minimal effort regarding hardware and signal processing.
+This is achieved by moving most of the signal processing into the digital domain of the application processor to leverage the effects of bandpass sampling, the efficiency of the Goertzel algorithm, and the simplicity of a detector based on an EMA.
+In addition, the proposed architecture also shrinks down the need for external specialized analog circuitry, leaving only a tuned antenna and a pre-amplifier.
+While the the complexity that is typically associated with analog receivers is reduced, the principle also increased adaptability to changing receiving conditions.
+As all algorithms were designed to require a minimum of resources, the principle can be applied to enable systems with restricted resources to make use of the DCF77 time signal.
 
 \section*{Acknowledgment}
-The preferred spelling of the word ``acknowledgment'' in America is without 
-an ``e'' after the ``g''. Avoid the stilted expression ``one of us (R. B. 
-G.) thanks $\ldots$''. Instead, try ``R. B. G. thanks$\ldots$''. Put sponsor 
-acknowledgments in the unnumbered footnote on the first page.
+This work was inspired by a project that was published by an anonymous author in a german forum about electronics (see \cite{b12}).
+The autor of this paper, L. Hackmann, wants to thank for the knowledge and ideas that were provided through freely accessible entries.
 
@@
 \bibitem{b11} R. G. Lyons, ``Setting the 3-dB Cutoff Frequency of an Exponential Averager,'' 2012, Internet Article. [Online]. Available: \url{https://www.dsprelated.com/showarticle/182.php}
-\bibitem{b12} -, ``ATTINY85 als DCF77-Empfänger,'' 2021, Board Entry. [Online]. Available: \url{https://www.mikrocontroller.net/topic/529477}
+\bibitem{b12} -, ``ATTINY85 als DCF77-Empfänger,'' 2021, Forum Entry. [Online]. Available: \url{https://www.mikrocontroller.net/topic/529477}
 \bibitem{b13} L. Hackmann, ``SiCo1\_Project,'' 2024, GitHub Repository. [Online]. Available: \url{https://github.com/lhckmn/SiCo1_Project}

### 2024-08-30 paper/main.tex
First round of fixing typos completed

@@
 \IEEEoverridecommandlockouts
-% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
 %Template version as of 6/27/2024
@@
 \begin{document}
-\title{Decoding the Amplitude-Modulated Part of the DCF77 Longwave Time Signal by using the Goertzel Algorithm}
+\title{A Software Defined Radio Based on the Goertzel Algorithm for the DCF77 Longwave Time Signal}
 
 \author{\IEEEauthorblockN{1\textsuperscript{st} Leander Hackmann}
-\IEEEauthorblockA{\textit{Master Embedded Systems Engineering} \\
+\IEEEauthorblockA{
+\textit{Master Embedded Systems Engineering}\\
 \textit{FH Dortmund}\\
-Dortmund, Germany \\
-Mat.-Nr.: 7217912, leander.hackmann001@stud.fh-dortmund.de}
+Dortmund, Germany\\
+Mat.-Nr.: 7217912, leander.hackmann001@stud.fh-dortmund.de\\}
 }
@@
 \section{Introduction}
-Radio controlled clocks are very popular because they dont require periodical re-adjustment in comparison to common mechanical or quartz-powered clocks.
+Radio controlled clocks are very popular because they do not require periodical re-adjustment in comparison to common mechanical or quartz-powered clocks.
 Instead, the information about the current time is obtained from a RF-signal, transmitted by an official authority that ensures its availability and correctness.
 The probably most important time signal in Europe is transmitted by the station DCF77 from Mainflingen, a city in Germany that is close to Frankfurt am Main.
-The station is operated by a private company that is commissioned by the Physikalisch-Technische Bundesanstalt (PTB) which also supplies the current time information,
+The station is operated by a private company that is commissioned by the Physikalisch-Technische Bundesanstalt (PTB), which also supplies the current time information,
 generated by two caesium clocks and two caesium fountains.
@@
 With the increasing availability of computation power and Digital Signal Processing (DSP) capabilities inside cheap mixed-signal microcontrollers, which are already used
-to process the time information, the idea to replace to replace the analog receiver portion with a Software Defined Radio (SDR) is more or less obvious.
+to process the time information, the idea to replace the analog receiver portion with a Software Defined Radio (SDR) is more or less obvious.
 Moving the receiver into the application processor would allow for a simpler hardware design by shrinking down the complexity and the parts count of the
@@
 \section{Principle of the receiver}
-As the seen in the description of the DCF77 signal, retrieving back the binary time signal from the amplitude-modulated part is more or less trivial.
+As seen in the description of the DCF77 signal, retrieving back the binary time signal from the amplitude-modulated part is more or less trivial.
 Conventional applications execute this task by using analog receiving circuits, usually by using a simple amplitude modulation receiver together with a
 tuned ferrite-rod antenna, acting as a Bandpass Filter (BPF), to filter out the irrelevant part of the spectrum. 
-Moving the receiver into the digital domain allows for more advanced techniques to retrieve this binary time signal, rather than demodulating the signal with a
+Moving the receiver into the digital domain allows more advanced techniques to retrieve this binary time signal, rather than demodulating the signal with a
 diode detector inside the amplitude modulation receiver.
@@
 It is therefore used to observe the DCF77 signal's amplitude over time by being executed periodically.
-As the gap of the encoded symbols is eiter \SI{100}{\milli\second} or \SI{200}{\milli\second} long, the duration of the analyzation set to \SI{10}{\milli\second} to provide a good tradeoff between resolution in time and a longest possible analyzation time
+As the gap of the encoded symbols is eiter \SI{100}{\milli\second} or \SI{200}{\milli\second} long, the duration of the analyzation is set to \SI{10}{\milli\second} to provide a good tradeoff between resolution in time and a longest possible analyzation time
 to leverage the DFT gain.
@@
 From the plot showing the DCF77 signal after passing the AWGN-channel, it can be seen that the noise floor is located at approximately \SI{-50}{\deci\bel} while the peaks
-of the DCF77 signaö have a value of approximately \SI{-8}{\deci\bel}.
+of the DCF77 signal have a value of approximately \SI{-8}{\deci\bel}.
 The difference of \SI{42}{\deci\bel} should not be confused with the SNR, as the power of the noise added by the AWGN-Channel is spread evenly over all frequencies.
@@
     \centerline{\includegraphics[width=0.4\textwidth]{img/sim_fd_m5dB.eps}}
-    \caption{Plots of the frequency domain at a SNR of \SI{-5}{\deci\bel}}
+    \caption{Frequency domain plots of the simulation run with a SNR of \SI{-5}{\deci\bel}}
     \label{fig:sim_fd_m5dB}
@@
 The first plot shows the time code signal that should be retrieved back by the receiver to allow a visual verification that the DCF77 signal is modulated retrieved back correctly.
-It can be seen that each symbol has a length of \SI{1}{\second} with a gap of either \SI{200}{\milli\second} or \SI{100}{\milli\second} at the beginning.
-From the second plot, the amplitude can be seen to switch between $0.15$ and $1$, representing the changes between \SI{15}{\percent} and \SI{100}{\percent}.
+It is visible that each symbol has the expected length of \SI{1}{\second} with a gap of either \SI{200}{\milli\second} or \SI{100}{\milli\second} at the beginning.
+From the second plot, the amplitude can be seen switching between $0.15$ and $1$, representing the changes between \SI{15}{\percent} and \SI{100}{\percent}.
 The third plot shows the DCF77 signal with added noise and an average amplitude of approximately $3.6$ with the orignal waveform not being visible anymore.
@@
     \centerline{\includegraphics[width=1.1\textwidth]{img/sim_td_m5dB.eps}}
-    \caption{Plots of the time domain at a SNR of \SI{-5}{\deci\bel}}
+    \caption{Time domain plots of the simulation run with a SNR of \SI{-5}{\deci\bel}}
     \label{fig:sim_td_m5dB}
@@
 The receiver's structure, shown in Fig. \ref{fig:block_diag_receiver}, was implemented on a STM32F103C8T6, an Arm Cortex-M3 microcontroller, to provide a brief proof of concept.
-To for an optical verification, the obtained time code signal is used to turn on and off a Light-Emitting Diode (LED), but this signal
+For an optical verification, the obtained time code signal is used to turn on and off a Light-Emitting Diode (LED), but this signal
 could also be used to decode the DCF77's transmitted time data.

### 2024-08-30 paper/main.tex
Final version

@@
 In 1973, the transmission of the current time information was added to the signal by using amplitude modulation.
-To allow a reception under more challenging conditions and with a higher resolution and accuracy, the same time information is also added to the signal since 1983 by using
-phase-modulation \cite{b3}.
-The two different parts of the signal that result out of the parallel amplitude and the phase-modulation can be used for different use-cases that are separated by the
+To allow a reception under more challenging conditions and with a higher resolution and accuracy, the same time information is also transmitted by using phase modulation since 1983 \cite{b3}.
+The two different parts of the signal that result out of the parallel amplitude and phase modulation can be used for different use-cases that are separated by the
 requirements regarding the resolution, accuracy, and the reliability of the obtained time information. 
-Whereas the amplitude-modulated part is mainly used for general-purpose time application with low resolution requirements, the phase-modulated part is usually used
+Whereas the amplitude-modulated part is mainly used for general-purpose time applications with low resolution requirements, the phase-modulated part is usually used
 for specialized applications that require a higher resolution, accuracy, and reliability.
 Although being considered as low in comparison to what is achievable by analyzing the phase-modulated part, the usually observed accuracy uncertainity when using the
-amplitude-modulated part it is still well below \SI{1}{\second}, being \SI{100}{\milli\second} \cite{b2}.
+amplitude-modulated part it is still well below \SI{1}{\second}, being equal to \SI{100}{\milli\second} \cite{b2}.
 When using the phase-modulated part, a standard deviation of \SIrange{\pm 2}{\pm 22}{\micro\second} from the time of the atomic clock to the time of the receving device can be observed \cite{b4}.
@@
 switch to or from Daylight Saving Time (DST), to show if DST is currently enabled or not, and to announce an upcoming leap second \cite{b5}.
-As the decryption of the weather date requires a specialized third-party integrated circuit and the notification bit is only important for the PTB, these parts
+As the decryption of the weather data requires a specialized third-party integrated circuit and the notification bit is only important for the PTB, these parts
 of the frame are discarded by most applications.
-The leftover Bits \SIrange{20}{58}{} are used to represent the current time and date in Binary Coded Decimal (BCD) format, including parity bits for recognizing errors.
+The leftover bits \SIrange{20}{58}{} are used to represent the current time and date in Binary Coded Decimal (BCD) format, including parity bits for recognizing errors.
 \begin{figure}[htbp]
@@
 \FloatBarrier\noindent
-This means that a receiver needs to run at least for \SI{39}{\second} after powerup to receive one whole block containing the current time information.
+Caused by this scheme, a receiver needs to run at least for \SI{39}{\second} after powerup to receive one whole block containing the current time information.
 In reality, this period is usually longer because the receiver needs to adapt to the current receiving conditions. 
@@
 tuned ferrite-rod antenna, acting as a Bandpass Filter (BPF), to filter out the irrelevant part of the spectrum. 
-Moving the receiver into the digital domain allows more advanced techniques to retrieve this binary time signal, rather than demodulating the signal with a
+Moving the receiver into the digital domain allows more advanced techniques to retrieve this binary time signal, rather than demodulating the RF-signal with a
 diode detector inside the amplitude modulation receiver.
@@
 continuous analysis of the spectrum at the carrier's frequency of \SI{77.5}{\kilo\hertz}.
-This task will be carried out by using the Goertzel algorithm, which is presented later.
+In the presented principle, this task will be carried out by using the Goertzel algorithm, which is introduced later.
 The structure of the whole receiver then simplifies to only two external hardware parts
@@
 The tuned ferrite-rod antenna is kept to filter out the irrelevant spectral components, leaving only the DCF77's component at \SI{77.5}{\kilo\hertz}.
-This signal is then amplified by a RF amplifier and sampled at a certain sampling rate $f_{s}$ using the Analog to Digital Converter (ADC) of the application processsor.
+This signal is then amplified by an amplifier and sampled at a certain sampling rate $f_{s}$ using the Analog to Digital Converter (ADC) of the application processsor.
 A timer producing a frequency equal to $f_{s}$ is used to trigger the sampling.
 The samples are passed to the Goertzel algorithm to analyze the amplitude of the DCF77 signal.
-The result of the analyzation is then passed to a detector to reconstruct the binary time signal.
+The result of the analyzation is then passed to a detector to reconstruct the time code signal.
 \par
@@
 \end{equation}
-Only when this condition is satisfied, the original signal can be reconstructed from the samples and it must be ensured that the signal contains no spectral elements
+Only when this condition is satisfied, the original signal can be reconstructed from the samples, so it must be ensured that the signal contains no spectral elements
 that might violate the condition \cite{b6}.
@@
 Its center frequency $f_{c}$ lies at \SI{77.5}{\kilo\hertz} with a theoretical maximum bandwidth $B$ of \SI{2.4}{\kilo\hertz} \cite{b2}.
-The effective bandwidth is much smaller in reality but \SI{2.4}{\kilo\hertz} will be used for finding a proper sampling frequency to provide enough safety margin.
-With \eqref{eqn:fs}, a table containing possible ranges for $f_{s}$ can be created.
+The effective bandwidth is much smaller in reality but \SI{2.4}{\kilo\hertz} will be used for finding a proper sampling frequency while providing enough safety margin.
+With \eqref{eqn:fs}, a table containing possible ranges for $f_{s}$ was be created:
 \begin{table}[htbp]
@@
 This then leads to higher requirements regarding the adherence to the exact sampling rate.
-A choice providing a good tradeoff between these effects $f_{s} = \SI{24}{\kilo\hertz}$ at $m = 7$, because it offers a distance of $\SI{2647}{\hertz}$ between the upper and lower limits with the sampling frequency lying almost in the middle \cite{b10}.
+A choice providing a good tradeoff between these effects is $f_{s} = \SI{24}{\kilo\hertz}$ at $m = 7$, because it offers a distance of $\SI{2647}{\hertz}$ between the upper and lower limits with the sampling frequency lying almost in the middle \cite{b10}.
 The DCF77 signal is then, as visible in Fig. \ref{fig:dcf77_bp_spectrum}, downconverted and centered at
@@
     }
-    \caption{Spectrum after bandpass sampling the DCF77 signal at $f_{s} = \SI{24}{\kilo\hertz}$. The original spectral parts are filled with blue dots.}
+    \caption{Spectrum after bandpass sampling the DCF77 signal at $f_{s} = \SI{24}{\kilo\hertz}$. The original spectral parts are filled with blue dots}
     \label{fig:dcf77_bp_spectrum}
@@
 ("frequency bins") within a range from \SI{0}{\hertz} to $\frac{f_{s}}{2}$ where $N$ is the number of samples and $f_{s}$ is the sampling frequency \cite{b6}.
-The signal strength, and therefore the binary time signal of the amplitude-modulated part, can then be examined by observing the magnitude of the curresponding frequency bin
+The signal strength, and therefore the time code signal of the amplitude-modulated part, can then be examined by observing the magnitude of the corresponding frequency bin
 over time. Because of only one frequency bin being relevant, it is obvious that a full FFT produces a lot of overhead and redundant calculation operations in this use-case. 
@@
 The constant $2 \cdot cos(\omega_{g})$, often called the "Goertzel coefficient", is calculated before the execution and used to adapt the algorithm to the frequency to be analyzed.
-The Value of $\omega_{g}$ itself is calculated based on a integer number $k$ and $N$.
+The value of $\omega_{g}$ itself is calculated based on an integer number $k$ and the number of samples $N$.
 The integer number $k$ is a rounded fraction based on $N$, the frequency to be analyzed $f_{a}$, and the the sampling frequency $f_{s}$:
@@
 Just as with the conventional FFT, the amount of needed calculations for executing the Goertzel algorithm is based on the number of samples.
-In total, $N + 1$ multiplications and $2 \cdot N + 2$ additions are needed, which can be seen from the formulas for the IIR-part and the final calculation of the squared magnitude.
+In total, $N + 1$ multiplications and $2 \cdot N + 2$ additions are needed, which can be seen from the formulas of the IIR-part and the final calculation of the squared magnitude.
 For example, a length of processing $N = 512$ samples requires in $513$ multiplications and $1026$ additions to calculate the squared magnitude of the desired frequency.
@@
 \par
-With this simple example, it is already visible that the Goertzel algorithm can reduce the amount of needed resources compared to a full FFT, when only one or a small amount of frequency bins should be analyzed.
+With this simple example, it is already visible that the Goertzel algorithm can reduce the amount of needed resources compared to a full FFT, when only one or a small number of frequency bins should be analyzed.
 It is therefore used to observe the DCF77 signal's amplitude over time by being executed periodically.
@@
 As the values of the Goertzel algorithm will follow the pattern of the signal's amplitude being switched between \SI{15}{\percent} and \SI{100}{\percent}, the detection can be done by comparing the value of the current sample to a threshold.
-To compensate the changing of magnitude of the Goertzel algorithm's values that is caused by the current receiving situation, an Exponential Moving Average (EMA) is calculated by using \eqref{eqn:ema} and employed to create an adaptive threshold \cite{b11}.
+To compensate the changing of magnitude of the Goertzel algorithm's values that is caused by the current receiving situation, an Exponential Moving Average (EMA) is calculated by using \eqref{eqn:ema} and employed to create an adaptive threshold \cite{b11}:
 \begin{equation}
@@
 \end{equation}
-The scaling factor is needed as the average percentage of time where the signal where is equal to \SI{100}{percent} is \SI{87.25}{\percent} (assuming an equal distribution between symbols representing a binary 1 and a 0).
+The scaling factor is needed as the average percentage of time where the signal's amplitude is equal to \SI{100}{\percent} is \SI{87.25}{\percent} (assuming an equal distribution between symbols representing a binary 0 and a 1).
 If the value of the current sample is above this threshold, it is treated as a 1.
 Otherwise it is treated as a 0.
-The series of ones and zeros is then following the waveform shown in Fig. \ref{fig:dcf77_symbol_encoding} and can be used to decode the current time.
+The series of ones and zeros produced by the detector is then following the waveform shown in Fig. \ref{fig:dcf77_symbol_encoding} and can be used to decode the current time.
 
@@
 To verify and further explain the working principle of the receiver, a simulation of the whole system was created using MATLAB.
-The whole simulation was divided into five sections to allow for a clear structure:
+The simulation was divided into five sections to allow for a clear structure:
 \begin{enumerate}
@@
 \subsection{Simulation Parameter Section}
-In the Simulation Parameter Section, static parameters for the following sections of the simulation are defined.
-These include the sampling frequency $f_{s}$, the duration of the whole simulation, the SNR that the signal should have after passing the Additive White Gaussian Noise (AWGN)-Channel, the frequency to be analyzed by the Goertzel algoritm, the duration of the Goertzel algorithm segments, and the time that should be taken into account by the EMA.
-By adjusting these parameters, the receiving situation and the receiver's behavior can be altered to, e.g. to simulate different receiving conditions and examine the system's performance.
+In the Simulation Parameter Section, static parameters for the other sections of the simulation are defined.
+These include the sampling frequency $f_{s}$, the duration of the whole simulation, the SNR that the signal should have after passing an Additive White Gaussian Noise (AWGN)-Channel, the frequency to be analyzed by the Goertzel algoritm, the duration of the Goertzel algorithm segments, and the time that should be taken into account by the EMA.
+By adjusting these parameters, the receiving situation and the receiver's behavior can be altered to simulate different receiving conditions and examine the system's performance.
 
@@
 The Signal Creation Section implements the creation of the amplitude-modulated DCF77 signal.
-First, a time vector with the length of the simulation's duration and a step size that depends on $f_{s}$ is created and its length stored in a variable.
-A vector containing the carrier signal at $f_{c} = \SI{77.5}{\kilo\hertz}$ by using this time vector is created afterwards.
-For the amplitude modulation of the carrier, the time code signal containing the binary encoded symbols needs to be created.
+First, a time vector with the length of the simulation's duration and a step size that depends on $f_{s}$ is created and its length is stored in a variable.
+A vector containing the carrier signal at $f_{c} = \SI{77.5}{\kilo\hertz}$ is created afterwards by using this time vector.
+For the amplitude modulation of the carrier, the time code signal containing the binary encoded symbols also needs to be created.
 As this signal is used for multiplication with the carrier, it needs to consist of rects with a period length of \SI{1}{\second} and a gap of either \SI{200}{\milli\second} or \SI{100}{\milli\second} at the beginning.
-These rects are prepared by creating and filling two vectors with the matching amount of zeros followed and filling the rest with ones.
+These rects are prepared by creating and filling two vectors with the matching amount of zeros and the rest of the vector's length with ones.
 A vector containing the time code signal with alternating symbols is created by concatenating these vectors inside a for loop.
-The number of iterations is given by rounding up the simulation's duration, because each symbol has the duration of \SI{1}{\second}.
+The number of iterations is given by rounding up the simulation's duration.
+This is needed because each symbol has the duration of \SI{1}{\second}.
 The vector is then cut down afterwards to exactly match the length of the time vector and therefore the duration of the simulation.
 To finally create the DCF77 signal, the vector with the time code signal is scaled and multiplied element-wise with the vector containing the carrier signal.
-This signal is then passed through a AWGN-Channel, creating a signal with a defined SNR to allow the simulation of different receiving conditions.
+This signal is then passed through an AWGN-Channel, creating a signal with a defined SNR to allow the simulation of different receiving conditions.
 
@@
 The segment-wise analyzation is then implemented by using an outer and an inner for-loop.
-The outer for-loop iterates over the number of segments, first resetting Q\_0, Q\_1, and Q\_2 followed by calculating the index of the first and the last sample of the current segment to provide the limits for the inner for-loop.
-Inside the inner for-loop, the formula \eqref{eqn:goertzel} of the IIR-Part is implemented by calculating the new output of the structure and shifting the previous results in each iteration.
-After all samples of the segment were processed (the inner for-loop finished), the magnitude is calculated by the implementation of \eqref{eqn:goertzel-mag}, using the values stored in Q\_1 and Q\_2 and taking the square root of the result.
+The outer for-loop iterates over the number of segments, first resetting Q\_0, Q\_1, and Q\_2 followed by calculating the index of the first and the last sample of the current segment to provide the inner for-loop's limits.
+Inside the inner for-loop, the formula \eqref{eqn:goertzel} of the IIR-Part is implemented by calculating the new output of the structure and shifting the previous results in each iteration through Q\_1 and Q\_2.
+After all samples of the segment were processed (the inner for-loop finished), the magnitude is calculated by the implementation of \eqref{eqn:goertzel-mag}, using the values stored in Q\_1 and Q\_2 and by taking the square root of the result.
 The result is then stored inside the prepared vector for the segments' results.
@@
 Then, the threshold is calculated based on the value of the EMA and the scaling factor (see \eqref{eqn:thresh}) and stored inside a vector.
-The decision whether the result of the current section was caused by the signal's amplitude being equal to either \SI{15}{\percent} or
+The decision whether the result of the current segment was caused by the signal's amplitude being equal to either \SI{15}{\percent} or
 \SI{100}{\percent} is done by comparing the value of the result to the calculated threshold.
@@
 Besides the calculation of the FFTs themselves, a vector containing the bins' frequencies is prepared for plotting.
-The results of the two FFTs are then plotted in figure.
+The results of the two FFTs are then plotted in a figure.
 \par
 In a second figure, multiple time domain plots are arranged to allow the observation of the receiver's stages.
-These include plots of the time code signal, the DCF77 signal with and without noise, the results of the Goertzel algorithm's segments together with the threshold of the detector, the value of the EMA, and the reconstructed time-code signal.
+These include plots of the time code signal, the DCF77 signal with and without noise, the results of the Goertzel algorithm's segments together with the threshold of the detector, and the reconstructed time-code signal.
 
@@
 Multiple simulations with different values for the SNR starting from \SIrange{5}{-7}{\deci\bel} were executed to verify and evaluate the receiver's capabilities to reconstruct the DCF77's time code signal in different receiving conditions.
-From these simulations, the most relevant results occured in the case where the SNR was equal to \SI{-5}{\deci\bel}, because this was the lowest SNR where the reciver was still able to
+From these simulations, the most relevant results occured in the case where the SNR was equal to \SI{-5}{\deci\bel}, because this was identified to be the lowest SNR where the receiver was still able to
 retrieve back the time code signal without errors.
@@
 The difference of \SI{42}{\deci\bel} should not be confused with the SNR, as the power of the noise added by the AWGN-Channel is spread evenly over all frequencies.
-The correct SNR was verified to be exactly \SI{-5}{\deci\bel} by using MATLAB's built-in command "snr()" to calculate the SNR by comparing the before and after adding noise.
+The SNR was verified to be exactly \SI{-5}{\deci\bel} by using MATLAB's built-in command "snr()" to calculate the SNR by comparing the signal before and after adding noise.
 \begin{figure}[!htbp]
@@
 The time domain plots of Fig. \ref{fig:sim_td_m5dB} show the creation of the DCF77 signal and the internal operation of the receiver.
-The first plot shows the time code signal that should be retrieved back by the receiver to allow a visual verification that the DCF77 signal is modulated retrieved back correctly.
+The first plot shows the time code signal to allow a visual verification that the DCF77 signal is modulated and retrieved back correctly.
 It is visible that each symbol has the expected length of \SI{1}{\second} with a gap of either \SI{200}{\milli\second} or \SI{100}{\milli\second} at the beginning.
 From the second plot, the amplitude can be seen switching between $0.15$ and $1$, representing the changes between \SI{15}{\percent} and \SI{100}{\percent}.
-The third plot shows the DCF77 signal with added noise and an average amplitude of approximately $3.6$ with the orignal waveform not being visible anymore.
-The fourth plot shows the results of the Goertzel algorithm segments together wit the value of the calculated threshold.
+The third plot shows the DCF77 signal with added noise and an average amplitude of approximately $3.6$ while the orignal waveform is not being visible anymore.
+The fourth plot shows the results of the Goertzel algorithm's segments together with the value of the calculated threshold.
 The operation of the Goertzel algorithm can be verified, as the calculated magnitude of the frequency bin is clearly following the waveform of the time code signal.
@@
 A value where the detector starts to take valid decisions is reached after approximately \SI{5}{\second}.
-The threshold then approaches asymptotically the value where it is exactly located in the middle between the area of values representing an apmlitude of \SI{15}{\percent} and
+The threshold then asymptotically approaches the value where it is exactly located in the middle between the area of values representing an amplitude of \SI{15}{\percent} and
 the area of values representing \SI{100}{\percent}.
@@
 All simulation runs with a smaller SNR contained an increasing amount of errors, caused by the noise to raise or drop single points above or below the threshold, placing them in the
-area where they were detected to correspond to the opposite symbol.
-This effect can be imagined by thinking of the height of the area where the results are distributed by the noise is increased until both areas touch the threshold and start to overlap.
-Single points ending up in the other area are then interpreted as the wrong symbol.
+area where they were assumed by the detector to correspond to the opposite symbol.
+This effect can be imagined by thinking of the height of the area where the results are distributed by the noise to be increased until both areas touch the threshold and begin to overlap.
+Single points can then end up in the other area and are interpreted as the wrong symbol.
 
@@
 \section{Demo implementation}
-The receiver's structure, shown in Fig. \ref{fig:block_diag_receiver}, was implemented on a STM32F103C8T6, an Arm Cortex-M3 microcontroller, to provide a brief proof of concept.
+The receiver's structure of Fig. \ref{fig:block_diag_receiver} was implemented on a STM32F103C8T6, an Arm Cortex-M3 microcontroller, to provide a brief proof of concept.
 For an optical verification, the obtained time code signal is used to turn on and off a Light-Emitting Diode (LED), but this signal
-could also be used to decode the DCF77's transmitted time data.
+could also already be used to decode the DCF77's transmitted time data.
 As a tuned antenna together with a pre-amplifier is needed to filter out the DCF77 signal and amplify it to a level where it can be measured by the microcontroller's internal ADC, a minimalistic circuit
 consisting of a tank circuit tuned to \SI{77.5}{\kilo\hertz} and a two-stage transistor amplifier was built based on the circuit shown in \cite{b12}.
-The rest of the of the receiver's structure was implemented in software using C and single-precision floating-point for the caluclations.
+The rest of the of the receiver's structure was implemented in software using C and single-precision floating-point arithmetics for the caluclations.
 \par
 A timer was set up to create an internal Pulse Width Modulation (PWM) signal to trigger the conversion of the microcontroller's internal ADC at the sampling frequency of \SI{24}{\kilo\hertz}.
-The samples are transferred using circular Direct Memory Access (DMA) into a buffer of the size of $480$.
+The samples are transferred into a buffer of the size of $480$ using Direct Memory Access (DMA) in circular mode.
 This size was chosen because it is equal to twice the amount of samples that are needed for the analyzation of one segment.
-During runtime, the DMA hardware module fills this buffer and two interrupts are executed when the buffer was filled half way and when it is completely full.
-Because of the circular setup of the DMA, it fills the buffer continuously and wraps around back to the first address, after reaching the buffer's end.
-This allows a continuous operation of the application with a precise sampling frequency while eliminating the need to handle ADC conversions manually. 
-As a segment is ready to be analyzed with every interrupt, the operations needed to process the signal processing are executed inside this Interrupt Service Routine (ISR).
+During runtime, the DMA hardware module fills this buffer and two interrupts are executed when the buffer is filled half way and when it is completely full.
+Because of the circular setup of the DMA, the hardware module fills the buffer continuously and wraps around back to the first address, after reaching the buffer's end.
+This allows a continuous operation of the application with a precise sampling frequency while eliminating the need to handle the ADC conversions manually. 
+As a segment is ready to be analyzed with every interrupt, the operations needed to process the signal processing are executed inside the corresponding Interrupt Service Routine (ISR).
 The result of each segment after the detector is then used to turn on or off a General Purpose Input Output (GPIO) that is connected to a LED.
@@
 After powerup or changes in the environment and therefore during the stabilization of the threshold to its new value, the LED shows
-arrythmic behavior for approximately \SI{5}{\second} before the application continues to operate correctly.
+arrythmic behavior for approximately \SI{5}{\second} before the application continues to operate stable and correctly.
 Other than that, the demo implementation shows that the presented principle also works in reality and that it can be implemented
 with low effort.
-Based on this structure, the code can be expanded to a full clock by decoding the information from the retrieved time code signal.
+Based on this structure, the code could be expanded to a full clock by decoding the information from the retrieved time code signal.
 The code is available in the paper's GitHub repository \cite{b13}.
@@
 This work was inspired by a project that was published by an anonymous author in a german forum about electronics (see \cite{b12}).
-The autor of this paper, L. Hackmann, wants to thank for the knowledge and ideas that were provided through freely accessible entries.
+The autor of this paper, L. Hackmann, wants to thank for the knowledge and ideas that were provided through the freely accessible entries of this online discussion.
 

### 2024-08-30 XX_Hackmann_7217912/demo_implementation/bluePill_DCF77_BP/Core/Src/main.c
Added handed in folder

@@ -1,0 +1,399 @@
+/* USER CODE BEGIN Header */
+/**
+  ******************************************************************************
+  * @file           : main.c
+  * @brief          : Main program body
+  ******************************************************************************
+  * @attention
+  *
+  * Copyright (c) 2024 STMicroelectronics.
+  * All rights reserved.
+  *
+  * This software is licensed under terms that can be found in the LICENSE file
+  * in the root directory of this software component.
+  * If no LICENSE file comes with this software, it is provided AS-IS.
+  *
+  ******************************************************************************
+  */
+/* USER CODE END Header */
+/* Includes ------------------------------------------------------------------*/
+#include "main.h"
+
+/* Private includes ----------------------------------------------------------*/
+/* USER CODE BEGIN Includes */
+#include <math.h>
+/* USER CODE END Includes */
+
+/* Private typedef -----------------------------------------------------------*/
+/* USER CODE BEGIN PTD */
+
+/* USER CODE END PTD */
+
+/* Private define ------------------------------------------------------------*/
+/* USER CODE BEGIN PD */
+#define N 480
+#define halfN 240
+/* USER CODE END PD */
+
+/* Private macro -------------------------------------------------------------*/
+/* USER CODE BEGIN PM */
+
+/* USER CODE END PM */
+
+/* Private variables ---------------------------------------------------------*/
+ADC_HandleTypeDef hadc1;
+DMA_HandleTypeDef hdma_adc1;
+
+TIM_HandleTypeDef htim3;
+
+/* USER CODE BEGIN PV */
+uint16_t adc_buffer[N];
[…]

### 2024-08-30 XX_Hackmann_7217912/demo_implementation/bluePill_DCF77_BP/Core/Src/stm32f1xx_hal_msp.c

@@ -1,0 +1,213 @@
+
+/* USER CODE BEGIN Header */
+/**
+  ******************************************************************************
+  * @file         stm32f1xx_hal_msp.c
+  * @brief        This file provides code for the MSP Initialization
+  *               and de-Initialization codes.
+  ******************************************************************************
+  * @attention
+  *
+  * Copyright (c) 2024 STMicroelectronics.
+  * All rights reserved.
+  *
+  * This software is licensed under terms that can be found in the LICENSE file
+  * in the root directory of this software component.
+  * If no LICENSE file comes with this software, it is provided AS-IS.
+  *
+  ******************************************************************************
+  */
+/* USER CODE END Header */
+
+/* Includes ------------------------------------------------------------------*/
+#include "main.h"
+/* USER CODE BEGIN Includes */
+
+/* USER CODE END Includes */
+extern DMA_HandleTypeDef hdma_adc1;
+
+/* Private typedef -----------------------------------------------------------*/
+/* USER CODE BEGIN TD */
+
+/* USER CODE END TD */
+
+/* Private define ------------------------------------------------------------*/
+/* USER CODE BEGIN Define */
+
+/* USER CODE END Define */
+
+/* Private macro -------------------------------------------------------------*/
+/* USER CODE BEGIN Macro */
+
+/* USER CODE END Macro */
+
+/* Private variables ---------------------------------------------------------*/
+/* USER CODE BEGIN PV */
+
+/* USER CODE END PV */
+
+/* Private function prototypes -----------------------------------------------*/
+/* USER CODE BEGIN PFP */
+
+/* USER CODE END PFP */
+
+/* External functions --------------------------------------------------------*/
[…]

### 2024-08-30 XX_Hackmann_7217912/matlab_simulation/main_script_bandpass_sampling_adaptive_threshold.m

@@ -1,0 +1,211 @@
+clear;
+close all;
+clc;
+
+%% Simulation Parameter Section
+
+%Sampling parameters
+fs = 24e3; %Sampling frequency in Hz
+duration = 30; %Overall sampling duration in s (duration of the simulation)
+
+%AWGN-Channel parameters
+awgn_snr = -5; %SNR after the AWGN-channel in dB
+
+%Goertzel macro parameters
+goertzel_analyzation_freq = 5.5e3; %Analyzation frequency of the Goertzel algorithm in Hz
+goertzel_segment_duration = 0.01; %Duration of the Goertzel algorithm segment in s
+
+%Detector parameters
+det_avg_time = 10; %Time of the Exponential Moving Average in s
+
+
+
+%% Signal Creation Section
+
+%Creating a time vector for the duration of the simulation
+t = 0:1/fs:duration;
+
+%Creating a variable with the number of samples
+N_samples = length(t);
+
+%Carrier signal (cos at 77.5kHz)
+fc = 77.5e3; %Storing the carrier frequency of the DCF77 transmitter in Hz (77.5kHz)
+carrier_signal = cos(2*pi*fc*t);
+
+%Time signal (square wave with frequency of 1Hz, 80% duty cycle, and a range from 0 to 1)
+one_samples_80 = round(0.8 * fs);
+one_samples_90 = round(0.9 * fs);
+
+rect_duty_80 = [zeros(1, fs - one_samples_80), ones(1, one_samples_80)]; %Rect, duty-cycle 80%, starting at 0
+rect_duty_90 = [zeros(1, fs - one_samples_90), ones(1, one_samples_90)]; %Rect, duty-cycle 90%, starting at 0
+
+%Concatenating the symbols after each other to create the time code signal
+time_code_signal = [];
+for i = 1:ceil(duration)
+    if mod(i, 2) == 0 %Alternating the symbols
+        time_code_signal = [time_code_signal, rect_duty_90];
+    else
+        time_code_signal = [time_code_signal, rect_duty_80];
+    end
+end
+time_code_signal = time_code_signal(1:N_samples-1); %Cutting to size
+time_code_signal = [zeros(1, 1), time_code_signal]; %Inserting a zero at the beginning
+
+%Creating the DCF77 signal by using Amplitude Modulation (carrier is reduced to 15% during the gap)
[…]
